---
title: "Analysis: Part I"
format: html
---


**Research Questions:**


Using a cohort of first-time system involved youth, look at adjusted differences in likelihood of being diverted and likelihood of a re-complaint for diverted vs. non-diverted youth.

A. How does the likelihood of being diverted differ by race, sex, and geography?

B. For youth who are diverted, how likely are they to come back into the system with a new complaint or new petition within a year of the initial intake decision? 

<br>

**Methods:**

For research question (A) we will build a series of logistic regression models, adjusting for race/ethnicity, age, offense, risk level, and other factors that may also be related to a decision to divert. Our outcome variable will be diversion/petition (0/1) and our independent variables of interest will be race, sex, and CSU. For research question (B) we will take a similar methodological approach, but restrict our cohort to diverted youth and focus on likelihood of a re-complaint within a year of diversion while adjusting for demographics, offense, risk level, etc. For research question (B) our outcome variable will be re-complaint within a year of the initial intake decision date (0/1) and our independent variables of interest will be race, sex, and CSU.

*Cohort:* first time system involved youth (no prior complaints), 2016-2021

*Method:* Logistic Regression, which allows us to look at the relationship between two variables (like race and decision to divert) while adjusting for other factors that may also be related to our outcome (like offense, risk, etc.).

<br>


```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog","ggpattern","scales","tidylog","ggtext")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal(26, base_family = "Calibri"))

### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_analysis_analytic_data <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Data/VA/analysis/analytic"))

### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_viz <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Output/VA/r_viz_output"))
```

```{r include=FALSE}
### pull in virginia djj analytic file

### read in df_analytic_complaints_disposition_caseload file for analysis
df_analytic_complaints_disposition_caseload <- read_rds(file.path(sharepoint_ojjdp_va_analysis_analytic_data,"df_analytic_complaints_disposition_caseload.rds")) %>% 
  ### when two unique complaints for same individual have same date and both are labelled as first time JJ involvement, keep
  ### most serious offense between them
  filter(jj_history_clean=="No Prior JJ History") %>% 
  ### also filter out complaints with prob/parole violations
  ### and court order violations
  ### and civil commitment offenses
  ### and court summons intake decisions
  ### double check w/ Becky
  filter(dai!="Prob./Parole Violation",
         dai!="Court Order Violation",
         drg!="Civil Commitment",
         intake_decision_label!="COURT SUMMONS") %>% 
  ### create intake flag for cases initially petitioned (to add to disposition model)
  mutate(intake_decision_petition_flag = ifelse(intake_decision_clean=="Petitioned",
                                                1,0)) |> 
  ### create hierarchy of charge types for de-duping youth/intake dates
    mutate(dai_severity_order = case_when(
      dai%in%c("Felony against Persons") ~ 1,
      dai%in%c("Felony Weapons and Felony Narcotics Distribution") ~ 2,
      dai%in%c("Other Felony") ~ 3,
      dai%in%c("Class 1 Misdemeanor Against Persons") ~ 4,
      dai%in%c("Other Class 1 Misdemeanor") ~ 5,
      dai%in%c("Status Offense") ~ 6,
      dai%in%c("Prob./Parole Violation","SENTENCED IN CIRCUIT COURT","Other Violation","Court Order Violation","TRANSFER LEGAL CUSTODY (16.1-278.8.12)") ~ 7,
   TRUE ~ as.numeric(NA))) %>% 
    ### create hierarchy of charge types for de-duping youth/intake dates
    mutate(dai_clean = case_when(
      dai%in%c("Felony against Persons") ~ "Felony against Persons",
      dai%in%c("Felony Weapons and Felony Narcotics Distribution") ~ "Felony Weapons and Felony Narcotics Distribution",
      dai%in%c("Other Felony") ~ "Other Felony",
      dai%in%c("Class 1 Misdemeanor Against Persons") ~ "Class 1 Misdemeanor Against Persons",
      dai%in%c("Other Class 1 Misdemeanor") ~ "Other Class 1 Misdemeanor",
      dai%in%c("Status Offense") & drg!="CHINS" ~ "Status Offense",
      dai%in%c("Status Offense") & drg=="CHINS" ~ "CHINS",
      dai%in%c("Other Violation") ~ "Other Violation",
   TRUE ~ as.character(NA))) %>% 
  mutate(same_dates = ifelse(date_opened==next_complaint_intake_date,
                                                             1,0)) %>% 
  arrange(juvenile_number,
          date_opened,
          dai_severity_order) %>% 
  distinct(juvenile_number,
           .keep_all=TRUE)
  
```

# Research Question A1: Petition
 
<br>

## Table 1. Model Output: Petition

In the following analysis, the outcome variable is binary -- split into petitioned at intake (excluding court summons) and either diverted, resolved, or referred to another agency. All records with other intake complaint decisions are excluded from this analysis.

**NOTE:** I am currently running the regression on youth with no prior JJ history.

Predictors included in model are:

* race

* gender

* age at intake

* CSU

* referral/petitioner source

* category of offense

* fiscal year of intake

* counts of felony, misdemeanor, status, and violation charges associated with intake/complaint


```{r message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(marginaleffects)

intake_complaints_no_prior_jj_to_model_diversion_petitioned <- df_analytic_complaints_disposition_caseload %>%
  filter(jj_history_clean=="No Prior JJ History",
         !is.na(intake_decision_regression_model_petition)==TRUE) %>% 
  mutate(race = fct_relevel(race_clean, "White"),
         gender = fct_relevel(gender_clean, "Male"),
         referral_source_clean = fct_relevel(referral_source_clean, "Other"),
         date_opened_fy = fct_relevel(as.character(date_opened_fy), "2016"),
         intake_decision_regression_model_petition_num = ifelse(intake_decision_regression_model_petition=="Petitioned",
                                           1,0)) %>% 
  distinct(juvenile_number,
           .keep_all=TRUE)

va_diversion_petition_model <- glm(
  intake_decision_regression_model_petition_num ~ race + gender + intake_age + csu + referral_source_clean + dai_clean +
    date_opened_fy + count_misd_with_case + count_felony_with_case + count_status_with_case + count_other_violation_with_case + count_violation_with_case,
  family = "binomial", 
  data = intake_complaints_no_prior_jj_to_model_diversion_petitioned)


tab_model(va_diversion_petition_model,
          p.style = "numeric_stars")

```

<br>

## Model A1 Variance Inflation Factor (VIF)

**Note:** Independent variables with VIF values over 5 indicate "a potentially severe correlation" between two predictors (see https://www.statology.org/variance-inflation-factor-r/)

**Question:** Should we be using GVIF or GVIF^(1/(2*DF)) which accounts for DF in calculating the GVIF?

Here's a relevant post:

* https://stats.stackexchange.com/questions/70679/which-variance-inflation-factor-should-i-be-using-textgvif-or-textgvif



```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### call the car library
library(car)

### calculate the VIF for each predictor variable in the model
car::vif(va_diversion_petition_model)

```

<br>

## Table 2: Predicted Probabilities by Race/Ethnicity

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_race_overall <- predictions(va_diversion_petition_model, 
                                                by = c("race")) %>%
  mutate(rri = estimate / estimate[race == "White"]) %>% 
  dplyr::select(race_eth=race,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high,
                rri)

### print table via kableextra
kable(pred_prob_diversion_petition_race_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 1: Predicted Probabilities by Race/Ethnicity

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_race <- predictions(va_diversion_petition_model, by = c("race")) %>%
  filter(race%in%c("Black","White","Hispanic")) 

pred_prob_diversion_petition_race %>%
  mutate(race = fct_reorder(race, estimate, max)) %>%
  ggplot(aes(estimate, race, color = race)) +
 geom_point(size = 9.5, alpha = 0.9) +
  scale_colour_manual(values = c("#2F7084","#2F7084","#2F7084")) +
  # geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
 scale_x_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(min(0), 
                                max(.45))
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Petition",
    y = NULL,
    color = NULL
  ) +
   theme(plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 14),
        axis.text.x = element_text(face = "bold", hjust = 1, size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t = 15)),
        axis.title.y = element_text(size = 14, margin = margin(r = 15)),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        axis.ticks.length = unit(0, "cm"),
        # panel.grid.major.y = element_blank(),
        # panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()
        ) 


### save out as png
ggsave(
    filename = file.path(sharepoint_ojjdp_va_viz, "pred_prob_petition_race.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br>

## Table 3: Predicted Probabilities by Gender

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%


pred_prob_diversion_petition_gender_overall <- predictions(va_diversion_petition_model, 
                                                by = c("gender")) %>%
  mutate(rri = estimate / estimate[gender == "Female"]) %>% 
  dplyr::select(gender,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high,
                rri)

### print table via kableextra
kable(pred_prob_diversion_petition_gender_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 2a: Predicted Probabilities by Gender

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%


pred_prob_diversion_petition_gender <- predictions(va_diversion_petition_model, by = c("gender")) 

pred_prob_diversion_petition_gender %>%
  mutate(gender = fct_reorder(gender, estimate, max)) %>%
  ggplot(aes(estimate, gender)) +
  geom_point(size = 6.5, alpha = 0.75, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.1)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Petition",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Figure 2b: Predicted Probabilities by Race/Ethnicity and Gender

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_race_by_referral_type <- predictions(va_diversion_petition_model, by = c("race","gender")) %>%
  group_by(gender) %>% 
  mutate(
    rri = estimate / estimate[race == "White"]) %>% 
  ungroup() %>% 
  filter(race%in%c("Black","White","Hispanic")) 

pred_prob_diversion_petition_race_by_referral_type %>%
  mutate(referral_source_clean = fct_reorder(gender, estimate, max)) %>%
  ggplot(aes(estimate, gender, color = race)) +
  geom_point(size = 9.5, alpha = 0.85) +
  scale_colour_manual(values = c("#1F4A58","#2F7084","#87C2D4")) +
    # geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  scale_x_continuous(
    expand = expansion(mult = c(0.1, 0.1)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.15)
  ) +
  guides(color = guide_legend(reverse = TRUE)) +
  expand_limits(x = 0) +
  labs(
    title = NULL,
    x = "Predicted Probability of Petition",
    y = NULL,
    color = NULL) +
   theme(legend.title = element_text(hjust = 0.5,size = 13),
        legend.text = element_text(size = 12),
        axis.text.y = element_markdown(size = 14),
        axis.text.x = element_text(face = "bold", hjust = 1, size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t = 15)),
        axis.title.y = element_text(size = 14, margin = margin(r = 15)),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        axis.ticks.length = unit(0, "cm"),
        # panel.grid.major.y = element_blank(),
        # panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()
        ) 


### save out as png
ggsave(
    filename = file.path(sharepoint_ojjdp_va_viz, "pred_prob_petition_race_gender.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br>

## Table 4: Predicted Probabilities by CSU

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%


pred_prob_diversion_petition_csu_overall <- predictions(va_diversion_petition_model, 
                                                by = c("csu")) %>%
  dplyr::select(csu,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high)

### print table via kableextra
kable(pred_prob_diversion_petition_csu_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 3a: Predicted Probabilities by CSU

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%


pred_prob_diversion_petition_csu <- predictions(va_diversion_petition_model, by = c("csu")) 

pred_prob_diversion_petition_csu %>%
  mutate(csu = fct_reorder(csu, estimate, max),
         state = "va") %>%
  ggplot(aes(estimate, csu, color = state)) +
  geom_point(size = 3.85, alpha = 0.8) +
   scale_colour_manual(values = c("#2F7084")) +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
   scale_x_continuous(
    labels = label_percent(accurracy=1),
    limits = c(min(0), 
                                max(.82))
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Petition",
    y = NULL,
    color = NULL
  ) +
   theme(plot.title = element_text(hjust = 0.5),
        axis.text.y = element_markdown(),
        axis.text.x = element_text(hjust = 1, size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t = 15)),
        axis.title.y = element_text(size = 14, margin = margin(r = 15)),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        axis.ticks.length = unit(0, "cm"),
        # panel.grid.major.y = element_blank(),
        # panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()
        ) 

### save out as png
ggsave(
    filename = file.path(sharepoint_ojjdp_va_viz, "pred_prob_petition_csu_overall.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br>

## Figure 3b: Predicted Probabilities by CSU (mapped)

```{r include=FALSE,message=FALSE,warning=FALSE}
### read in census/acs api key from environmnent
### this allows us to pull census/acs data via the tidycensus package
readRenviron("~/.Renviron")

### read in va county-level shape file and keep geometry for mapping
### from kyle walker/tidycensus: specify cb = TRUE which defaults to the Census Bureau’s cartographic boundary shapefiles. Cartographic boundary shapefiles are preferred to the core TIGER/Line shapefiles in tidycensus as their smaller size speeds up processing and because they are pre-clipped to the US coastline.
va_county_shoreline_clipped <- get_acs(
  geography = "county",
  variables = "B19013_001",
  state = "VA",
  year = 2020,
  geometry = TRUE,
  cb = TRUE
  ) %>%
  clean_names() %>%
  group_by(geoid) %>%
  summarize(geometry = st_union(geometry)) %>%
  ungroup() %>% 
  mutate(state = "VA")

### read in va county-level shape file with fips codes to use as lookup table
va_county_shape <- read_sf("C:\\Users\\abyrum\\OneDrive - The Council of State Governments\\Geospatial_Mapping\\US County Geo Data\\tl_2019_us_county\\tl_2019_us_county.shp") %>%
  clean_names() %>%
  filter(statefp=="51") %>% ### filter by state fip code
  dplyr::select(county=name,
               county_fip=countyfp,
               geoid)

### lose geometry as this is just a lookup table
va_county_lookup <- as.data.frame(va_county_shape) %>% 
    dplyr::select(-(geometry))

### now join va_county_shoreline_clipped and va_county_lookup
va_county_shoreline_clipped_final <- left_join(va_county_shoreline_clipped,
                                               va_county_lookup,
                                               by = "geoid")


### add geometry to counts of complaints, diversions, and petitions by county, csu, and csu region
df_complaints_youth_intake_decision_county_to_join <- df_analytic_complaints_disposition_caseload %>%
  mutate(fips_code = ifelse(fips_code=="X71",
                            "071",fips_code),
         fips_code = ifelse(fips_code=="X21",
                            "021",fips_code)) %>%
  dplyr::group_by(fips_code,csu,csu_region) %>%
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_diverted_flag=="Yes"]),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Resolved/Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Resolved/Dismissed"])) %>%
  ungroup()

### join geometry to file
df_county_level_intake_complaints_summary_geo <- left_join(va_county_shoreline_clipped_final,
                                                     df_complaints_youth_intake_decision_county_to_join,
                                                     by = c("county_fip"="fips_code"))

### group geometry by csu
df_csu_level_intake_summary_geo <- df_county_level_intake_complaints_summary_geo %>%
  dplyr::group_by(csu) %>%
  dplyr::summarise(`All Complaints (N)` = sum(`All Complaints (N)`),
                   geometry = st_union(geometry)) %>%
  ungroup()

```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set constants for mapping
default_font_color <- "#4e4d47"
default_font_family <- "Franklin Gothic Book"
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### create static map theme (based on https://timogrossenbacher.ch/2019/04/bivariate-maps-with-ggplot2-and-sf/)
theme_map <- function(...) {
  theme_minimal() +
  theme(
    text = element_text(family = default_font_family,
                        color = default_font_color),
    # remove all axes
    axis.line = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    # add a subtle grid
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # borders and margins
    plot.margin = unit(c(.5, .5, .2, .5), "cm"),
    panel.border = element_blank(),
    panel.spacing = unit(c(-.1, 0.2, .2, 0.2), "cm"),
    # titles
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 9, hjust = 0,
                               color = default_font_color),
    plot.title = element_text(size = 15, hjust = 0.5,
                              color = default_font_color),
    # plot.subtitle = element_text(size = 10, hjust = 0.5,
    #                              color = default_font_color,
    #                              margin = margin(b = -0.1,
    #                                              t = -0.1,
    #                                              l = 2,
    #                                              unit = "cm"),
    #                              debug = F),
    # # captions
    # plot.caption = element_text(size = 7,
    #                             hjust = .5,
    #                             margin = margin(t = 0.2,
    #                                             b = 0,
    #                                             unit = "cm"),
    #                             color = default_font_color),
    ...
  )
}
```


```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 100%

knitr::opts_chunk$set(dev = "ragg_png")


### join va_county_shoreline_clipped_final and pred_prob_diversion_petition_csu
pred_prob_diversion_petition_csu_geo <- left_join(df_csu_level_intake_summary_geo,
                                                pred_prob_diversion_petition_csu,
                                                     by = "csu")

### create quantiles object
no_classes <- 4

### extract quantiles from var we're mapping
quantiles <- pred_prob_diversion_petition_csu_geo %>%
  pull(estimate) %>%
  quantile(probs = seq(0, 1, length.out = no_classes + 1), 
           na.rm=TRUE) %>%
  as.vector() 

### make labels for map's legend
label_estimate_rate <- c("51% to 80%","41% to 51%","30% to 41%","8% to 30%")

### create a new variable with the specified quantiles
pred_prob_diversion_petition_csu_geo_to_map <- pred_prob_diversion_petition_csu_geo %>%
  mutate(percent_estimate_quartile = cut(-estimate,
                               breaks = -quantiles,
                               right = TRUE,
                               labels = label_estimate_rate,
                               include.lowest = T)) 


### map via ggplot 
ggplot(
  # define main data source
  data = pred_prob_diversion_petition_csu_geo_to_map
) +
  scale_alpha(name = "",
              range = c(0.6, 0),
              guide = F) + # suppress legend
  # add main fill aesthetic
  geom_sf(
    mapping = aes(
      fill = percent_estimate_quartile
      ),
    color = "white",
    size = 0.1
  ) +
  ### use jr palette here
 scale_fill_manual(
    values = c("#1F4A58","#2F7084","#87C2D4","#AFD6E2"),
    name = "Predicted Probability, Petition",
    na.value = "grey50",
    guide = guide_legend(
     keyheight = unit(7.5, units = "mm"),
     title.position = "top",
     reverse = F # display highest on top
  )) +
 # use white stroke borders for county boundaries
  geom_sf(
    data = va_county_shoreline_clipped_final,
    fill = "transparent",
    color = "grey90",
    linewidth = .05
  ) +
  # use white stroke borders for csu boundaries
  geom_sf(
    data = pred_prob_diversion_petition_csu_geo_to_map,
    fill = "transparent",
    color = "white",
    linewidth = .8
  )  +
  # add theme
  theme_map() 


# ### write out
# ggsave(
#     filename = file.path(sharepoint_ojjdp_va_viz, "csu_level_diversion_rate_map.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Table 5: Predicted Probabilities by Charge Type

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%


pred_prob_diversion_petition_dai_overall <- predictions(va_diversion_petition_model, 
                                                by = c("dai_clean"),
                                                type = "response") %>%
  dplyr::select(dai_clean,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high)

### print table via kableextra
kable(pred_prob_diversion_petition_dai_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 3: Predicted Probabilities by Charge Type

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%


pred_prob_diversion_petition_dai <- predictions(va_diversion_petition_model, by = c("dai_clean")) 

pred_prob_diversion_petition_dai %>%
  mutate(dai_clean = fct_reorder(dai_clean, estimate, max)) %>%
  ggplot(aes(estimate, dai_clean)) +
  geom_point(size = 6.5, alpha = 0.7, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.1)
  ) +
  scale_y_discrete(labels = wrap_format(15)) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Petition",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```
<br>

## Figure 4a: Predicted Probabilities of Petition by CSU for Status Offenses 

**NOTE:** This analysis excludes CHINS complaints.

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%


pred_prob_petition_status_by_csu <- predictions(va_diversion_petition_model, by = c("dai_clean","csu")) %>%
  filter(dai_clean%in%c("Status Offense"))

pred_prob_petition_status_by_csu %>%
  mutate(csu = fct_reorder(csu, estimate, max)) %>%
  ggplot(aes(estimate, csu, color = dai_clean)) +
  geom_point(size = 3.5, alpha = 0.9) +
  scale_colour_manual(values = c("#2F7084")) +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_colour_manual(values = rev(c("#2F7084"))) +
  scale_x_continuous(
    expand = expansion(mult = c(0.1, 0.1)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.15)) +
  guides(color = FALSE) +
  expand_limits(x = 0) +
  labs(
    title = NULL,
    x = "Predicted Probability of Petition, Status",
    y = "CSU",
    color = NULL) +
  # theme(
  #   plot.title = element_text(size = 16),
  #   axis.text.y = element_text(size = 8),
  #   axis.title.x = element_text(vjust=-0.5))
  theme(legend.position = "top",
        plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(),
        axis.text.y = element_text(),
        axis.title.x = element_text(margin = margin(t = 15)),
        axis.title.y = element_text(margin = margin(r = 15)),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        axis.ticks.length = unit(0, "cm"),
        # panel.grid.major.y = element_blank(),
        # panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()
        )  

### save out as png
ggsave(
    filename = file.path(sharepoint_ojjdp_va_viz, "pred_prob_csu_status_only.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br>

## Figure 4b: Predicted Probabilities of Petition by CSU for Class 1 Misdemeanor Offenses 

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%


pred_prob_petition_status_by_csu <- predictions(va_diversion_petition_model, by = c("dai_clean","csu")) %>%
  filter(dai_clean%in%c("Class 1 Misdemeanor Against Persons"))

pred_prob_petition_status_by_csu %>%
  mutate(csu = fct_reorder(csu, estimate, max)) %>%
  ggplot(aes(estimate, csu, color = dai_clean)) +
  geom_point(size = 3.5, alpha = 0.75) +
    scale_colour_manual(values = c("#2F7084")) +
  # scale_colour_manual(values = c("#1F4A58","#2F7084","#87C2D4")) +
  # geom_point(size = 3.5, alpha = 0.85, color = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_colour_manual(values = rev(c("#2F7084"))) +
  scale_x_continuous(
    expand = expansion(mult = c(0.1, 0.1)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.15)) +
  guides(color = FALSE) +
  expand_limits(x = 0) +
  labs(
    title = NULL,
    x = "Predicted Probability of Petition, Class 1 Misdemeanor against Persons",
    y = "CSU",
    color = NULL) +
  # theme(
  #   plot.title = element_text(size = 16),
  #   axis.text.y = element_text(size = 8),
  #   axis.title.x = element_text(vjust=-0.5))
  theme(legend.position = "top",
        plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(),
        axis.text.y = element_text(),
        axis.title.x = element_text(margin = margin(t = 15)),
        axis.title.y = element_text(margin = margin(r = 15)),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        axis.ticks.length = unit(0, "cm"),
        # panel.grid.major.y = element_blank(),
        # panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()
        )  

### save out as png
ggsave(
    filename = file.path(sharepoint_ojjdp_va_viz, "pred_prob_csu_misd_only.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br>

## Figure 4c: Predicted Probabilities of Petition by CSU for Felony Offenses 


```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_petition_status_by_csu <- predictions(va_diversion_petition_model, by = c("dai_clean","csu")) %>%
  filter(dai_clean%in%c("Other Felony"))

pred_prob_petition_status_by_csu %>%
  mutate(csu = fct_reorder(csu, estimate, max)) %>%
  ggplot(aes(estimate, csu, color = dai_clean)) +
  geom_point(size = 3.5, alpha = 0.75) +
  scale_colour_manual(values = c("#2F7084")) +
  # geom_point(size = 3.5, alpha = 0.85, color = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_colour_manual(values = rev(c("#2F7084"))) +
  scale_x_continuous(
    expand = expansion(mult = c(0.1, 0.1)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.15)) +
  guides(color = FALSE) +
  expand_limits(x = 0) +
  labs(
    title = NULL,
    x = "Predicted Probability of Petition, Other Felony",
    y = "CSU",
    color = NULL) +
  # theme(
  #   plot.title = element_text(size = 16),
  #   axis.text.y = element_text(size = 8),
  #   axis.title.x = element_text(vjust=-0.5))
  theme(legend.position = "top",
        plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(),
        axis.text.y = element_text(),
        axis.title.x = element_text(margin = margin(t = 15)),
        axis.title.y = element_text(margin = margin(r = 15)),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        axis.ticks.length = unit(0, "cm"),
        # panel.grid.major.y = element_blank(),
        # panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()
        )  

### save out as png
ggsave(
    filename = file.path(sharepoint_ojjdp_va_viz, "pred_prob_csu_felony_only.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br><br>

# Research Question A2: Diversion Outcomes
 
<br>

## Table 6. Model Output: Successful Diversion

In the following analysis, the outcome variable is binary -- split into youth with successful diversion outcomes and those with unsuccessful diversion outcomes (whether petitioned or not). All records with other intake complaint decisions are excluded from this analysis, including diversions which were still active at time of data pull. 

**NOTE:** I am currently running the regression for youth with no prior JJ history **and** who were initially diverted.

Predictors included in model are:

* race

* gender

* age at intake

* CSU

* referral/petitioner source

* category of offense

* fiscal year of intake

* counts of felony, misdemeanor, status, and violation charges associated with intake/complaint


```{r message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

intake_complaints_no_prior_jj_to_model_diversion_outcome <- df_analytic_complaints_disposition_caseload %>%
  filter(jj_history_clean=="No Prior JJ History",
         !is.na(intake_decision_regression_model_petition)==TRUE,
         intake_decision_label%in%c("UNSUCCESSFUL DIVERSION/PETITION FILED", "SUCCESSFUL DIVERSION","UNSUCCESSFUL DIVERSION/NO PETITION FILED")) %>% 
  mutate(race = fct_relevel(race_clean, "White"),
         gender = fct_relevel(gender_clean, "Male"),
         referral_source_clean = fct_relevel(referral_source_clean, "Other"),
         date_opened_fy = fct_relevel(as.character(date_opened_fy), "2016"),
         diversion_success_regression_model_num = ifelse(intake_decision_label=="SUCCESSFUL DIVERSION",
                                           1,0)) %>% 
  distinct(juvenile_number,
           .keep_all=TRUE)

va_diversion_outcome_model <- glm(
  diversion_success_regression_model_num ~ race + gender + intake_age + csu + referral_source_clean + dai_clean +
    date_opened_fy + count_misd_with_case + count_felony_with_case + count_status_with_case + count_other_violation_with_case + count_violation_with_case,
  family = "binomial", 
  data = intake_complaints_no_prior_jj_to_model_diversion_outcome)


tab_model(va_diversion_outcome_model,
          p.style = "numeric_stars")

```

<br>

## Model A2 Variance Inflation Factor (VIF)

**Note:** Independent variables with VIF values over 5 indicate "a potentially severe correlation" between two predictors (see https://www.statology.org/variance-inflation-factor-r/)

**Question:** Should we be using GVIF or GVIF^(1/(2*DF)) which accounts for DF in calculating the GVIF?

Here's a relevant post:

* https://stats.stackexchange.com/questions/70679/which-variance-inflation-factor-should-i-be-using-textgvif-or-textgvif



```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### call the car library
library(car)

### calculate the VIF for each predictor variable in the model
car::vif(va_diversion_outcome_model)

```

<br>

## Table 7: Predicted Probabilities by Race/Ethnicity

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_race_overall <- predictions(va_diversion_outcome_model, 
                                                by = c("race")) %>%
  mutate(rri = estimate / estimate[race == "White"]) %>% 
  dplyr::select(race_eth=race,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high,
                rri)

### print table via kableextra
kable(pred_prob_diversion_petition_race_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 5: Predicted Probabilities by Race/Ethnicity

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_race <- predictions(va_diversion_outcome_model, by = c("race")) %>%
  filter(race%in%c("Black","White","Hispanic")) 

pred_prob_diversion_petition_race %>%
  mutate(race = fct_reorder(race, estimate, max)) %>%
  ggplot(aes(estimate, race, color = race)) +
  geom_point(size = 9.5, alpha = 0.85) +
    scale_color_manual(values = c("#2F7084","#2F7084","#2F7084")) +
  # geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
   scale_x_continuous(
    labels = label_percent(accurracy=1),
    limits = c(min(0), 
                                max(1))
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Successful Diversion",
    y = NULL,
    color = NULL
  ) +
   theme(plot.title = element_text(hjust = 0.5),
        axis.text.y = element_markdown(size = 14),
        axis.text.x = element_text(hjust = 1, size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t = 15)),
        axis.title.y = element_text(size = 14, margin = margin(r = 15)),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        axis.ticks.length = unit(0, "cm"),
        # panel.grid.major.y = element_blank(),
        # panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()
        ) 

### save out as png
ggsave(
    filename = file.path(sharepoint_ojjdp_va_viz, "pred_prob_diversion_success_by_race_eth.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br>

## Table 8: Predicted Probabilities by Gender

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%


pred_prob_diversion_petition_gender_overall <- predictions(va_diversion_outcome_model, 
                                                by = c("gender")) %>%
  mutate(rri = estimate / estimate[gender == "Female"]) %>% 
  dplyr::select(gender,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high,
                rri)

### print table via kableextra
kable(pred_prob_diversion_petition_gender_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 6a: Predicted Probabilities by Gender

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%


pred_prob_diversion_petition_gender <- predictions(va_diversion_outcome_model, by = c("gender")) 

pred_prob_diversion_petition_gender %>%
  mutate(gender = fct_reorder(gender, estimate, max)) %>%
  ggplot(aes(estimate, gender)) +
  geom_point(size = 6.5, alpha = 0.75, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.1)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Successful Diversion",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Figure 6b: Predicted Probabilities by Race/Ethnicity and Gender

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_race_by_referral_type <- predictions(va_diversion_outcome_model, by = c("race","gender")) %>%
  group_by(gender) %>% 
  mutate(
    rri = estimate / estimate[race == "White"]) %>% 
  ungroup() %>% 
  filter(race%in%c("Black","White","Hispanic")) 

pred_prob_diversion_petition_race_by_referral_type %>%
  mutate(referral_source_clean = fct_reorder(gender, estimate, max)) %>%
  ggplot(aes(estimate, gender, color = race)) +
  geom_point(size = 6.5, alpha = 0.75) +
  scale_colour_manual(values = c("#1F4A58","#2F7084","#87C2D4")) +
  scale_x_continuous(
    expand = expansion(mult = c(0.1, 0.1)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.15)
  ) +
  guides(color = guide_legend(reverse = TRUE)) +
  expand_limits(x = 0) +
  labs(
    title = NULL,
    x = "Predicted Probability of Successful Diversion",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title.x = element_text(vjust=-0.5)
  )

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Table 9: Predicted Probabilities by CSU

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_csu_overall <- predictions(va_diversion_outcome_model, 
                                                by = c("csu")) %>%
  dplyr::select(csu,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high)

### print table via kableextra
kable(pred_prob_diversion_petition_csu_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 7a: Predicted Probabilities by CSU

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%


pred_prob_diversion_petition_csu <- predictions(va_diversion_outcome_model, by = c("csu")) 

pred_prob_diversion_petition_csu %>%
  mutate(csu = fct_reorder(csu, estimate, max)) %>%
  ggplot(aes(estimate, csu)) +
  geom_point(size = 3.75, alpha = 0.7, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.1)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Successful Diversion",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Figure 7b: Predicted Probabilities by CSU (mapped)

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 100%

### join va_county_shoreline_clipped_final and pred_prob_diversion_petition_csu
pred_prob_diversion_petition_csu_geo <- left_join(df_csu_level_intake_summary_geo,
                                                pred_prob_diversion_petition_csu,
                                                     by = "csu")

### create quantiles object
no_classes <- 4

### extract quantiles from var we're mapping
quantiles <- pred_prob_diversion_petition_csu_geo %>%
  pull(estimate) %>%
  quantile(probs = seq(0, 1, length.out = no_classes + 1), 
           na.rm=TRUE) %>%
  as.vector() 

### make labels for map's legend
label_estimate_rate <- c("90% to 95%","88% to 90%","85% to 88%","71% to 85%")

### create a new variable with the specified quantiles
pred_prob_diversion_petition_csu_geo_to_map <- pred_prob_diversion_petition_csu_geo %>%
  mutate(percent_estimate_quartile = cut(-estimate,
                               breaks = -quantiles,
                               right = TRUE,
                               labels = label_estimate_rate,
                               include.lowest = T)) 


### map via ggplot 
ggplot(
  # define main data source
  data = pred_prob_diversion_petition_csu_geo_to_map
) +
  scale_alpha(name = "",
              range = c(0.6, 0),
              guide = F) + # suppress legend
  # add main fill aesthetic
  geom_sf(
    mapping = aes(
      fill = percent_estimate_quartile
      ),
    color = "white",
    size = 0.1
  ) +
  ### use jr palette here
 scale_fill_manual(
    values = c("#1F4A58","#2F7084","#87C2D4","#AFD6E2"),
    name = "Predicted Probability, Successful Diversion",
    na.value = "grey50",
    guide = guide_legend(
     keyheight = unit(7.5, units = "mm"),
     title.position = "top",
     reverse = F # display highest on top
  )) +
 # use white stroke borders for county boundaries
  geom_sf(
    data = va_county_shoreline_clipped_final,
    fill = "transparent",
    color = "grey90",
    linewidth = .05
  ) +
  # use white stroke borders for csu boundaries
  geom_sf(
    data = pred_prob_diversion_petition_csu_geo_to_map,
    fill = "transparent",
    color = "white",
    linewidth = .8
  )  +
  # add theme
  theme_map() 


# ### write out
# ggsave(
#     filename = file.path(sharepoint_ojjdp_va_viz, "csu_level_diversion_rate_map.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Table 10: Predicted Probabilities by Charge Type

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%


pred_prob_diversion_petition_dai_overall <- predictions(va_diversion_outcome_model, 
                                                by = c("dai_clean"),
                                                type = "response") %>%
  dplyr::select(dai_clean,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high)

### print table via kableextra
kable(pred_prob_diversion_petition_dai_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 8: Predicted Probabilities by Charge Type

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%


pred_prob_diversion_petition_dai <- predictions(va_diversion_outcome_model, by = c("dai_clean")) 

pred_prob_diversion_petition_dai %>%
  # filter(dai_clean!="CHINS") |> 
  mutate(dai_clean = fct_reorder(dai_clean, estimate, max)) %>%
  ggplot(aes(estimate, dai_clean, colour = dai_clean)) +
  geom_point(size = 6.5, alpha = 0.7) +
  scale_colour_manual(values = c("#2F7084","#2F7084","#2F7084","#2F7084","#2F7084","#2F7084","#2F7084","#2F7084")) +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  scale_x_continuous(
    labels = label_percent(accurracy=1),
    limits = c(min(0), 
                                max(1))
  ) +
  scale_y_discrete(labels = wrap_format(20)) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Successful Diversion",
    y = NULL,
    color = NULL
  ) +
   theme(plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size=11),
        axis.text.x = element_text(hjust = 1, size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t = 15)),
        axis.title.y = element_text(size = 14, margin = margin(r = 15)),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        axis.ticks.length = unit(0, "cm"),
        # panel.grid.major.y = element_blank(),
        # panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()
        ) 

### save out as png
ggsave(
    filename = file.path(sharepoint_ojjdp_va_viz, "pred_prob_diversion_success_by_charge_type.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br>

## Figure 9: Predicted Probabilities of Petition by CSU for Status Offenses 

**NOTE:** This analysis excludes CHINS complaints.

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%


pred_prob_petition_status_by_csu <- predictions(va_diversion_outcome_model, by = c("dai_clean","csu")) %>%
  filter(dai_clean%in%c("Status Offense"))

pred_prob_petition_status_by_csu %>%
  mutate(csu = fct_reorder(csu, estimate, max)) %>%
  ggplot(aes(estimate, csu, color = dai_clean)) +
  geom_point(size = 3.5, alpha = 0.85) +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  scale_colour_manual(values = rev(c("#2F7084"))) +
  scale_x_continuous(
    expand = expansion(mult = c(0.1, 0.1)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.15)) +
  guides(color = FALSE) +
  expand_limits(x = 0) +
  labs(
    title = NULL,
    x = "Predicted Probability of Successful Diversion",
    y = NULL,
    color = NULL) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(vjust=-0.5))

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```


```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

# Research Question A: Disposition


# **NOTE:** To explore JJ system involvement, we have landed on disposition as the outcome instead of petition -- partly because of the notable drop-off between the % of youth petitioned and the % of youth ultimately disposed. We have modeled both petition and disposition. 
# 
# <br>
# 
# ## Table 1. Model Output: Disposition
# 
# In the following analysis, the outcome variable is binary -- split into disposed or not disposed (whether complaint was petitioned and had any disposition data, regardless of disposition)
# 
# **NOTE:** I am currently running the regression on youth with no prior JJ history. 
# 
# Predictors included in model are:
# 
# * temporary: intake_decision_petition_flag (whether case was initially petitioned)
# 
# * race
# 
# * gender
# 
# * age at intake
# 
# * CSU
# 
# * referral/petitioner source
# 
# * category of offense
# 
# * fiscal year of intake
# 
# * counts of felony, misdemeanor, status, and violation charges associated with intake/complaint

intake_complaints_no_prior_jj_to_model_disposition <- df_analytic_complaints_disposition_caseload %>%
  filter(jj_history_clean=="No Prior JJ History",
         !is.na(intake_decision_regression_model_petition)==TRUE) %>% 
  mutate(race = fct_relevel(race_clean, "White"),
         gender = fct_relevel(gender_clean, "Male"),
         referral_source_clean = fct_relevel(referral_source_clean, "Other"),
         date_opened_fy = fct_relevel(as.character(date_opened_fy), "2016"),
         regression_model_dispo_num = ifelse(!is.na(dispo_description_clean)==TRUE,
                                           1,0)) %>% 
  distinct(juvenile_number,
           .keep_all=TRUE)

va_dispo_model <- glm(
  regression_model_dispo_num ~ race + gender + intake_age + csu + referral_source_clean + dai_clean +
    date_opened_fy + count_misd_with_case + count_felony_with_case + count_status_with_case + count_other_violation_with_case + count_violation_with_case + intake_decision_petition_flag,
  family = "binomial", 
  data = intake_complaints_no_prior_jj_to_model_disposition)


tab_model(va_dispo_model,
          p.style = "numeric_stars")

```


```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

## Table 2: Predicted Probabilities by Race/Ethnicity

pred_prob_diversion_dispo_race_overall <- predictions(va_dispo_model, 
                                                by = c("race")) %>%
  mutate(rri = estimate / estimate[race == "White"]) %>% 
  dplyr::select(race_eth=race,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high,
                rri)

### print table via kableextra
kable(pred_prob_diversion_dispo_race_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```



```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

## Figure 1: Predicted Probabilities by Race/Ethnicity

pred_prob_diversion_petition_race <- predictions(va_dispo_model, by = c("race")) %>%
  filter(race%in%c("Black","White","Hispanic","Asian")) 

pred_prob_diversion_petition_race %>%
  mutate(race = fct_reorder(race, estimate, max)) %>%
  ggplot(aes(estimate, race)) +
  geom_point(size = 6.5, alpha = 0.75, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    # expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    # breaks = seq(0, 1, by = 0.1)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Disposition",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```


```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

## Table 3: Predicted Probabilities by Gender

pred_prob_diversion_petition_gender_overall <- predictions(va_dispo_model, 
                                                by = c("gender")) %>%
  mutate(rri = estimate / estimate[gender == "Female"]) %>% 
  dplyr::select(gender,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high,
                rri)

### print table via kableextra
kable(pred_prob_diversion_petition_gender_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```


```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

## Figure 2: Predicted Probabilities by Gender

pred_prob_diversion_petition_gender <- predictions(va_dispo_model, by = c("gender")) 

pred_prob_diversion_petition_gender %>%
  mutate(gender = fct_reorder(gender, estimate, max)) %>%
  ggplot(aes(estimate, gender)) +
  geom_point(size = 6.5, alpha = 0.75, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    # expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(),
    breaks = seq(0, .4, by = 0.05)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Disposition",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

## Table 4: Predicted Probabilities by CSU

pred_prob_dispo_csu_overall <- predictions(va_dispo_model, 
                                                by = c("csu")) %>%
  dplyr::select(csu,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high)

### print table via kableextra
kable(pred_prob_dispo_csu_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```


```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

## Figure 3a: Predicted Probabilities by CSU

pred_prob_dispo_csu <- predictions(va_dispo_model, by = c("csu")) 

pred_prob_dispo_csu %>%
  mutate(csu = fct_reorder(csu, estimate, max)) %>%
  ggplot(aes(estimate, csu)) +
  geom_point(size = 3.75, alpha = 0.7, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.1)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Disposition",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 100%

## Figure 3b: Predicted Probabilities by CSU (mapped)

knitr::opts_chunk$set(dev = "ragg_png")

### join va_county_shoreline_clipped_final and pred_prob_dispo_csu
pred_prob_dispo_csu_geo <- left_join(df_csu_level_intake_summary_geo,
                                                pred_prob_dispo_csu,
                                                     by = "csu")

### create quantiles object
no_classes <- 4

### extract quantiles from var we're mapping
quantiles <- pred_prob_dispo_csu_geo %>%
  pull(estimate) %>%
  quantile(probs = seq(0, 1, length.out = no_classes + 1), 
           na.rm=TRUE) %>%
  as.vector() 

### make labels for map's legend
label_estimate_rate <- c("29% to 48%","21% to 29%","15% to 21%","8% to 15%")

### create a new variable with the specified quantiles
pred_prob_dispo_csu_geo_to_map <- pred_prob_dispo_csu_geo %>%
  mutate(percent_estimate_quartile = cut(-estimate,
                               breaks = -quantiles,
                               right = TRUE,
                               labels = label_estimate_rate,
                               include.lowest = T)) 


### map via ggplot 
ggplot(
  # define main data source
  data = pred_prob_dispo_csu_geo_to_map
) +
  scale_alpha(name = "",
              range = c(0.6, 0),
              guide = F) + # suppress legend
  # add main fill aesthetic
  geom_sf(
    mapping = aes(
      fill = percent_estimate_quartile
      ),
    color = "white",
    size = 0.1
  ) +
  ### use jr palette here
 scale_fill_manual(
    values = c("#1F4A58","#2F7084","#87C2D4","#AFD6E2"),
    name = "Predicted Probability, Disposition",
    na.value = "grey50",
    guide = guide_legend(
     keyheight = unit(7.5, units = "mm"),
     title.position = "top",
     reverse = F # display highest on top
  )) +
  # use white stroke borders for county boundaries
  geom_sf(
    data = va_county_shoreline_clipped_final,
    fill = "transparent",
    color = "grey90",
    linewidth = .05
  ) +
  # use white stroke borders for csu boundaries
  geom_sf(
    data = pred_prob_dispo_csu_geo_to_map,
    fill = "transparent",
    color = "white",
    linewidth = .8
  )  +
  # add theme
  theme_map() 


# ### write out
# ggsave(
#     filename = file.path(sharepoint_ojjdp_va_viz, "csu_level_diversion_rate_map.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```


```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

## Table 5: Predicted Probabilities by Charge Type

pred_prob_dispo_dai_overall <- predictions(va_dispo_model, 
                                                by = c("dai_clean")) %>%
  dplyr::select(dai_clean,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high)

### print table via kableextra
kable(pred_prob_dispo_dai_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```


```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

## Figure 4: Predicted Probabilities by Charge Type

pred_prob_dispo_dai <- predictions(va_dispo_model, by = c("dai_clean")) 

pred_prob_dispo_dai %>%
  mutate(dai_clean = fct_reorder(dai_clean, estimate, max)) %>%
  ggplot(aes(estimate, dai_clean)) +
  geom_point(size = 6.5, alpha = 0.7, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.1)
  ) +
  scale_y_discrete(labels = wrap_format(15)) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Disposition",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

## Figure 5: Predicted Probabilities of Disposition by CSU for Status Offenses 

# **NOTE:** This analysis excludes CHINS complaints. We may want to exclude CSU's with small N sizes -- I haven't yet done that. 

pred_prob_dispo_status_by_csu <- predictions(va_dispo_model, by = c("dai_clean","csu")) %>%
  filter(dai_clean%in%c("Status Offense"))

pred_prob_dispo_status_by_csu %>%
  mutate(csu = fct_reorder(csu, estimate, max)) %>%
  ggplot(aes(estimate, csu, color = dai_clean)) +
  geom_point(size = 3.5, alpha = 0.85) +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  scale_colour_manual(values = rev(c("#2F7084"))) +
  scale_x_continuous(
    expand = expansion(mult = c(0.1, 0.1)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.15)) +
  guides(color = FALSE) +
  expand_limits(x = 0) +
  labs(
    title = NULL,
    x = "Predicted Probability of Disposition",
    y = NULL,
    color = NULL) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(vjust=-0.5))

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br><br>

# Research Question B: Subsequent Complaint

<br>

## Table 6. Model Output: Subsequent Complaint within One Year

In the following analysis, the outcome variable is binary -- whether a youth received another complaint within a year of their first intake (where the intake decision was diversion). All records with other intake complaint decisions are excluded from this analysis.

**NOTE:** I am currently running the regression on youth with no prior JJ history *and* who were initially diverted. I have also removed youth whose first complaint occurred after 6/30/2020. Since the sample is through 6/30/2021, there needs to be at least a year from a youth's initial intake during which there could be a subsequent complaint/petition. 


Predictors included in model are:

* race

* gender

* age at intake

* CSU

* referral/petitioner source

* category of offense

* fiscal year of intake

* counts of felony, misdemeanor, status, and violation charges associated with intake/complaint


```{r message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

intake_initial_diversion_re_complaint_within_a_year_model <- df_analytic_complaints_disposition_caseload %>%
  filter(jj_history_clean=="No Prior JJ History",
         intake_decision_clean=="Diverted",
         !is.na(intake_decision_regression_model_petition)==TRUE,
         date_opened<="2020-06-30") %>% 
  mutate(race = fct_relevel(race_clean, "White"),
         gender = fct_relevel(gender_clean, "Male"),
         referral_source_clean = fct_relevel(referral_source_clean, "Other"),
         date_opened_fy = fct_relevel(as.character(date_opened_fy), "2016")) %>% 
  distinct(juvenile_number,
           .keep_all=TRUE)

va_diversion_re_complaint_model <- glm(
  regression_outcome_new_complaint_one_year_first_time_jj ~ race + gender + intake_age + csu + referral_source_clean + dai_clean +
    date_opened_fy + count_misd_with_case + count_felony_with_case + count_status_with_case + count_other_violation_with_case + count_violation_with_case,
  family = "binomial", 
  data = intake_initial_diversion_re_complaint_within_a_year_model)


tab_model(va_diversion_re_complaint_model,
          p.style = "numeric_stars")

```

<br>

## Model B Variance Inflation Factor (VIF)

**Note:** Independent variables with VIF values over 5 indicate "a potentially severe correlation" between two predictors (see https://www.statology.org/variance-inflation-factor-r/)

**Question:** Should we be using GVIF or GVIF^(1/(2*DF)) which accounts for DF in calculating the GVIF?

Here's a relevant post:

* https://stats.stackexchange.com/questions/70679/which-variance-inflation-factor-should-i-be-using-textgvif-or-textgvif



```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### call the car library
library(car)

### calculate the VIF for each predictor variable in the model
car::vif(va_diversion_re_complaint_model)

```

<br>

## Table 7: Predicted Probabilities by Race/Ethnicity

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_race_overall <- predictions(va_diversion_re_complaint_model, 
                                                by = c("race")) %>%
  mutate(rri = estimate / estimate[race == "White"]) %>% 
  dplyr::select(race_eth=race,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high,
                rri)

### print table via kableextra
kable(pred_prob_diversion_petition_race_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 6: Predicted Probabilities by Race/Ethnicity

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_race <- predictions(va_diversion_re_complaint_model, by = c("race")) %>%
  filter(race%in%c("Black","White","Hispanic","Asian")) 

pred_prob_diversion_petition_race %>%
  mutate(race = fct_reorder(race, estimate, max)) %>%
  ggplot(aes(estimate, race)) +
  geom_point(size = 6.5, alpha = 0.75, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.05)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Second Complaint",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Table 8: Predicted Probabilities by Gender

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_gender_overall <- predictions(va_diversion_re_complaint_model, 
                                                by = c("gender")) %>%
  mutate(rri = estimate / estimate[gender == "Female"]) %>% 
  dplyr::select(gender,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high,
                rri)

### print table via kableextra
kable(pred_prob_diversion_petition_gender_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 7: Predicted Probabilities by Gender

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_gender <- predictions(va_diversion_re_complaint_model, by = c("gender")) 

pred_prob_diversion_petition_gender %>%
  mutate(gender = fct_reorder(gender, estimate, max)) %>%
  ggplot(aes(estimate, gender)) +
  geom_point(size = 6.5, alpha = 0.75, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.05)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Second Complaint",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Table 9: Predicted Probabilities by CSU

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_csu_overall <- predictions(va_diversion_re_complaint_model, 
                                                by = c("csu")) %>%
  dplyr::select(csu,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high)

### print table via kableextra
kable(pred_prob_diversion_petition_csu_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 8a: Predicted Probabilities by CSU

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

va_diversion_re_complaint_model_csu <- predictions(va_diversion_re_complaint_model, by = c("csu")) 

va_diversion_re_complaint_model_csu %>%
  mutate(csu = fct_reorder(csu, estimate, max)) %>%
  mutate(reference = "VA") |> 
  ggplot(aes(estimate, csu, color = reference)) +
  geom_point(size = 3.75, alpha = 0.7) +
  scale_color_manual(values = c("#2F7084")) +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
   scale_x_continuous(
    labels = label_percent(accurracy=1),
    limits = c(min(0), 
                                max(.31))
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Second Complaint",
    y = "CSU",
    color = NULL
  ) +
   theme(plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(),
        axis.text.x = element_text(hjust = 1, size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t = 15)),
        axis.title.y = element_text(size = 14, margin = margin(r = 15)),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        axis.ticks.length = unit(0, "cm"),
        # panel.grid.major.y = element_blank(),
        # panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()
        ) 



### save out as png
ggsave(
    filename = file.path(sharepoint_ojjdp_va_viz, "pred_prob_subsequent_complaint_by_csu.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br>

## Figure 8b: Predicted Probabilities by CSU (mapped)

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 100%

### join va_county_shoreline_clipped_final and va_diversion_re_complaint_model_csu
va_diversion_re_complaint_model_csu_geo <- left_join(df_csu_level_intake_summary_geo,
                                                va_diversion_re_complaint_model_csu,
                                                     by = "csu")

### create quantiles object
no_classes <- 4

### extract quantiles from var we're mapping
quantiles <- va_diversion_re_complaint_model_csu_geo %>%
  pull(estimate) %>%
  quantile(probs = seq(0, 1, length.out = no_classes + 1), 
           na.rm=TRUE) %>%
  as.vector() 

### make labels for map's legend
label_estimate_rate <- c("21% to 27%","18% to 21%","16% to 18%","11% to 16%")

### create a new variable with the specified quantiles
va_diversion_re_complaint_model_csu_geo_to_map <- va_diversion_re_complaint_model_csu_geo %>%
  mutate(percent_estimate_quartile = cut(-estimate,
                               breaks = -quantiles,
                               right = TRUE,
                               labels = label_estimate_rate,
                               include.lowest = T)) 


### map via ggplot 
ggplot(
  # define main data source
  data = va_diversion_re_complaint_model_csu_geo_to_map
) +
  scale_alpha(name = "",
              range = c(0.6, 0),
              guide = F) + # suppress legend
  # add main fill aesthetic
  geom_sf(
    mapping = aes(
      fill = percent_estimate_quartile
      ),
    color = "white",
    size = 0.1
  ) +
  ### use jr palette here
 scale_fill_manual(
    values = c("#1F4A58","#2F7084","#87C2D4","#AFD6E2"),
    name = "Predicted Probability, Second Complaint",
    na.value = "grey50",
    guide = guide_legend(
     keyheight = unit(7.5, units = "mm"),
     title.position = "top",
     reverse = F # display highest on top
  )) +
  # use white stroke borders for county boundaries
  geom_sf(
    data = va_county_shoreline_clipped_final,
    fill = "transparent",
    color = "white",
    linewidth = .05
  ) +
  # use white stroke borders for csu boundaries
  geom_sf(
    data = va_diversion_re_complaint_model_csu_geo_to_map,
    fill = "transparent",
    color = "white",
    linewidth = .85
  )  +
  # add theme
  theme_map() 


# ### write out
# ggsave(
#     filename = file.path(sharepoint_ojjdp_va_viz, "csu_level_diversion_rate_map.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Table 10a: Predicted Probabilities by Charge Type

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_dai_overall <- predictions(va_diversion_re_complaint_model, 
                                                by = c("dai_clean")) %>%
  dplyr::select(dai_clean,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high)

### print table via kableextra
kable(pred_prob_diversion_petition_dai_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Table 10b: Charge Type of Subsequent Complaint (initial offense is status)

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### create denominator -- unique complaint for entire sample
subsequent_complaints_status_sample_denom <- n_distinct(intake_initial_diversion_re_complaint_within_a_year_model$unique_complaint_id[intake_initial_diversion_re_complaint_within_a_year_model$dai=="Status Offense" & intake_initial_diversion_re_complaint_within_a_year_model$next_complaint_dai=="Status Offense" &  intake_initial_diversion_re_complaint_within_a_year_model$regression_outcome_new_complaint_one_year_first_time_jj==1])

### unique complaints split out
df_complaints_youth_intake_decision_table_subsequent_offense <- intake_initial_diversion_re_complaint_within_a_year_model %>% 
    mutate(description_clean_viz = case_when(
    description=="CURFEW VIOLATION BETWEEN 10 PM AND 6 AM" ~ "Curfew",
    description=="MOTION TO SHOW CAUSE - PARENTS FAIL TO OBEY CHINS/DELINQ ORD" ~ "Parents/CHINS",
    description=="Purchase, attempted purchase or possession of tobacco by minor" ~ "Tobacco",
    description=="RUNAWAY, CHILD IN NEED OF SUPERVISION" ~ "Runaway",
    description=="SERVICES, CHILD IN NEED OF" ~ "Need for Services",
    description=="TRUANCY, CHILD IN NEED OF SUPERVISION" ~ "Truancy",
    TRUE ~ as.character(NA)),
    next_complaint_description_clean_viz = case_when(
    next_complaint_description=="CURFEW VIOLATION BETWEEN 10 PM AND 6 AM" ~ "Curfew",
    next_complaint_description=="MOTION TO SHOW CAUSE - PARENTS FAIL TO OBEY CHINS/DELINQ ORD" ~ "Parents/CHINS",
    next_complaint_description=="Purchase, attempted purchase or possession of tobacco by minor" ~ "Tobacco",
    next_complaint_description=="RUNAWAY, CHILD IN NEED OF SUPERVISION" ~ "Runaway",
    next_complaint_description=="SERVICES, CHILD IN NEED OF" ~ "Need for Services",
    next_complaint_description=="TRUANCY, CHILD IN NEED OF SUPERVISION" ~ "Truancy",
    TRUE ~ as.character(NA))) |>
  # filter(description_clean_viz!="Parents/CHINS") |> 
  filter(dai=="Status Offense",
         next_complaint_dai=="Status Offense",
         regression_outcome_new_complaint_one_year_first_time_jj==1) |> 
  dplyr::group_by(next_complaint_description_clean_viz) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/subsequent_complaints_status_sample_denom,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Subsequent Offense` = next_complaint_description_clean_viz)  


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_subsequent_offense, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 9: Predicted Probabilities by Charge Type

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_dai <- predictions(va_diversion_re_complaint_model, by = c("dai_clean")) 

pred_prob_diversion_petition_dai %>%
  mutate(dai_clean = fct_reorder(dai_clean, estimate, max)) %>%
  ggplot(aes(estimate, dai_clean, color = dai_clean)) +
  geom_point(size = 6.5, alpha = 0.7) +
  scale_color_manual(values = c("#2F7084","#2F7084","#2F7084","#2F7084","#2F7084","#2F7084","#2F7084","#2F7084")) +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
   scale_x_continuous(
    labels = label_percent(accurracy=1),
    limits = c(min(0), 
                                max(.4))
  ) +
  scale_y_discrete(labels = wrap_format(15)) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Second Complaint",
    y = NULL,
    color = NULL
  ) +
   theme(plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 10),
        axis.text.x = element_text(hjust = 1, size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t = 15)),
        axis.title.y = element_text(size = 14, margin = margin(r = 15)),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        axis.ticks.length = unit(0, "cm"),
        # panel.grid.major.y = element_blank(),
        # panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()
        ) 


### save out as png
ggsave(
    filename = file.path(sharepoint_ojjdp_va_viz, "pred_prob_subsequent_complaint_by_charge_type.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br>

## Figure 10: Predicted Probabilities by CSU for Status Offenses

**NOTE:** This analysis excludes CHINS complaints.

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_petition_status_by_csu <- predictions(va_diversion_re_complaint_model, by = c("dai_clean","csu")) %>%
  filter(dai_clean%in%c("Status Offense"))

pred_prob_petition_status_by_csu %>%
  mutate(csu = fct_reorder(csu, estimate, max)) %>%
  ggplot(aes(estimate, csu)) +
  geom_point(size = 3.5, alpha = 0.85, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_colour_manual(values = rev(c("#2F7084"))) +
  scale_x_continuous(
    expand = expansion(mult = c(0.1, 0.1)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.05)) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Second Complaint",
    y = NULL,
    color = NULL) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(vjust=-0.5))

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br><br>

```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

# Research Question B2: Subsequent Petition

## Table 11. Model Output: Petition within One Year

# In the following analysis, the outcome variable is binary -- whether a youth received a petitioned complaint within a year of their first intake (where the intake decision was diversion). All records with other intake complaint decisions are excluded from this analysis.
# 
# **NOTE:** I am currently running the regression on youth with no prior JJ history *and* who were initially diverted. I have also removed youth whose first complaint occurred after 6/30/2020. Since the sample is through 6/30/2021, there needs to be at least a year from a youth's initial intake during which there could be a subsequent complaint/petition. 
# 
# 
# Predictors included in model are:
# 
# * race
# 
# * gender
# 
# * age at intake
# 
# * CSU
# 
# * referral/petitioner source
# 
# * category of offense
# 
# * fiscal year of intake
# 
# * counts of felony, misdemeanor, status, and violation charges associated with intake/complaint

intake_initial_diversion_new_petition_within_a_year_model <- df_analytic_complaints_disposition_caseload %>%
  filter(jj_history_clean=="No Prior JJ History",
         intake_decision_clean=="Diverted",
         !is.na(intake_decision_regression_model_petition)==TRUE,
         date_opened<="2020-06-30") %>% 
  mutate(race = fct_relevel(race_clean, "White"),
         gender = fct_relevel(gender_clean, "Male"),
         referral_source_clean = fct_relevel(referral_source_clean, "Other"),
         date_opened_fy = fct_relevel(as.character(date_opened_fy), "2016")) %>% 
  distinct(juvenile_number,
           .keep_all=TRUE)

va_diversion_new_petition_model <- glm(
  regression_outcome_new_petition_one_year_first_time_jj ~ race + gender + intake_age + csu + referral_source_clean + dai_clean +
    date_opened_fy + count_misd_with_case + count_felony_with_case + count_status_with_case + count_other_violation_with_case + count_violation_with_case,
  family = "binomial", 
  data = intake_initial_diversion_new_petition_within_a_year_model)


tab_model(va_diversion_new_petition_model,
          p.style = "numeric_stars")

```



```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

## Table 12: Predicted Probabilities by Race/Ethnicity

pred_prob_diversion_petition_race_overall <- predictions(va_diversion_new_petition_model, 
                                                by = c("race")) %>%
  mutate(rri = estimate / estimate[race == "White"]) %>% 
  dplyr::select(race_eth=race,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high,
                rri)

### print table via kableextra
kable(pred_prob_diversion_petition_race_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```



```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

## Figure 11: Predicted Probabilities by Race/Ethnicity

pred_prob_diversion_petition_race <- predictions(va_diversion_new_petition_model, by = c("race")) %>%
  filter(race%in%c("Black","White","Hispanic","Asian")) 

pred_prob_diversion_petition_race %>%
  mutate(race = fct_reorder(race, estimate, max)) %>%
  ggplot(aes(estimate, race)) +
  geom_point(size = 6.5, alpha = 0.75, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.05)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Second Complaint",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```



```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

## Table 13: Predicted Probabilities by Gender

pred_prob_diversion_petition_gender_overall <- predictions(va_diversion_new_petition_model, 
                                                by = c("gender")) %>%
  mutate(rri = estimate / estimate[gender == "Female"]) %>% 
  dplyr::select(gender,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high,
                rri)

### print table via kableextra
kable(pred_prob_diversion_petition_gender_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```



```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

## Figure 12: Predicted Probabilities by Gender

pred_prob_diversion_petition_gender <- predictions(va_diversion_new_petition_model, by = c("gender")) 

pred_prob_diversion_petition_gender %>%
  mutate(gender = fct_reorder(gender, estimate, max)) %>%
  ggplot(aes(estimate, gender)) +
  geom_point(size = 6.5, alpha = 0.75, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.05)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Subsequent Petition",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```



```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

## Table 14: Predicted Probabilities by CSU

pred_prob_diversion_petition_csu_overall <- predictions(va_diversion_new_petition_model, 
                                                by = c("csu")) %>%
  dplyr::select(csu,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high)

### print table via kableextra
kable(pred_prob_diversion_petition_csu_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```



```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

## Figure 13a: Predicted Probabilities by CSU

va_diversion_new_petition_model_csu <- predictions(va_diversion_new_petition_model, by = c("csu")) 

va_diversion_new_petition_model_csu %>%
  mutate(csu = fct_reorder(csu, estimate, max)) %>%
  ggplot(aes(estimate, csu)) +
  geom_point(size = 3.75, alpha = 0.7, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.05)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Subsequent Petition",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```



```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 100%

## Figure 13b: Predicted Probabilities by CSU (mapped)

### join va_county_shoreline_clipped_final and pred_prob_diversion_petition_csu
va_diversion_new_petition_model_csu_geo <- left_join(df_csu_level_intake_summary_geo,
                                                va_diversion_new_petition_model_csu,
                                                     by = "csu")

### create quantiles object
no_classes <- 4

### extract quantiles from var we're mapping
quantiles <- va_diversion_new_petition_model_csu_geo %>%
  pull(estimate) %>%
  quantile(probs = seq(0, 1, length.out = no_classes + 1), 
           na.rm=TRUE) %>%
  as.vector() 

### make labels for map's legend
label_estimate_rate <- c("14% to 18%","12% to 14%","9% to 12%","7% to 9%")

### create a new variable with the specified quantiles
va_diversion_new_petition_model_csu_geo_to_map <- va_diversion_new_petition_model_csu_geo %>%
  mutate(percent_estimate_quartile = cut(-estimate,
                               breaks = -quantiles,
                               right = TRUE,
                               labels = label_estimate_rate,
                               include.lowest = T)) 


### map via ggplot 
ggplot(
  # define main data source
  data = va_diversion_new_petition_model_csu_geo_to_map
) +
  scale_alpha(name = "",
              range = c(0.6, 0),
              guide = F) + # suppress legend
  # add main fill aesthetic
  geom_sf(
    mapping = aes(
      fill = percent_estimate_quartile
      ),
    color = "white",
    size = 0.1
  ) +
  ### use jr palette here
 scale_fill_manual(
    values = c("#1F4A58","#2F7084","#87C2D4","#AFD6E2"),
    name = "Predicted Probability, Subsequent Petition",
    na.value = "grey50",
    guide = guide_legend(
     keyheight = unit(7.5, units = "mm"),
     title.position = "top",
     reverse = F # display highest on top
  )) +
  # use white stroke borders for county boundaries
  geom_sf(
    data = va_county_shoreline_clipped_final,
    fill = "transparent",
    color = "white",
    linewidth = .05
  ) +
  # use white stroke borders for csu boundaries
  geom_sf(
    data = va_diversion_new_petition_model_csu_geo_to_map,
    fill = "transparent",
    color = "white",
    linewidth = .85
  )  +
  # add theme
  theme_map() 


# ### write out
# ggsave(
#     filename = file.path(sharepoint_ojjdp_va_viz, "csu_level_diversion_rate_map.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```



```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

## Table 15: Predicted Probabilities by Charge Type

pred_prob_diversion_petition_dai_overall <- predictions(va_diversion_new_petition_model, 
                                                by = c("dai_clean")) %>%
  dplyr::select(dai_clean,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high)

### print table via kableextra
kable(pred_prob_diversion_petition_dai_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```



```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

## Figure 14: Predicted Probabilities by Charge Type

pred_prob_diversion_petition_dai <- predictions(va_diversion_new_petition_model, by = c("dai_clean")) 

pred_prob_diversion_petition_dai %>%
  mutate(dai_clean = fct_reorder(dai_clean, estimate, max)) %>%
  ggplot(aes(estimate, dai_clean)) +
  geom_point(size = 6.5, alpha = 0.7, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.05)
  ) +
  scale_y_discrete(labels = wrap_format(15)) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Subsequent Petition",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```




```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

## Figure 15: Predicted Probabilities by CSU for Status Offenses

# **NOTE:** This analysis excludes CHINS complaints. We may want to exclude CSU's with small N sizes -- I haven't yet done that. 

pred_prob_petition_status_by_csu <- predictions(va_diversion_new_petition_model, by = c("dai_clean","csu")) %>%
  filter(dai_clean%in%c("Status Offense"))

pred_prob_petition_status_by_csu %>%
  mutate(csu = fct_reorder(csu, estimate, max)) %>%
  ggplot(aes(estimate, csu)) +
  geom_point(size = 3.5, alpha = 0.85, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_colour_manual(values = rev(c("#2F7084"))) +
  scale_x_continuous(
    expand = expansion(mult = c(0.1, 0.1)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.05)) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Subsequent Petition",
    y = NULL,
    color = NULL) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(vjust=-0.5))

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

