---
title: "Part II Analysis: Race/Ethnicity"
format: html
---

**Data Sample:** 

* Juvenile intake complaints with intake dates from July 1, 2015 - June 30, 2021

* Dispositions – all dispositions for the intake complaints in the sample. 


**Research Question:**

Conduct a front-end system assessment from intake through petition for all complaints 2016-2021.


**Methods:**

We will conduct a descriptive analysis of the front end of the system from intake through petition, provide unadjusted counts, RRI’s and means tests where applicable, by race, sex, offense, risk, CSU, and year for:

*	Complaints

*	Intake decisions: divert, resolve, petition, other

*	Average LOS on diversion 

*	Diversion completions: successful, unsuccessful, other

*	Dispositions on petitioned cases

*Cohort:* All complaints from 2016-2021  

<br>

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())

### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_analysis_analytic_data <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Data/VA/analysis/analytic"))

### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_viz <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Output/VA/r_viz_output"))
```

```{r include=FALSE}
### pull in virginia djj analytic files 

# ### read in df_analytic_complaints_disposition_caseload.rds analytic rds file 
# df_complaints_youth_intake_decision_csu <- read_rds(file.path(sharepoint_ojjdp_va_analysis_analytic_data,"df_complaints_youth_intake_decision_csu.rds"))
# 
# ### read in caseload_clean.rds analytic rds file 
# caseload_clean <- read_rds(file.path(sharepoint_ojjdp_va_analysis_analytic_data,"caseload_clean.rds"))

### read in df_analytic_complaints_disposition_caseload file for analysis
df_analytic_complaints_disposition_caseload <- read_rds(file.path(sharepoint_ojjdp_va_analysis_analytic_data,"df_analytic_complaints_disposition_caseload.rds"))
```

```{r include=FALSE,warning=FALSE,include=FALSE}
### create denominator -- unique complaint for entire sample
unique_complaints_sample_denom <- n_distinct(df_analytic_complaints_disposition_caseload$unique_complaint_id)

### create denominator -- unique youth for entire sample
unique_youth_sample_denom <- n_distinct(df_analytic_complaints_disposition_caseload$juvenile_number)
```


# Tables

## Table 1: Intake Decisions by Race/Ethnicity

**Note:** I am currently coding the following intake decisions as 'Diverted': "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'), and "REQ'D TO PARTICIPATE-DIVERSION" (code of '7'). All other intake decisions are coded as "Not Diverted". See preliminary coding of intake decisions in `Intake Complaints, Intake Decision Descriptions` table on `codebook` page in `sample descriptives` tab

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_youth_intake_decision_table_race <- df_analytic_complaints_disposition_caseload %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean) 

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_analytic_complaints_disposition_caseload %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Race/Ethnicity` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_race_final <- rbind(df_complaints_youth_intake_decision_table_race,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_race_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(8, bold = TRUE)
```

<br>

## Table 2: Disposition Outcomes by Race/Ethnicity

Note: The preliminary options for grouping dispositions that I am using are: Detention, Commitment, Probation/Supervision, Deferral, Community Service, Fine, No further action/none, Restitution, Other. See the `Disposition, Preliminary Disposition Groupings` table on the `codebook` page in the `sample descriptives` tab for a full list of each disposition and I've grouped it. 

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_disposition_outcome_table_race <- df_analytic_complaints_disposition_caseload %>% 
  dplyr::group_by(race_clean) %>% 
    dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Disposed Complaints (column %)` = scales::percent(`All Disposed Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Detention (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Detention"]),
                   `Detention (row %)` = scales::percent(`Detention (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Commitment (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Commitment"]),
                   `Commitment (row %)` = scales::percent(`Commitment (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row %)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Deferral (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Deferral"]),
                   `Deferral (row %)` = scales::percent(`Deferral (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Community Service (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Community Service"]),
                   `Community Service (row %)` = scales::percent(`Community Service (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Fine (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Fine"]),
                   `Fine (row %)` = scales::percent(`Fine (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `No further action/none (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="No further action/none"]),
                   `No further action/none (row %)` = scales::percent(`No further action/none (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Restitution (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Restitution"]),
                   `Restitution (row %)` = scales::percent(`Restitution (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean) 

### unique complaints statewide
df_complaints_disposition_outcome_table_overall <- df_analytic_complaints_disposition_caseload %>% 
    dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Disposed Complaints (column %)` = scales::percent(`All Disposed Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Detention (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Detention"]),
                   `Detention (row %)` = scales::percent(`Detention (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Commitment (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Commitment"]),
                   `Commitment (row %)` = scales::percent(`Commitment (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row %)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Deferral (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Deferral"]),
                   `Deferral (row %)` = scales::percent(`Deferral (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Community Service (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Community Service"]),
                   `Community Service (row %)` = scales::percent(`Community Service (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Fine (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Fine"]),
                   `Fine (row %)` = scales::percent(`Fine (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `No further action/none (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="No further action/none"]),
                   `No further action/none (row %)` = scales::percent(`No further action/none (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Restitution (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Restitution"]),
                   `Restitution (row %)` = scales::percent(`Restitution (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Race/Ethnicity` = "Overall") 

### combine two dataframes for table
df_complaints_disposition_outcome_table_race_final <- rbind(df_complaints_disposition_outcome_table_race,
                                                              df_complaints_disposition_outcome_table_overall)


### print table via kableextra
kable(df_complaints_disposition_outcome_table_race_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(8, bold = TRUE)
```

<br>

## Table : Average Length of Stay on Diversion by Race/Ethnicity

Both measures of LOS on diversion are calculated by DJJ and provided in the `caseload` file -- see codebook page for more information. The two LOS measures are the "Number of days on the workload status "Diversion at Intake" and the "Number of days on the workload status "Diversion Beyond 90 Days"

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

###  mean and median diversion lengths of stay by race/ethnicity
df_diversion_race_eth_los <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(div_at_int)==TRUE | !is.na(div_bey_90)==TRUE) %>% 
  group_by(race_clean) %>% 
  dplyr::summarise(`Mean Diversion LOS (at intake)` = mean(div_at_int,
                                           na.rm=TRUE),
                   `Median Diversion LOS (at intake)` = median(div_at_int,
                                           na.rm=TRUE),
                   `Mean Diversion LOS (beyond 90 days)` = mean(div_bey_90,
                                           na.rm=TRUE),
                   `Median Diversion LOS (beyond 90 days)` = median(div_bey_90,
                                           na.rm=TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean)

### overall mean and median diversion lengths of stay
df_diversion_overall_los <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(div_at_int)==TRUE | !is.na(div_bey_90)==TRUE) %>% 
  dplyr::summarise(`Mean Diversion LOS (at intake)` = mean(div_at_int,
                                           na.rm=TRUE),
                   `Median Diversion LOS (at intake)` = median(div_at_int,
                                           na.rm=TRUE),
                   `Mean Diversion LOS (beyond 90 days)` = mean(div_bey_90,
                                           na.rm=TRUE),
                   `Median Diversion LOS (beyond 90 days)` = median(div_bey_90,
                                           na.rm=TRUE)) %>% 
  mutate(`Race/Ethnicity` = "Overall")
 
### combine two dataframes for table
df_diversion_race_eth_los_final <- rbind(df_diversion_race_eth_los,
                                                             df_diversion_overall_los)

### print table via kableextra
kable(df_diversion_race_eth_los_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(8, bold = TRUE)
```

<br>
