---
title: "Part II Analysis: Intake Decisions and Diversion"
format: html
---

**Data Sample:** 

* Juvenile intake complaints with intake dates from July 1, 2015 - June 30, 2021

* Dispositions – all dispositions for the intake complaints in the sample. 


**Research Question:**

Conduct a front-end system assessment from intake through petition for all complaints 2016-2021.


**Methods:**

We will conduct a descriptive analysis of the front end of the system from intake through petition, provide unadjusted counts, RRI’s and means tests where applicable, by race, sex, offense, risk, CSU, and year for:

*	Complaints

*	Intake decisions: divert, resolve, petition, other

*	Average LOS on diversion 

*	Diversion completions: successful, unsuccessful, other

*	Dispositions on petitioned cases


**Intake Decision Coding Decisions (for part II analysis):**

* Diverted: "UNSUCCESSFUL DIVERSION/PETITION FILED", "SUCCESSFUL DIVERSION","UNSUCCESSFUL DIVERSION/NO PETITION FILED","REQ'D TO PARTICIPATE-DIVERSION"

* Diverted (Informal): "REFERRED TO ANOTHER AGY FOR SV","UNOFFICIAL COUNSELING-FAMILY C"

* Petitioned: "PETITION FILED", "PETITION/DETENTION ORDER FILED","COURT SUMMONS","PETITION/SHELTER CARE FILED"

* Resolved/Dismissed: "RESOLVED", "COMPLAINT UNFOUNDED"

* Other: "DETENTION ORDER ONLY","ACCEPTED VIA ICJ","RETURNED TO PROBATION SUPERVIS","PENDING","SHELTER CARE ONLY","RETURNED TO OUT-OF-STATE"


*Cohort:* All complaints from 2016-2021  

<br>

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())

### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_analysis_analytic_data <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Data/VA/analysis/analytic"))

### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_viz <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Output/VA/r_viz_output"))
```

```{r include=FALSE}
### pull in virginia djj analytic files 

# ### read in df_analytic_complaints_disposition_caseload.rds analytic rds file 
# df_complaints_youth_intake_decision_csu <- read_rds(file.path(sharepoint_ojjdp_va_analysis_analytic_data,"df_complaints_youth_intake_decision_csu.rds"))
# 
# ### read in caseload_clean.rds analytic rds file 
# caseload_clean <- read_rds(file.path(sharepoint_ojjdp_va_analysis_analytic_data,"caseload_clean.rds"))

### read in df_analytic_complaints_disposition_caseload file for analysis
df_analytic_complaints_disposition_caseload <- read_rds(file.path(sharepoint_ojjdp_va_analysis_analytic_data,"df_analytic_complaints_disposition_caseload.rds")) %>% 
  mutate(date_opened_fy = as.character(date_opened_fy)) 
```

```{r include=FALSE,warning=FALSE,include=FALSE}
### create denominator -- unique complaint for entire sample
unique_complaints_sample_denom <- n_distinct(df_analytic_complaints_disposition_caseload$unique_complaint_id)

### create denominator -- unique youth for entire sample
unique_youth_sample_denom <- n_distinct(df_analytic_complaints_disposition_caseload$juvenile_number)
```


# Intake Decisions


## Table 1: Overall Intake Decisions, 2015-2021

**Note:** I am currently coding the following intake decisions as 'Diverted': "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'), and "REQ'D TO PARTICIPATE-DIVERSION" (code of '7'). All other intake decisions are coded as "Not Diverted". See preliminary coding of intake decisions in `Intake Complaints, Intake Decision Descriptions` table on `codebook` page in `sample descriptives` tab

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### overall complaints by diversion status
df_complaints_youth_intake_decision_table <- df_analytic_complaints_disposition_caseload %>% 
  dplyr::group_by(intake_decision_clean) %>% 
  dplyr::summarise(`Unique Complaints (N)` = n_distinct(unique_complaint_id),
            `Complaints, Percent of Sample (%)` = scales::percent(`Unique Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Intake Decision` = intake_decision_clean) 


### print table via kableextra
kable(df_complaints_youth_intake_decision_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Table 2: Intake Decisions by Year

**Note:** I am currently coding the following intake decisions as 'Diverted': "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'), and "REQ'D TO PARTICIPATE-DIVERSION" (code of '7'). All other intake decisions are coded as "Not Diverted". See preliminary coding of intake decisions in `Intake Complaints, Intake Decision Descriptions` table on `codebook` page in `sample descriptives` tab

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%


### unique complaints split out
df_complaints_youth_intake_decision_table_year <- df_analytic_complaints_disposition_caseload %>% 
  dplyr::group_by(date_opened_fy) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Resolved/Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Resolved/Dismissed"]),
                   `Complaints Resolved/Dismissed (row %)` = scales::percent(`Complaints Resolved/Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Year of Complaint` = date_opened_fy) 

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_analytic_complaints_disposition_caseload %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Resolved/Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Resolved/Dismissed"]),
                   `Complaints Resolved/Dismissed (row %)` = scales::percent(`Complaints Resolved/Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Year of Complaint` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_year_final <- rbind(df_complaints_youth_intake_decision_table_year,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_year_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(7, bold = TRUE)
```

<br>

## Table 3: Intake Decisions by Gender

**Note:** I am currently coding the following intake decisions as 'Diverted': "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'), and "REQ'D TO PARTICIPATE-DIVERSION" (code of '7'). All other intake decisions are coded as "Not Diverted". See preliminary coding of intake decisions in `Intake Complaints, Intake Decision Descriptions` table on `codebook` page in `sample descriptives` tab

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_youth_intake_decision_table_gender <- df_analytic_complaints_disposition_caseload %>% 
  dplyr::group_by(gender_clean) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Resolved/Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Resolved/Dismissed"]),
                   `Complaints Resolved/Dismissed (row %)` = scales::percent(`Complaints Resolved/Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Gender` = gender_clean) 

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_analytic_complaints_disposition_caseload %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Resolved/Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Resolved/Dismissed"]),
                   `Complaints Resolved/Dismissed (row %)` = scales::percent(`Complaints Resolved/Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Gender` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_gender_final <- rbind(df_complaints_youth_intake_decision_table_gender,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_gender_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE)
```

<br>

## Table 4: Intake Decisions by Age at Intake

**Note:** I am currently coding the following intake decisions as 'Diverted': "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'), and "REQ'D TO PARTICIPATE-DIVERSION" (code of '7'). All other intake decisions are coded as "Not Diverted". See preliminary coding of intake decisions in `Intake Complaints, Intake Decision Descriptions` table on `codebook` page in `sample descriptives` tab

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_youth_intake_decision_table_age <- df_analytic_complaints_disposition_caseload %>% 
  dplyr::group_by(intake_age_clean) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Resolved/Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Resolved/Dismissed"]),
                   `Complaints Resolved/Dismissed (row %)` = scales::percent(`Complaints Resolved/Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Age at Intake` = intake_age_clean) 

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_analytic_complaints_disposition_caseload %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Resolved/Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Resolved/Dismissed"]),
                   `Complaints Resolved/Dismissed (row %)` = scales::percent(`Complaints Resolved/Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Age at Intake` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_age_final <- rbind(df_complaints_youth_intake_decision_table_age,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_age_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(4, bold = TRUE)
```


<br>

## Table 5a: Complaints by Charge Type over Time (most serious offense; mso_flag == "Y")

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_youth_intake_decision_table_offense <- df_analytic_complaints_disposition_caseload %>% 
  dplyr::group_by(date_opened_fy) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Felony against Persons (N)` = n_distinct(unique_complaint_id[dai=="Felony against Persons"]),
                   `Felony against Persons (row %)` = scales::percent(`Felony against Persons (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Felony Weapons and Felony Narcotics Distribution (N)` = n_distinct(unique_complaint_id[dai=="Felony Weapons and Felony Narcotics Distribution"]),
                   `Felony Weapons and Felony Narcotics Distribution (row %)` = scales::percent(`Felony Weapons and Felony Narcotics Distribution (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other Felony (N)` = n_distinct(unique_complaint_id[dai=="Other Felony"]),
                   `Other Felony (row %)` = scales::percent(`Other Felony (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Class 1 Misdemeanor Against Persons (N)` = n_distinct(unique_complaint_id[dai=="Class 1 Misdemeanor Against Persons"]),
                   `Class 1 Misdemeanor Against Persons (row %)` = scales::percent(`Class 1 Misdemeanor Against Persons (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other Class 1 Misdemeanor (N)` = n_distinct(unique_complaint_id[dai=="Other Class 1 Misdemeanor"]),
                   `Other Class 1 Misdemeanor (row %)` = scales::percent(`Other Class 1 Misdemeanor (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Status Offense (N)` = n_distinct(unique_complaint_id[dai=="Status Offense"]),
                   `Status Offense (row %)` = scales::percent(`Status Offense (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other Violation (N)` = n_distinct(unique_complaint_id[dai=="Other Violation"]),
                   `Other Violation (row %)` = scales::percent(`Other Violation (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Prob./Parole Violation (N)` = n_distinct(unique_complaint_id[dai=="Prob./Parole Violation"]),
                   `Prob./Parole Violation (row %)` = scales::percent(`Prob./Parole Violation (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Court Order Violation (N)` = n_distinct(unique_complaint_id[dai=="Court Order Violation"]),
                   `Court Order Violation (row %)` = scales::percent(`Court Order Violation (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Year of Intake` = date_opened_fy)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_analytic_complaints_disposition_caseload %>% 
   dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Felony against Persons (N)` = n_distinct(unique_complaint_id[dai=="Felony against Persons"]),
                   `Felony against Persons (row %)` = scales::percent(`Felony against Persons (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Felony Weapons and Felony Narcotics Distribution (N)` = n_distinct(unique_complaint_id[dai=="Felony Weapons and Felony Narcotics Distribution"]),
                   `Felony Weapons and Felony Narcotics Distribution (row %)` = scales::percent(`Felony Weapons and Felony Narcotics Distribution (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other Felony (N)` = n_distinct(unique_complaint_id[dai=="Other Felony"]),
                   `Other Felony (row %)` = scales::percent(`Other Felony (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Class 1 Misdemeanor Against Persons (N)` = n_distinct(unique_complaint_id[dai=="Class 1 Misdemeanor Against Persons"]),
                   `Class 1 Misdemeanor Against Persons (row %)` = scales::percent(`Class 1 Misdemeanor Against Persons (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other Class 1 Misdemeanor (N)` = n_distinct(unique_complaint_id[dai=="Other Class 1 Misdemeanor"]),
                   `Other Class 1 Misdemeanor (row %)` = scales::percent(`Other Class 1 Misdemeanor (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Status Offense (N)` = n_distinct(unique_complaint_id[dai=="Status Offense"]),
                   `Status Offense (row %)` = scales::percent(`Status Offense (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other Violation (N)` = n_distinct(unique_complaint_id[dai=="Other Violation"]),
                   `Other Violation (row %)` = scales::percent(`Other Violation (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Prob./Parole Violation (N)` = n_distinct(unique_complaint_id[dai=="Prob./Parole Violation"]),
                   `Prob./Parole Violation (row %)` = scales::percent(`Prob./Parole Violation (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Court Order Violation (N)` = n_distinct(unique_complaint_id[dai=="Court Order Violation"]),
                   `Court Order Violation (row %)` = scales::percent(`Court Order Violation (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Year of Intake` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_offense_final <- rbind(df_complaints_youth_intake_decision_table_offense,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_offense_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(7, bold = TRUE)
```


<br>

## Table 5b: Complaints by Charge Type and Referral Source 

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%


### unique complaints split out
df_complaints_youth_intake_decision_table_offense <- df_analytic_complaints_disposition_caseload %>% 
  dplyr::group_by(referral_source_clean) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Felony against Persons (N)` = n_distinct(unique_complaint_id[dai=="Felony against Persons"]),
                   `Felony against Persons (row %)` = scales::percent(`Felony against Persons (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Felony Weapons and Felony Narcotics Distribution (N)` = n_distinct(unique_complaint_id[dai=="Felony Weapons and Felony Narcotics Distribution"]),
                   `Felony Weapons and Felony Narcotics Distribution (row %)` = scales::percent(`Felony Weapons and Felony Narcotics Distribution (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other Felony (N)` = n_distinct(unique_complaint_id[dai=="Other Felony"]),
                   `Other Felony (row %)` = scales::percent(`Other Felony (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Class 1 Misdemeanor Against Persons (N)` = n_distinct(unique_complaint_id[dai=="Class 1 Misdemeanor Against Persons"]),
                   `Class 1 Misdemeanor Against Persons (row %)` = scales::percent(`Class 1 Misdemeanor Against Persons (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other Class 1 Misdemeanor (N)` = n_distinct(unique_complaint_id[dai=="Other Class 1 Misdemeanor"]),
                   `Other Class 1 Misdemeanor (row %)` = scales::percent(`Other Class 1 Misdemeanor (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Status Offense (N)` = n_distinct(unique_complaint_id[dai=="Status Offense"]),
                   `Status Offense (row %)` = scales::percent(`Status Offense (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other Violation (N)` = n_distinct(unique_complaint_id[dai=="Other Violation"]),
                   `Other Violation (row %)` = scales::percent(`Other Violation (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Prob./Parole Violation (N)` = n_distinct(unique_complaint_id[dai=="Prob./Parole Violation"]),
                   `Prob./Parole Violation (row %)` = scales::percent(`Prob./Parole Violation (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Court Order Violation (N)` = n_distinct(unique_complaint_id[dai=="Court Order Violation"]),
                   `Court Order Violation (row %)` = scales::percent(`Court Order Violation (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Referral Source` = referral_source_clean) %>% 
  arrange(desc(`All Complaints (N)`))

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_analytic_complaints_disposition_caseload %>% 
   dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Felony against Persons (N)` = n_distinct(unique_complaint_id[dai=="Felony against Persons"]),
                   `Felony against Persons (row %)` = scales::percent(`Felony against Persons (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Felony Weapons and Felony Narcotics Distribution (N)` = n_distinct(unique_complaint_id[dai=="Felony Weapons and Felony Narcotics Distribution"]),
                   `Felony Weapons and Felony Narcotics Distribution (row %)` = scales::percent(`Felony Weapons and Felony Narcotics Distribution (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other Felony (N)` = n_distinct(unique_complaint_id[dai=="Other Felony"]),
                   `Other Felony (row %)` = scales::percent(`Other Felony (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Class 1 Misdemeanor Against Persons (N)` = n_distinct(unique_complaint_id[dai=="Class 1 Misdemeanor Against Persons"]),
                   `Class 1 Misdemeanor Against Persons (row %)` = scales::percent(`Class 1 Misdemeanor Against Persons (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other Class 1 Misdemeanor (N)` = n_distinct(unique_complaint_id[dai=="Other Class 1 Misdemeanor"]),
                   `Other Class 1 Misdemeanor (row %)` = scales::percent(`Other Class 1 Misdemeanor (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Status Offense (N)` = n_distinct(unique_complaint_id[dai=="Status Offense"]),
                   `Status Offense (row %)` = scales::percent(`Status Offense (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other Violation (N)` = n_distinct(unique_complaint_id[dai=="Other Violation"]),
                   `Other Violation (row %)` = scales::percent(`Other Violation (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Prob./Parole Violation (N)` = n_distinct(unique_complaint_id[dai=="Prob./Parole Violation"]),
                   `Prob./Parole Violation (row %)` = scales::percent(`Prob./Parole Violation (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Court Order Violation (N)` = n_distinct(unique_complaint_id[dai=="Court Order Violation"]),
                   `Court Order Violation (row %)` = scales::percent(`Court Order Violation (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Referral Source` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_offense_final <- rbind(df_complaints_youth_intake_decision_table_offense,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_offense_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(10, bold = TRUE)
```

<br>

## Table 5c: Complaints by Status Description and Referral Source 

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_youth_intake_decision_table_status <- df_analytic_complaints_disposition_caseload %>% 
  filter(dai=="Status Offense") %>%
  dplyr::group_by(referral_source_clean) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Curfew Violation (N)` = n_distinct(unique_complaint_id[description=="CURFEW VIOLATION BETWEEN 10 PM AND 6 AM"]),
                   `Curfew Violation (row %)` = scales::percent(`Curfew Violation (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Parents/CHINS (N)` = n_distinct(unique_complaint_id[description=="MOTION TO SHOW CAUSE - PARENTS FAIL TO OBEY CHINS/DELINQ ORD"]),
                   `Parents/CHINS (row %)` = scales::percent(`Parents/CHINS (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Purchase or Possession of Tobacco (N)` = n_distinct(unique_complaint_id[description=="Purchase, attempted purchase or possession of tobacco by minor"]),
                   `Purchase or Possession of Tobacco (row %)` = scales::percent(`Purchase or Possession of Tobacco (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Runaway (N)` = n_distinct(unique_complaint_id[description=="RUNAWAY, CHILD IN NEED OF SUPERVISION"]),
                   `Runaway (row %)` = scales::percent(`Runaway (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Child in Need of Services (N)` = n_distinct(unique_complaint_id[description=="SERVICES, CHILD IN NEED OF"]),
                   `Child in Need of Services (row %)` = scales::percent(`Child in Need of Services (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Truancy (N)` = n_distinct(unique_complaint_id[description=="TRUANCY, CHILD IN NEED OF SUPERVISION"]),
                   `Truancy (row %)` = scales::percent(`Truancy (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Referral Source` = referral_source_clean) %>% 
  arrange(desc(`All Complaints (N)`))

### unique complaints statewide
df_complaints_youth_intake_decision_table_status_overall <- df_analytic_complaints_disposition_caseload %>% 
  filter(dai=="Status Offense") %>%
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Curfew Violation (N)` = n_distinct(unique_complaint_id[description=="CURFEW VIOLATION BETWEEN 10 PM AND 6 AM"]),
                   `Curfew Violation (row %)` = scales::percent(`Curfew Violation (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Parents/CHINS (N)` = n_distinct(unique_complaint_id[description=="MOTION TO SHOW CAUSE - PARENTS FAIL TO OBEY CHINS/DELINQ ORD"]),
                   `Parents/CHINS (row %)` = scales::percent(`Parents/CHINS (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Purchase or Possession of Tobacco (N)` = n_distinct(unique_complaint_id[description=="Purchase, attempted purchase or possession of tobacco by minor"]),
                   `Purchase or Possession of Tobacco (row %)` = scales::percent(`Purchase or Possession of Tobacco (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Runaway (N)` = n_distinct(unique_complaint_id[description=="RUNAWAY, CHILD IN NEED OF SUPERVISION"]),
                   `Runaway (row %)` = scales::percent(`Runaway (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Child in Need of Services (N)` = n_distinct(unique_complaint_id[description=="SERVICES, CHILD IN NEED OF"]),
                   `Child in Need of Services (row %)` = scales::percent(`Child in Need of Services (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Truancy (N)` = n_distinct(unique_complaint_id[description=="TRUANCY, CHILD IN NEED OF SUPERVISION"]),
                   `Truancy (row %)` = scales::percent(`Truancy (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  dplyr::mutate(`Referral Source` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_status_final <- rbind(df_complaints_youth_intake_decision_table_status,
                                                              df_complaints_youth_intake_decision_table_status_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_status_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(10, bold = TRUE)
```

<br>

## Table 5d: Intake Decisions by Offense Type (most serious offense; mso_flag == "Y")

**Note:** I am currently coding the following intake decisions as 'Diverted': "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'), and "REQ'D TO PARTICIPATE-DIVERSION" (code of '7'). All other intake decisions are coded as "Not Diverted". See preliminary coding of intake decisions in `Intake Complaints, Intake Decision Descriptions` table on `codebook` page in `sample descriptives` tab

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_youth_intake_decision_table_offense <- df_analytic_complaints_disposition_caseload %>% 
  dplyr::group_by(dai) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Resolved/Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Resolved/Dismissed"]),
                   `Complaints Resolved/Dismissed (row %)` = scales::percent(`Complaints Resolved/Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Offense Description` = dai)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_analytic_complaints_disposition_caseload %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Resolved/Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Resolved/Dismissed"]),
                   `Complaints Resolved/Dismissed (row %)` = scales::percent(`Complaints Resolved/Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Offense Description` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_offense_final <- rbind(df_complaints_youth_intake_decision_table_offense,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_offense_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(10, bold = TRUE)
```

<br>

## Table 5e: Intake Decisions by Status Offense Type (most serious offense is status; mso_flag == "Y")

**Note:** I am currently coding the following intake decisions as 'Diverted': "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'), and "REQ'D TO PARTICIPATE-DIVERSION" (code of '7'). All other intake decisions are coded as "Not Diverted". See preliminary coding of intake decisions in `Intake Complaints, Intake Decision Descriptions` table on `codebook` page in `sample descriptives` tab

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### create denominator -- unique complaint for entire sample
unique_complaints_status_sample_denom <- n_distinct(df_analytic_complaints_disposition_caseload$unique_complaint_id[df_analytic_complaints_disposition_caseload$dai=="Status Offense"])

### create denominator -- unique youth for entire sample
unique_youth_status_sample_denom <- n_distinct(df_analytic_complaints_disposition_caseload$juvenile_number[df_analytic_complaints_disposition_caseload$dai=="Status Offense"])

### unique complaints split out
df_complaints_youth_intake_decision_table_offense_status <- df_analytic_complaints_disposition_caseload %>% 
  filter(dai=="Status Offense") %>% 
  dplyr::group_by(drg) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_status_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Resolved/Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Resolved/Dismissed"]),
                   `Complaints Resolved/Dismissed (row %)` = scales::percent(`Complaints Resolved/Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>%  
  ungroup() %>% 
  dplyr::rename(`Status Offense Description` = drg)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_analytic_complaints_disposition_caseload %>% 
  filter(dai=="Status Offense") %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_status_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Resolved/Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Resolved/Dismissed"]),
                   `Complaints Resolved/Dismissed (row %)` = scales::percent(`Complaints Resolved/Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Status Offense Description` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_offense_status_final <- rbind(df_complaints_youth_intake_decision_table_offense_status,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_offense_status_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(4, bold = TRUE)
```

<br>

## Table 5f: Intake Decisions by Status Offense Description (most serious offense is status; mso_flag == "Y")

**Note:** I am currently coding the following intake decisions as 'Diverted': "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'), and "REQ'D TO PARTICIPATE-DIVERSION" (code of '7'). All other intake decisions are coded as "Not Diverted". See preliminary coding of intake decisions in `Intake Complaints, Intake Decision Descriptions` table on `codebook` page in `sample descriptives` tab

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_youth_intake_decision_table_offense_status_desc <- df_analytic_complaints_disposition_caseload %>% 
  filter(dai=="Status Offense") %>% 
  dplyr::group_by(description) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_status_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Resolved/Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Resolved/Dismissed"]),
                   `Complaints Resolved/Dismissed (row %)` = scales::percent(`Complaints Resolved/Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>%  
  ungroup() %>% 
  dplyr::rename(`Status Offense Description` = description)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_analytic_complaints_disposition_caseload %>% 
  filter(dai=="Status Offense") %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_status_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Resolved/Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Resolved/Dismissed"]),
                   `Complaints Resolved/Dismissed (row %)` = scales::percent(`Complaints Resolved/Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Status Offense Description` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_offense_status_desc_final <- rbind(df_complaints_youth_intake_decision_table_offense_status_desc,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_offense_status_desc_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(7, bold = TRUE)
```

<br>


## Table 5g: Complaints by Status Description over Time

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_youth_intake_decision_table_status <- df_analytic_complaints_disposition_caseload %>% 
  filter(dai=="Status Offense") %>%
  dplyr::group_by(date_opened_fy) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Curfew Violation (N)` = n_distinct(unique_complaint_id[description=="CURFEW VIOLATION BETWEEN 10 PM AND 6 AM"]),
                   `Curfew Violation (row %)` = scales::percent(`Curfew Violation (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Parents/CHINS (N)` = n_distinct(unique_complaint_id[description=="MOTION TO SHOW CAUSE - PARENTS FAIL TO OBEY CHINS/DELINQ ORD"]),
                   `Parents/CHINS (row %)` = scales::percent(`Parents/CHINS (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Purchase or Possession of Tobacco (N)` = n_distinct(unique_complaint_id[description=="Purchase, attempted purchase or possession of tobacco by minor"]),
                   `Purchase or Possession of Tobacco (row %)` = scales::percent(`Purchase or Possession of Tobacco (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Runaway (N)` = n_distinct(unique_complaint_id[description=="RUNAWAY, CHILD IN NEED OF SUPERVISION"]),
                   `Runaway (row %)` = scales::percent(`Runaway (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Child in Need of Services (N)` = n_distinct(unique_complaint_id[description=="SERVICES, CHILD IN NEED OF"]),
                   `Child in Need of Services (row %)` = scales::percent(`Child in Need of Services (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Truancy (N)` = n_distinct(unique_complaint_id[description=="TRUANCY, CHILD IN NEED OF SUPERVISION"]),
                   `Truancy (row %)` = scales::percent(`Truancy (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Year of Intake` = date_opened_fy) 

### unique complaints statewide
df_complaints_youth_intake_decision_table_status_overall <- df_analytic_complaints_disposition_caseload %>% 
  filter(dai=="Status Offense") %>%
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Curfew Violation (N)` = n_distinct(unique_complaint_id[description=="CURFEW VIOLATION BETWEEN 10 PM AND 6 AM"]),
                   `Curfew Violation (row %)` = scales::percent(`Curfew Violation (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Parents/CHINS (N)` = n_distinct(unique_complaint_id[description=="MOTION TO SHOW CAUSE - PARENTS FAIL TO OBEY CHINS/DELINQ ORD"]),
                   `Parents/CHINS (row %)` = scales::percent(`Parents/CHINS (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Purchase or Possession of Tobacco (N)` = n_distinct(unique_complaint_id[description=="Purchase, attempted purchase or possession of tobacco by minor"]),
                   `Purchase or Possession of Tobacco (row %)` = scales::percent(`Purchase or Possession of Tobacco (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Runaway (N)` = n_distinct(unique_complaint_id[description=="RUNAWAY, CHILD IN NEED OF SUPERVISION"]),
                   `Runaway (row %)` = scales::percent(`Runaway (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Child in Need of Services (N)` = n_distinct(unique_complaint_id[description=="SERVICES, CHILD IN NEED OF"]),
                   `Child in Need of Services (row %)` = scales::percent(`Child in Need of Services (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Truancy (N)` = n_distinct(unique_complaint_id[description=="TRUANCY, CHILD IN NEED OF SUPERVISION"]),
                   `Truancy (row %)` = scales::percent(`Truancy (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  dplyr::mutate(`Year of Intake` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_status_final <- rbind(df_complaints_youth_intake_decision_table_status,
                                                              df_complaints_youth_intake_decision_table_status_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_status_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(7, bold = TRUE)
```

<br>

## Table 6: Intake Decisions by Prior JJ History 

**Note:** I am currently coding the following intake decisions as 'Diverted': "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'), and "REQ'D TO PARTICIPATE-DIVERSION" (code of '7'). All other intake decisions are coded as "Not Diverted". See preliminary coding of intake decisions in `Intake Complaints, Intake Decision Descriptions` table on `codebook` page in `sample descriptives` tab

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_youth_intake_decision_table_jj_history <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(jj_history_clean)==TRUE) %>% 
  dplyr::group_by(jj_history_clean) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Resolved/Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Resolved/Dismissed"]),
                   `Complaints Resolved/Dismissed (row %)` = scales::percent(`Complaints Resolved/Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`JJ History` = jj_history_clean)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(jj_history_clean)==TRUE) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Resolved/Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Resolved/Dismissed"]),
                   `Complaints Resolved/Dismissed (row %)` = scales::percent(`Complaints Resolved/Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`JJ History` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_jj_history_final <- rbind(df_complaints_youth_intake_decision_table_jj_history,
                                                             df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_jj_history_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 7: Intake Decisions by Petitioner Type/Referral Source

**Note:** I am currently coding the following intake decisions as 'Diverted': "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'), and "REQ'D TO PARTICIPATE-DIVERSION" (code of '7'). All other intake decisions are coded as "Not Diverted". See preliminary coding of intake decisions in `Intake Complaints, Intake Decision Descriptions` table on `codebook` page in `sample descriptives` tab

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_youth_intake_decision_table_pet_desc <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(referral_source_clean)==TRUE) %>% 
  dplyr::group_by(referral_source_clean) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Resolved/Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Resolved/Dismissed"]),
                   `Complaints Resolved/Dismissed (row %)` = scales::percent(`Complaints Resolved/Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Petitioner/Referral Source` = referral_source_clean) %>% 
  arrange(desc(`All Complaints (N)`))

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(referral_source_clean)==TRUE) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Resolved/Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Resolved/Dismissed"]),
                   `Complaints Resolved/Dismissed (row %)` = scales::percent(`Complaints Resolved/Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Petitioner/Referral Source` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_pet_desc_final <- rbind(df_complaints_youth_intake_decision_table_pet_desc,
                                                             df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_pet_desc_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(9, bold = TRUE)
```

<br>

# Diversion Length of Stay


## Table 8: Average Length of Stay on Diversion by Status Offense Description (most serious offense is status; mso_flag == "Y")

Both measures of LOS on diversion are calculated by DJJ and provided in the `caseload` file -- see codebook page for more information. The two LOS measures are the "Number of days on the workload status "Diversion at Intake" and the "Number of days on the workload status "Diversion Beyond 90 Days". Filtered on cases/complaints diverted only.

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

###  mean and median diversion lengths of stay by race/ethnicity
df_diversion_offense_los <- df_analytic_complaints_disposition_caseload %>%
  filter(dai=="Status Offense",
         intake_decision_clean=="Diverted") %>% 
  filter(!is.na(div_at_int)==TRUE | !is.na(div_bey_90)==TRUE) %>% 
  group_by(description) %>% 
  dplyr::summarise(`Mean Diversion LOS (at intake)` = mean(div_at_int,
                                           na.rm=TRUE),
                   `Median Diversion LOS (at intake)` = median(div_at_int,
                                           na.rm=TRUE),
                   `Mean Diversion LOS (beyond 90 days)` = mean(div_bey_90,
                                           na.rm=TRUE),
                   `Median Diversion LOS (beyond 90 days)` = median(div_bey_90,
                                           na.rm=TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Offense Description` = description)

### overall mean and median diversion lengths of stay
df_diversion_overall_los <- df_analytic_complaints_disposition_caseload %>% 
  filter(dai=="Status Offense",
         intake_decision_clean=="Diverted") %>% 
  filter(!is.na(div_at_int)==TRUE | !is.na(div_bey_90)==TRUE) %>% 
  dplyr::summarise(`Mean Diversion LOS (at intake)` = mean(div_at_int,
                                           na.rm=TRUE),
                   `Median Diversion LOS (at intake)` = median(div_at_int,
                                           na.rm=TRUE),
                   `Mean Diversion LOS (beyond 90 days)` = mean(div_bey_90,
                                           na.rm=TRUE),
                   `Median Diversion LOS (beyond 90 days)` = median(div_bey_90,
                                           na.rm=TRUE)) %>% 
  mutate(`Offense Description` = "Overall")
 
### combine two dataframes for table
df_diversion_offense_los_final <- rbind(df_diversion_offense_los,
                                        df_diversion_overall_los)

### print table via kableextra
kable(df_diversion_offense_los_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 9: Average Length of Stay on Diversion by JJ History

Both measures of LOS on diversion are calculated by DJJ and provided in the `caseload` file -- see codebook page for more information. The two LOS measures are the "Number of days on the workload status "Diversion at Intake" and the "Number of days on the workload status "Diversion Beyond 90 Days"

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

###  mean and median diversion lengths of stay by race/ethnicity
df_diversion_jj_history_los <- df_analytic_complaints_disposition_caseload %>%
  filter(!is.na(jj_history_clean)==TRUE,
         intake_decision_clean=="Diverted") %>% 
  filter(!is.na(div_at_int)==TRUE | !is.na(div_bey_90)==TRUE) %>% 
  dplyr::group_by(jj_history_clean) %>% 
  dplyr::summarise(`Mean Diversion LOS (at intake)` = mean(div_at_int,
                                           na.rm=TRUE),
                   `Median Diversion LOS (at intake)` = median(div_at_int,
                                           na.rm=TRUE),
                   `Mean Diversion LOS (beyond 90 days)` = mean(div_bey_90,
                                           na.rm=TRUE),
                   `Median Diversion LOS (beyond 90 days)` = median(div_bey_90,
                                           na.rm=TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`JJ History` = jj_history_clean)

### overall mean and median diversion lengths of stay
df_diversion_overall_los <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(jj_history_clean)==TRUE,
         intake_decision_clean=="Diverted") %>% 
  filter(!is.na(div_at_int)==TRUE | !is.na(div_bey_90)==TRUE) %>% 
  dplyr::summarise(`Mean Diversion LOS (at intake)` = mean(div_at_int,
                                           na.rm=TRUE),
                   `Median Diversion LOS (at intake)` = median(div_at_int,
                                           na.rm=TRUE),
                   `Mean Diversion LOS (beyond 90 days)` = mean(div_bey_90,
                                           na.rm=TRUE),
                   `Median Diversion LOS (beyond 90 days)` = median(div_bey_90,
                                           na.rm=TRUE)) %>% 
  mutate(`JJ History` = "Overall")
 
### combine two dataframes for table
df_diversion_jj_history_los_final <- rbind(df_diversion_jj_history_los,
                                        df_diversion_overall_los)

### print table via kableextra
kable(df_diversion_jj_history_los_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 10: Average Length of Stay on Diversion by Petitioner/Referral Source

Both measures of LOS on diversion are calculated by DJJ and provided in the `caseload` file -- see codebook page for more information. The two LOS measures are the "Number of days on the workload status "Diversion at Intake" and the "Number of days on the workload status "Diversion Beyond 90 Days"

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

###  mean and median diversion lengths of stay by race/ethnicity
df_diversion_referral_source_los <- df_analytic_complaints_disposition_caseload %>%
  filter(!is.na(referral_source_clean)==TRUE,
         intake_decision_clean=="Diverted") %>% 
  filter(!is.na(div_at_int)==TRUE | !is.na(div_bey_90)==TRUE) %>% 
  dplyr::group_by(referral_source_clean) %>% 
  dplyr::summarise(`Mean Diversion LOS (at intake)` = mean(div_at_int,
                                           na.rm=TRUE),
                   `Median Diversion LOS (at intake)` = median(div_at_int,
                                           na.rm=TRUE),
                   `Mean Diversion LOS (beyond 90 days)` = mean(div_bey_90,
                                           na.rm=TRUE),
                   `Median Diversion LOS (beyond 90 days)` = median(div_bey_90,
                                           na.rm=TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Petitioner/Referral Source` = referral_source_clean)

### overall mean and median diversion lengths of stay
df_diversion_overall_los <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(referral_source_clean)==TRUE,
         intake_decision_clean=="Diverted") %>% 
  filter(!is.na(div_at_int)==TRUE | !is.na(div_bey_90)==TRUE) %>% 
  dplyr::summarise(`Mean Diversion LOS (at intake)` = mean(div_at_int,
                                           na.rm=TRUE),
                   `Median Diversion LOS (at intake)` = median(div_at_int,
                                           na.rm=TRUE),
                   `Mean Diversion LOS (beyond 90 days)` = mean(div_bey_90,
                                           na.rm=TRUE),
                   `Median Diversion LOS (beyond 90 days)` = median(div_bey_90,
                                           na.rm=TRUE)) %>% 
  mutate(`Petitioner/Referral Source` = "Overall")
 
### combine two dataframes for table
df_diversion_referral_source_los_final <- rbind(df_diversion_referral_source_los,
                                        df_diversion_overall_los)

### print table via kableextra
kable(df_diversion_referral_source_los_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(9, bold = TRUE)
```

<br>

## Table 11: Average Length of Stay on Diversion by Gender

Both measures of LOS on diversion are calculated by DJJ and provided in the `caseload` file -- see codebook page for more information. The two LOS measures are the "Number of days on the workload status "Diversion at Intake" and the "Number of days on the workload status "Diversion Beyond 90 Days"

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

###  mean and median diversion lengths of stay by race/ethnicity
df_diversion_gender_los <- df_analytic_complaints_disposition_caseload %>% 
  filter((!is.na(div_at_int)==TRUE | !is.na(div_bey_90)==TRUE),
         intake_decision_clean=="Diverted") %>% 
  group_by(gender_clean) %>% 
  dplyr::summarise(`Mean Diversion LOS (at intake)` = mean(div_at_int,
                                           na.rm=TRUE),
                   `Median Diversion LOS (at intake)` = median(div_at_int,
                                           na.rm=TRUE),
                   `Mean Diversion LOS (beyond 90 days)` = mean(div_bey_90,
                                           na.rm=TRUE),
                   `Median Diversion LOS (beyond 90 days)` = median(div_bey_90,
                                           na.rm=TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Gender` = gender_clean)

### overall mean and median diversion lengths of stay
df_diversion_overall_los <- df_analytic_complaints_disposition_caseload %>% 
  filter((!is.na(div_at_int)==TRUE | !is.na(div_bey_90)==TRUE),
         intake_decision_clean=="Diverted") %>% 
  dplyr::summarise(`Mean Diversion LOS (at intake)` = mean(div_at_int,
                                           na.rm=TRUE),
                   `Median Diversion LOS (at intake)` = median(div_at_int,
                                           na.rm=TRUE),
                   `Mean Diversion LOS (beyond 90 days)` = mean(div_bey_90,
                                           na.rm=TRUE),
                   `Median Diversion LOS (beyond 90 days)` = median(div_bey_90,
                                           na.rm=TRUE)) %>% 
  mutate(`Gender` = "Overall")
 
### combine two dataframes for table
df_diversion_gender_los_final <- rbind(df_diversion_gender_los,
                                                             df_diversion_overall_los)

### print table via kableextra
kable(df_diversion_gender_los_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE)
```

<br>

# Diversion Outcomes


## Table 11: Diversion Outcomes, 2015-2021

**Note:** Options for diversion outcomes include successful, unsuccessful with petition, and unsuccessful without petition

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### by year
df_diversion_outcome_year_overall <- df_analytic_complaints_disposition_caseload %>% 
  filter(intake_decision_clean=="Diverted") %>% 
  dplyr::group_by(date_opened_fy) %>% 
   dplyr::summarise(`Unique Complaints Diverted (N)` = n_distinct(unique_complaint_id),
                    `Unique Complaints w/ Successful Diversion (N)` = n_distinct(unique_complaint_id[diversion_successful_flag==1]),
                    `Successful Diversion Rate (%)` = scales::percent(`Unique Complaints w/ Successful Diversion (N)`/`Unique Complaints Diverted (N)`,
                                                                       accuracy = .1),
                    `Unique Complaints w/ Unsuccessful Diversion without petition (N)` = n_distinct(unique_complaint_id[diversion_not_successful_no_petition_flag==1]),
                    `Unsuccessful Diversion without petition (%)` = scales::percent(`Unique Complaints w/ Unsuccessful Diversion without petition (N)`/`Unique Complaints Diverted (N)`,
                                                                       accuracy = .1),
                    `Unique Complaints w/ Unsuccessful Diversion (with petition) (N)` = n_distinct(unique_complaint_id[diversion_not_successful_petition_flag==1]),
                    `Unsuccessful Diversion with petition (%)` = scales::percent(`Unique Complaints w/ Unsuccessful Diversion (with petition) (N)`/`Unique Complaints Diverted (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Year` = date_opened_fy)

### overall
df_diversion_outcome_overall <- df_analytic_complaints_disposition_caseload %>% 
  filter(intake_decision_clean=="Diverted") %>% 
   dplyr::summarise(`Unique Complaints Diverted (N)` = n_distinct(unique_complaint_id),
                    `Unique Complaints w/ Successful Diversion (N)` = n_distinct(unique_complaint_id[diversion_successful_flag==1]),
                    `Successful Diversion Rate (%)` = scales::percent(`Unique Complaints w/ Successful Diversion (N)`/`Unique Complaints Diverted (N)`,
                                                                       accuracy = .1),
                    `Unique Complaints w/ Unsuccessful Diversion without petition (N)` = n_distinct(unique_complaint_id[diversion_not_successful_no_petition_flag==1]),
                    `Unsuccessful Diversion without petition (%)` = scales::percent(`Unique Complaints w/ Unsuccessful Diversion without petition (N)`/`Unique Complaints Diverted (N)`,
                                                                       accuracy = .1),
                    `Unique Complaints w/ Unsuccessful Diversion (with petition) (N)` = n_distinct(unique_complaint_id[diversion_not_successful_petition_flag==1]),
                    `Unsuccessful Diversion with petition (%)` = scales::percent(`Unique Complaints w/ Unsuccessful Diversion (with petition) (N)`/`Unique Complaints Diverted (N)`,
                                                                       accuracy = .1)) %>%  
  dplyr::mutate(`Year` = "Overall")
 

df_diversion_outcome_year_overall_table <- rbind(df_diversion_outcome_year_overall,
                                                 df_diversion_outcome_overall)


### print table via kableextra
kable(df_diversion_outcome_year_overall_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(7, bold = TRUE)
```

<br>

## Table 12: Diversion Outcomes by Charge Type 

**Note:** Options for diversion outcomes include successful, unsuccessful with petition, and unsuccessful without petition. Most serious charge per complaint was selected.

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### by year
df_diversion_outcome_dai_overall <- df_analytic_complaints_disposition_caseload %>% 
  filter(intake_decision_clean=="Diverted") %>% 
  dplyr::group_by(dai) %>% 
   dplyr::summarise(`Unique Complaints Diverted (N)` = n_distinct(unique_complaint_id),
                    `Unique Complaints w/ Successful Diversion (N)` = n_distinct(unique_complaint_id[diversion_successful_flag==1]),
                    `Successful Diversion Rate (%)` = scales::percent(`Unique Complaints w/ Successful Diversion (N)`/`Unique Complaints Diverted (N)`,
                                                                       accuracy = .1),
                    `Unique Complaints w/ Unsuccessful Diversion without petition (N)` = n_distinct(unique_complaint_id[diversion_not_successful_no_petition_flag==1]),
                    `Unsuccessful Diversion without petition (%)` = scales::percent(`Unique Complaints w/ Unsuccessful Diversion without petition (N)`/`Unique Complaints Diverted (N)`,
                                                                       accuracy = .1),
                    `Unique Complaints w/ Unsuccessful Diversion (with petition) (N)` = n_distinct(unique_complaint_id[diversion_not_successful_petition_flag==1]),
                    `Unsuccessful Diversion with petition (%)` = scales::percent(`Unique Complaints w/ Unsuccessful Diversion (with petition) (N)`/`Unique Complaints Diverted (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Offense Description` = dai) %>% 
  arrange(desc(`Unique Complaints Diverted (N)`))

### overall
df_diversion_outcome_overall <- df_analytic_complaints_disposition_caseload %>% 
  filter(intake_decision_clean=="Diverted") %>% 
   dplyr::summarise(`Unique Complaints Diverted (N)` = n_distinct(unique_complaint_id),
                    `Unique Complaints w/ Successful Diversion (N)` = n_distinct(unique_complaint_id[diversion_successful_flag==1]),
                    `Successful Diversion Rate (%)` = scales::percent(`Unique Complaints w/ Successful Diversion (N)`/`Unique Complaints Diverted (N)`,
                                                                       accuracy = .1),
                    `Unique Complaints w/ Unsuccessful Diversion without petition (N)` = n_distinct(unique_complaint_id[diversion_not_successful_no_petition_flag==1]),
                    `Unsuccessful Diversion without petition (%)` = scales::percent(`Unique Complaints w/ Unsuccessful Diversion without petition (N)`/`Unique Complaints Diverted (N)`,
                                                                       accuracy = .1),
                    `Unique Complaints w/ Unsuccessful Diversion (with petition) (N)` = n_distinct(unique_complaint_id[diversion_not_successful_petition_flag==1]),
                    `Unsuccessful Diversion with petition (%)` = scales::percent(`Unique Complaints w/ Unsuccessful Diversion (with petition) (N)`/`Unique Complaints Diverted (N)`,
                                                                       accuracy = .1)) %>% 
  dplyr::mutate(`Offense Description` = "Overall")
 

df_diversion_outcome_dai_overall_table <- rbind(df_diversion_outcome_dai_overall,
                                                 df_diversion_outcome_overall) 


### print table via kableextra
kable(df_diversion_outcome_dai_overall_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(9, bold = TRUE)
```
<br><br>
