---
title: "Part II Analysis: CSU-Level Analysis"
format: html
---

**Data Sample:** 

* Juvenile intake complaints with intake dates from July 1, 2015 - June 30, 2021

* Dispositions – all dispositions for the intake complaints in the sample. 


*Cohort:* All complaints from 2016-2021  

<br>

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())

### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_analysis_analytic_data <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Data/VA/analysis/analytic"))

### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_viz <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Output/VA/r_viz_output"))
```

```{r include=FALSE}
### pull in virginia djj analytic files 

# ### read in df_analytic_complaints_disposition_caseload.rds analytic rds file 
# df_complaints_youth_intake_decision_csu <- read_rds(file.path(sharepoint_ojjdp_va_analysis_analytic_data,"df_complaints_youth_intake_decision_csu.rds"))
# 
# ### read in caseload_clean.rds analytic rds file 
# caseload_clean <- read_rds(file.path(sharepoint_ojjdp_va_analysis_analytic_data,"caseload_clean.rds"))

### read in df_analytic_complaints_disposition_caseload file for analysis
df_analytic_complaints_disposition_caseload <- read_rds(file.path(sharepoint_ojjdp_va_analysis_analytic_data,"df_analytic_complaints_disposition_caseload.rds"))
```

```{r include=FALSE,warning=FALSE,include=FALSE}
### create denominator -- unique complaint for entire sample
unique_complaints_sample_denom <- n_distinct(df_analytic_complaints_disposition_caseload$unique_complaint_id)

### create denominator -- unique youth for entire sample
unique_youth_sample_denom <- n_distinct(df_analytic_complaints_disposition_caseload$juvenile_number)
```

# Tables


## Table 1: Intake Decisions by Court Service Unit (CSU)

**Note:** I am currently coding the following intake decisions as 'Diverted': "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'), and "REQ'D TO PARTICIPATE-DIVERSION" (code of '7'). All other intake decisions are coded as "Not Diverted". See preliminary coding of intake decisions in `Intake Complaints, Intake Decision Descriptions` table on `codebook` page in `sample descriptives` tab

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_youth_intake_decision_table_csu <- df_analytic_complaints_disposition_caseload %>% 
  dplyr::group_by(csu) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`CSU` = csu)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_analytic_complaints_disposition_caseload %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>%  
  ungroup() %>% 
  dplyr::mutate(`CSU` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_csu_final <- rbind(df_complaints_youth_intake_decision_table_csu,
                                                             df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_csu_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(33, bold = TRUE)
```

<br>

## Table 2: Intake Decisions by Court Service Unit (CSU) Region

**Note:** I am currently coding the following intake decisions as 'Diverted': "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'), and "REQ'D TO PARTICIPATE-DIVERSION" (code of '7'). All other intake decisions are coded as "Not Diverted". See preliminary coding of intake decisions in `Intake Complaints, Intake Decision Descriptions` table on `codebook` page in `sample descriptives` tab

See CSU regions here: https://www.djj.virginia.gov/pages/community/court-service-units.htm

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_youth_intake_decision_table_csu_region <- df_analytic_complaints_disposition_caseload %>% 
  dplyr::group_by(csu_region) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`CSU Region` = csu_region)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_analytic_complaints_disposition_caseload %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`CSU Region` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_csu_region_final <- rbind(df_complaints_youth_intake_decision_table_csu_region,
                                                             df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_csu_region_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 3: Disposition Outcomes by Court Service Unit (CSU) Region

**BUSINESS RULE:** Filtering on non-missing dispositions for this analysis

Note: The preliminary options for grouping dispositions that I am using are: Detention, Commitment, Probation/Supervision, Deferral, Community Service, Fine, No further action/none, Restitution, Other. See the `Disposition, Preliminary Disposition Groupings` table on the `codebook` page in the `sample descriptives` tab for a full list of each disposition and I've grouped it. 

See CSU regions here: https://www.djj.virginia.gov/pages/community/court-service-units.htm

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_disposition_outcome_table_csu_region <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(dispo_description_clean)) %>% 
  dplyr::group_by(csu_region) %>% 
     dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Disposed Complaints (column %)` = scales::percent(`All Disposed Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Detention (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Detention"]),
                   `Detention (row %)` = scales::percent(`Detention (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Commitment (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Commitment"]),
                   `Commitment (row %)` = scales::percent(`Commitment (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row %)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Deferral (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Deferral"]),
                   `Deferral (row %)` = scales::percent(`Deferral (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Community Service (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Community Service"]),
                   `Community Service (row %)` = scales::percent(`Community Service (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Fine (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Fine"]),
                   `Fine (row %)` = scales::percent(`Fine (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `No further action/none (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="No further action/none"]),
                   `No further action/none (row %)` = scales::percent(`No further action/none (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Restitution (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Restitution"]),
                   `Restitution (row %)` = scales::percent(`Restitution (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`CSU Region` = csu_region)  

### unique complaints statewide
df_complaints_disposition_outcome_table_overall <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(dispo_description_clean)) %>% 
   dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Disposed Complaints (column %)` = scales::percent(`All Disposed Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Detention (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Detention"]),
                   `Detention (row %)` = scales::percent(`Detention (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Commitment (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Commitment"]),
                   `Commitment (row %)` = scales::percent(`Commitment (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row %)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Deferral (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Deferral"]),
                   `Deferral (row %)` = scales::percent(`Deferral (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Community Service (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Community Service"]),
                   `Community Service (row %)` = scales::percent(`Community Service (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Fine (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Fine"]),
                   `Fine (row %)` = scales::percent(`Fine (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `No further action/none (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="No further action/none"]),
                   `No further action/none (row %)` = scales::percent(`No further action/none (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Restitution (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Restitution"]),
                   `Restitution (row %)` = scales::percent(`Restitution (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`CSU Region` = "Overall") 

### combine two dataframes for table
df_complaints_disposition_outcome_table_csu_region_final <- rbind(df_complaints_disposition_outcome_table_csu_region,
                                                             df_complaints_disposition_outcome_table_overall)


### print table via kableextra
kable(df_complaints_disposition_outcome_table_csu_region_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 4: Disposition Outcomes by Court Service Unit (CSU)

**BUSINESS RULE:** Filtering on non-missing dispositions for this analysis

Note: The preliminary options for grouping dispositions that I am using are: Detention, Commitment, Probation/Supervision, Deferral, Community Service, Fine, No further action/none, Restitution, Other. See the `Disposition, Preliminary Disposition Groupings` table on the `codebook` page in the `sample descriptives` tab for a full list of each disposition and I've grouped it. 

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_disposition_outcome_table_csu <- df_analytic_complaints_disposition_caseload %>% 
    filter(!is.na(dispo_description_clean)) %>% 
  dplyr::group_by(csu) %>% 
     dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Disposed Complaints (column %)` = scales::percent(`All Disposed Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Detention (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Detention"]),
                   `Detention (row %)` = scales::percent(`Detention (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Commitment (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Commitment"]),
                   `Commitment (row %)` = scales::percent(`Commitment (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row %)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Deferral (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Deferral"]),
                   `Deferral (row %)` = scales::percent(`Deferral (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Community Service (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Community Service"]),
                   `Community Service (row %)` = scales::percent(`Community Service (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Fine (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Fine"]),
                   `Fine (row %)` = scales::percent(`Fine (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `No further action/none (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="No further action/none"]),
                   `No further action/none (row %)` = scales::percent(`No further action/none (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Restitution (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Restitution"]),
                   `Restitution (row %)` = scales::percent(`Restitution (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`CSU` = csu)  

### unique complaints statewide
df_complaints_disposition_outcome_table_overall <- df_analytic_complaints_disposition_caseload %>% 
    filter(!is.na(dispo_description_clean)) %>% 
    dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Disposed Complaints (column %)` = scales::percent(`All Disposed Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Detention (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Detention"]),
                   `Detention (row %)` = scales::percent(`Detention (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Commitment (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Commitment"]),
                   `Commitment (row %)` = scales::percent(`Commitment (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row %)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Deferral (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Deferral"]),
                   `Deferral (row %)` = scales::percent(`Deferral (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Community Service (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Community Service"]),
                   `Community Service (row %)` = scales::percent(`Community Service (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Fine (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Fine"]),
                   `Fine (row %)` = scales::percent(`Fine (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `No further action/none (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="No further action/none"]),
                   `No further action/none (row %)` = scales::percent(`No further action/none (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Restitution (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Restitution"]),
                   `Restitution (row %)` = scales::percent(`Restitution (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`CSU` = "Overall") 

### combine two dataframes for table
df_complaints_disposition_outcome_table_csu_final <- rbind(df_complaints_disposition_outcome_table_csu,
                                                             df_complaints_disposition_outcome_table_overall)


### print table via kableextra
kable(df_complaints_disposition_outcome_table_csu_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(33, bold = TRUE)
```

<br>

## Table 5: Average Length of Stay on Diversion by CSU

Both measures of LOS on diversion are calculated by DJJ and provided in the `caseload` file -- see codebook page for more information. The two LOS measures are the "Number of days on the workload status "Diversion at Intake" and the "Number of days on the workload status "Diversion Beyond 90 Days"

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

###  mean and median diversion lengths of stay by race/ethnicity
df_diversion_csu_los <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(div_at_int)==TRUE | !is.na(div_bey_90)==TRUE) %>% 
  group_by(csu) %>% 
  dplyr::summarise(`Mean Diversion LOS (at intake)` = mean(div_at_int,
                                           na.rm=TRUE),
                   `Median Diversion LOS (at intake)` = median(div_at_int,
                                           na.rm=TRUE),
                   `Mean Diversion LOS (beyond 90 days)` = mean(div_bey_90,
                                           na.rm=TRUE),
                   `Median Diversion LOS (beyond 90 days)` = median(div_bey_90,
                                           na.rm=TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`CSU` = csu)

### overall mean and median diversion lengths of stay
df_diversion_overall_los <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(div_at_int)==TRUE | !is.na(div_bey_90)==TRUE) %>% 
  dplyr::summarise(`Mean Diversion LOS (at intake)` = mean(div_at_int,
                                           na.rm=TRUE),
                   `Median Diversion LOS (at intake)` = median(div_at_int,
                                           na.rm=TRUE),
                   `Mean Diversion LOS (beyond 90 days)` = mean(div_bey_90,
                                           na.rm=TRUE),
                   `Median Diversion LOS (beyond 90 days)` = median(div_bey_90,
                                           na.rm=TRUE)) %>% 
  mutate(`CSU` = "Overall")
 
### combine two dataframes for table
df_diversion_csu_los_final <- rbind(df_diversion_csu_los,
                                                             df_diversion_overall_los)

### print table via kableextra
kable(df_diversion_csu_los_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(33, bold = TRUE)
```

<br>

## Table 6a: Intake Decisions by Offense Type (most serious offense is felony)

Most serious offense = "Felony against Persons","Felony Weapons and Felony Narcotics Distribution","Other Felony"

**Note:** I am currently coding the following intake decisions as 'Diverted': "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'), and "REQ'D TO PARTICIPATE-DIVERSION" (code of '7'). All other intake decisions are coded as "Not Diverted". See preliminary coding of intake decisions in `Intake Complaints, Intake Decision Descriptions` table on `codebook` page in `sample descriptives` tab

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_youth_intake_decision_table_offense_felony <- df_analytic_complaints_disposition_caseload %>% 
  filter(dai%in%c("Felony against Persons","Felony Weapons and Felony Narcotics Distribution","Other Felony")) %>% 
  dplyr::group_by(csu) %>% 
    dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`CSU` = csu)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_analytic_complaints_disposition_caseload %>% 
    filter(dai%in%c("Felony against Persons","Felony Weapons and Felony Narcotics Distribution","Other Felony")) %>% 
   dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`CSU` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_offense_felony_final <- rbind(df_complaints_youth_intake_decision_table_offense_felony,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_offense_felony_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(33, bold = TRUE)
```

<br>


## Table 6b: Intake Decisions by Offense Type (most serious offense is misdemeanor)

Most serious offense = "Class 1 Misdemeanor Against Persons","Other Class 1 Misdemeanor"

**Note:** I am currently coding the following intake decisions as 'Diverted': "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'), and "REQ'D TO PARTICIPATE-DIVERSION" (code of '7'). All other intake decisions are coded as "Not Diverted". See preliminary coding of intake decisions in `Intake Complaints, Intake Decision Descriptions` table on `codebook` page in `sample descriptives` tab

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_youth_intake_decision_table_offense_misd <- df_analytic_complaints_disposition_caseload %>% 
  filter(dai%in%c("Class 1 Misdemeanor Against Persons","Other Class 1 Misdemeanor")) %>% 
  dplyr::group_by(csu) %>% 
   dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`CSU` = csu)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_analytic_complaints_disposition_caseload %>% 
  filter(dai%in%c("Class 1 Misdemeanor Against Persons","Other Class 1 Misdemeanor")) %>% 
    dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`CSU` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_offense_misd_final <- rbind(df_complaints_youth_intake_decision_table_offense_misd,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_offense_misd_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(33, bold = TRUE)
```

<br>

## Table 6c: Intake Decisions by Offense Type (most serious offense is status)

Most serious offense = "Status Offense"

**Note:** I am currently coding the following intake decisions as 'Diverted': "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'), and "REQ'D TO PARTICIPATE-DIVERSION" (code of '7'). All other intake decisions are coded as "Not Diverted". See preliminary coding of intake decisions in `Intake Complaints, Intake Decision Descriptions` table on `codebook` page in `sample descriptives` tab

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_youth_intake_decision_table_offense_status <- df_analytic_complaints_disposition_caseload %>% 
  filter(dai%in%c("Status Offense")) %>% 
  dplyr::group_by(csu) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`CSU` = csu)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_analytic_complaints_disposition_caseload %>% 
  filter(dai%in%c("Status Offense")) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`CSU` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_offense_status_final <- rbind(df_complaints_youth_intake_decision_table_offense_status,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_offense_status_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(33, bold = TRUE)
```

<br>

## Table 7: Disposition Outcomes by YASI Risk Level

**TO DO:** Double check that I’m using correct YASI assessment for dispo exploration (does it matter if it is initial, case closure, etc.?)


**BUSINESS RULE:** Filtering on non-missing dispositions and non-missing YASI values for this analysis


Note: The preliminary options for grouping dispositions that I am using are: Detention, Commitment, Probation/Supervision, Deferral, Community Service, Fine, No further action/none, Restitution, Other. See the `Disposition, Preliminary Disposition Groupings` table on the `codebook` page in the `sample descriptives` tab for a full list of each disposition and I've grouped it. 

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_disposition_outcome_table_risk_score <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(dispo_description_clean),
         !is.na(risk_level_clean)) %>% 
  dplyr::group_by(csu) %>% 
  dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row % of all dispositions)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision, Low Risk (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision" & risk_level_clean=="Low"]),
                   `Probation/Supervision, Low Risk (row % of probation/supervision)` = scales::percent(`Probation/Supervision, Low Risk (N)`/`Probation/Supervision (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision, Medium Risk (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision" & risk_level_clean=="Medium"]),
                   `Probation/Supervision, Medium Risk (row % of probation/supervision)` = scales::percent(`Probation/Supervision, Medium Risk (N)`/`Probation/Supervision (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision, High Risk (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision" & risk_level_clean=="High"]),
                   `Probation/Supervision, High Risk (row % of probation/supervision)` = scales::percent(`Probation/Supervision, High Risk (N)`/`Probation/Supervision (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`CSU` = csu) 

### unique complaints statewide
df_complaints_disposition_outcome_table_overall <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(dispo_description_clean),
         !is.na(risk_level_clean)) %>% 
  dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row % of all dispositions)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision, Low Risk (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision" & risk_level_clean=="Low"]),
                   `Probation/Supervision, Low Risk (row % of probation/supervision)` = scales::percent(`Probation/Supervision, Low Risk (N)`/`Probation/Supervision (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision, Medium Risk (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision" & risk_level_clean=="Medium"]),
                   `Probation/Supervision, Medium Risk (row % of probation/supervision)` = scales::percent(`Probation/Supervision, Medium Risk (N)`/`Probation/Supervision (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision, High Risk (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision" & risk_level_clean=="High"]),
                   `Probation/Supervision, High Risk (row % of probation/supervision)` = scales::percent(`Probation/Supervision, High Risk (N)`/`Probation/Supervision (N)`,
                                                                       accuracy = .1)) %>% 
  dplyr::mutate(`CSU` = "Overall") 

### combine two dataframes for table
df_complaints_disposition_outcome_table_risk_score_final_csu <- rbind(df_complaints_disposition_outcome_table_risk_score,df_complaints_disposition_outcome_table_overall)


### print table via kableextra
kable(df_complaints_disposition_outcome_table_risk_score_final_csu, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(33, bold = TRUE)
```

<br>

## Table 7: Disposition Outcomes by YASI Risk Level

**TO DO:** Double check that I’m using correct YASI assessment for dispo exploration (does it matter if it is initial, case closure, etc.?)


**BUSINESS RULE:** Filtering on non-missing dispositions and non-missing YASI values for this analysis

         
Note: The preliminary options for grouping dispositions that I am using are: Detention, Commitment, Probation/Supervision, Deferral, Community Service, Fine, No further action/none, Restitution, Other. See the `Disposition, Preliminary Disposition Groupings` table on the `codebook` page in the `sample descriptives` tab for a full list of each disposition and I've grouped it. 

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_disposition_outcome_table_risk_score <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(dispo_description_clean),
         !is.na(risk_level_clean)) %>% 
  dplyr::group_by(csu) %>% 
  dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row % of all dispositions)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision, Low Risk (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision" & risk_level_clean=="Low"]),
                   `Probation/Supervision, Low Risk (row % of probation/supervision)` = scales::percent(`Probation/Supervision, Low Risk (N)`/`Probation/Supervision (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision, Medium Risk (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision" & risk_level_clean=="Medium"]),
                   `Probation/Supervision, Medium Risk (row % of probation/supervision)` = scales::percent(`Probation/Supervision, Medium Risk (N)`/`Probation/Supervision (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision, High Risk (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision" & risk_level_clean=="High"]),
                   `Probation/Supervision, High Risk (row % of probation/supervision)` = scales::percent(`Probation/Supervision, High Risk (N)`/`Probation/Supervision (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`CSU` = csu) 

### unique complaints statewide
df_complaints_disposition_outcome_table_overall <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(dispo_description_clean),
         !is.na(risk_level_clean)) %>% 
  dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row % of all dispositions)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision, Low Risk (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision" & risk_level_clean=="Low"]),
                   `Probation/Supervision, Low Risk (row % of probation/supervision)` = scales::percent(`Probation/Supervision, Low Risk (N)`/`Probation/Supervision (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision, Medium Risk (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision" & risk_level_clean=="Medium"]),
                   `Probation/Supervision, Medium Risk (row % of probation/supervision)` = scales::percent(`Probation/Supervision, Medium Risk (N)`/`Probation/Supervision (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision, High Risk (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision" & risk_level_clean=="High"]),
                   `Probation/Supervision, High Risk (row % of probation/supervision)` = scales::percent(`Probation/Supervision, High Risk (N)`/`Probation/Supervision (N)`,
                                                                       accuracy = .1)) %>% 
  dplyr::mutate(`CSU` = "Overall") 

### combine two dataframes for table
df_complaints_disposition_outcome_table_risk_score_final_csu <- rbind(df_complaints_disposition_outcome_table_risk_score,df_complaints_disposition_outcome_table_overall)


### print table via kableextra
kable(df_complaints_disposition_outcome_table_risk_score_final_csu, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(33, bold = TRUE)
```

<br>

## Table 8: Intake Decisions by Petitioner Type/Referral Source (as % of complaints) (petitioned and diverted only)

**Note:** I am currently coding the following intake decisions as 'Diverted': "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'), and "REQ'D TO PARTICIPATE-DIVERSION" (code of '7'). All other intake decisions are coded as "Not Diverted". See preliminary coding of intake decisions in `Intake Complaints, Intake Decision Descriptions` table on `codebook` page in `sample descriptives` tab

**Also:** for this CSU-level analysis, I've further collapsed the petitioner/referral source categories for ease of interpretation. Here are the categories I'm currently using: school (including SRO), law enforcement (including probation officer), and other

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_youth_intake_decision_table_pet_desc_csu <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(referral_source_clean_csu_level_categories)==TRUE) %>% 
  dplyr::group_by(csu) %>% 
   dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints, School (N)` = n_distinct(unique_complaint_id[referral_source_clean_csu_level_categories=="School"]),
                   `All Complaints, School (row %)` = scales::percent(`All Complaints, School (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `All Complaints, Law Enforcement (N)` = n_distinct(unique_complaint_id[referral_source_clean_csu_level_categories=="Law Enforcement"]),
                  `All Complaints, Law Enforcement (row %)` = scales::percent(`All Complaints, Law Enforcement (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   
                   `All Complaints, Other (N)` = n_distinct(unique_complaint_id[referral_source_clean_csu_level_categories=="Other"]),
                  `All Complaints, Other (row %)` = scales::percent(`All Complaints, Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                  `Complaints Petitioned, School (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned" & referral_source_clean_csu_level_categories=="School"])/`All Complaints (N)`,
                                                                       accuracy = .1),
                  `Complaints Petitioned, Law Enforcement (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned" & referral_source_clean_csu_level_categories=="Law Enforcement"])/`All Complaints (N)`,
                                                                       accuracy = .1),
                  `Complaints Petitioned, Other (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned" & referral_source_clean_csu_level_categories=="Other"])/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted, School (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Diverted" & referral_source_clean_csu_level_categories=="School"])/`All Complaints (N)`,
                                                                       accuracy = .1),
                  `Complaints Diverted, Law Enforcement (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Diverted" & referral_source_clean_csu_level_categories=="Law Enforcement"])/`All Complaints (N)`,
                                                                       accuracy = .1),
                  `Complaints Diverted, Other (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Diverted" & referral_source_clean_csu_level_categories=="Other"])/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`CSU` = csu) 

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(referral_source_clean_csu_level_categories)==TRUE) %>% 
   dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints, School (N)` = n_distinct(unique_complaint_id[referral_source_clean_csu_level_categories=="School"]),
                   `All Complaints, School (row %)` = scales::percent(`All Complaints, School (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `All Complaints, Law Enforcement (N)` = n_distinct(unique_complaint_id[referral_source_clean_csu_level_categories=="Law Enforcement"]),
                  `All Complaints, Law Enforcement (row %)` = scales::percent(`All Complaints, Law Enforcement (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   
                   `All Complaints, Other (N)` = n_distinct(unique_complaint_id[referral_source_clean_csu_level_categories=="Other"]),
                  `All Complaints, Other (row %)` = scales::percent(`All Complaints, Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                  `Complaints Petitioned, School (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned" & referral_source_clean_csu_level_categories=="School"])/`All Complaints (N)`,
                                                                       accuracy = .1),
                  `Complaints Petitioned, Law Enforcement (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned" & referral_source_clean_csu_level_categories=="Law Enforcement"])/`All Complaints (N)`,
                                                                       accuracy = .1),
                  `Complaints Petitioned, Other (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned" & referral_source_clean_csu_level_categories=="Other"])/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted, School (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Diverted" & referral_source_clean_csu_level_categories=="School"])/`All Complaints (N)`,
                                                                       accuracy = .1),
                  `Complaints Diverted, Law Enforcement (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Diverted" & referral_source_clean_csu_level_categories=="Law Enforcement"])/`All Complaints (N)`,
                                                                       accuracy = .1),
                  `Complaints Diverted, Other (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Diverted" & referral_source_clean_csu_level_categories=="Other"])/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  dplyr::mutate(`CSU` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_pet_desc_csu_final <- rbind(df_complaints_youth_intake_decision_table_pet_desc_csu,
                                                             df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_pet_desc_csu_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(33, bold = TRUE)
```

<br>

## Table 9: TO DO: Intake Decisions by Petitioner Type/Referral Source (per 10k youth by CSU) (petitioned and diverted only)


**Note:** I am currently coding the following intake decisions as 'Diverted': "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'), and "REQ'D TO PARTICIPATE-DIVERSION" (code of '7'). All other intake decisions are coded as "Not Diverted". See preliminary coding of intake decisions in `Intake Complaints, Intake Decision Descriptions` table on `codebook` page in `sample descriptives` tab

**Also:** for this CSU-level analysis, I've further collapsed the petitioner/referral source categories for ease of interpretation. Here are the categories I'm currently using: school (including SRO), law enforcement (including probation officer), and other

```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_youth_intake_decision_table_pet_desc_csu <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(referral_source_clean_csu_level_categories)==TRUE) %>% 
  dplyr::group_by(csu) %>% 
   dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints, School (N)` = n_distinct(unique_complaint_id[referral_source_clean_csu_level_categories=="School"]),
                   `All Complaints, School (row %)` = scales::percent(`All Complaints, School (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `All Complaints, Law Enforcement (N)` = n_distinct(unique_complaint_id[referral_source_clean_csu_level_categories=="Law Enforcement"]),
                  `All Complaints, Law Enforcement (row %)` = scales::percent(`All Complaints, Law Enforcement (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   
                   `All Complaints, Other (N)` = n_distinct(unique_complaint_id[referral_source_clean_csu_level_categories=="Other"]),
                  `All Complaints, Other (row %)` = scales::percent(`All Complaints, Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                  `Complaints Petitioned, School (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned" & referral_source_clean_csu_level_categories=="School"])/`All Complaints (N)`,
                                                                       accuracy = .1),
                  `Complaints Petitioned, Law Enforcement (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned" & referral_source_clean_csu_level_categories=="Law Enforcement"])/`All Complaints (N)`,
                                                                       accuracy = .1),
                  `Complaints Petitioned, Other (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned" & referral_source_clean_csu_level_categories=="Other"])/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted, School (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Diverted" & referral_source_clean_csu_level_categories=="School"])/`All Complaints (N)`,
                                                                       accuracy = .1),
                  `Complaints Diverted, Law Enforcement (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Diverted" & referral_source_clean_csu_level_categories=="Law Enforcement"])/`All Complaints (N)`,
                                                                       accuracy = .1),
                  `Complaints Diverted, Other (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Diverted" & referral_source_clean_csu_level_categories=="Other"])/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`CSU` = csu) 

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(referral_source_clean_csu_level_categories)==TRUE) %>% 
   dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints, School (N)` = n_distinct(unique_complaint_id[referral_source_clean_csu_level_categories=="School"]),
                   `All Complaints, School (row %)` = scales::percent(`All Complaints, School (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `All Complaints, Law Enforcement (N)` = n_distinct(unique_complaint_id[referral_source_clean_csu_level_categories=="Law Enforcement"]),
                  `All Complaints, Law Enforcement (row %)` = scales::percent(`All Complaints, Law Enforcement (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   
                   `All Complaints, Other (N)` = n_distinct(unique_complaint_id[referral_source_clean_csu_level_categories=="Other"]),
                  `All Complaints, Other (row %)` = scales::percent(`All Complaints, Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                  `Complaints Petitioned, School (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned" & referral_source_clean_csu_level_categories=="School"])/`All Complaints (N)`,
                                                                       accuracy = .1),
                  `Complaints Petitioned, Law Enforcement (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned" & referral_source_clean_csu_level_categories=="Law Enforcement"])/`All Complaints (N)`,
                                                                       accuracy = .1),
                  `Complaints Petitioned, Other (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned" & referral_source_clean_csu_level_categories=="Other"])/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted, School (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Diverted" & referral_source_clean_csu_level_categories=="School"])/`All Complaints (N)`,
                                                                       accuracy = .1),
                  `Complaints Diverted, Law Enforcement (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Diverted" & referral_source_clean_csu_level_categories=="Law Enforcement"])/`All Complaints (N)`,
                                                                       accuracy = .1),
                  `Complaints Diverted, Other (row %)` = scales::percent(n_distinct(unique_complaint_id[intake_decision_clean=="Diverted" & referral_source_clean_csu_level_categories=="Other"])/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  dplyr::mutate(`CSU` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_pet_desc_csu_final <- rbind(df_complaints_youth_intake_decision_table_pet_desc_csu,
                                                             df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_pet_desc_csu_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(33, bold = TRUE)
```

<br><br>

# Visuals

```{r include=FALSE,message=FALSE,warning=FALSE}
### read in census/acs api key from environmnent
### this allows us to pull census/acs data via the tidycensus package
readRenviron("~/.Renviron")

### read in va county-level shape file and keep geometry for mapping
### from kyle walker/tidycensus: specify cb = TRUE which defaults to the Census Bureau’s cartographic boundary shapefiles. Cartographic boundary shapefiles are preferred to the core TIGER/Line shapefiles in tidycensus as their smaller size speeds up processing and because they are pre-clipped to the US coastline.
va_county_shoreline_clipped <- get_acs(
  geography = "county",
  variables = "B19013_001",
  state = "VA",
  year = 2020,
  geometry = TRUE,
  cb = TRUE
  ) %>%
  clean_names() %>%
  # mutate(county = word(NAME, 1)) %>% 
  group_by(geoid) %>%
  summarize(geometry = st_union(geometry)) %>%
  ungroup() %>% 
  mutate(state = "VA")

# ### use group_by and st_union to create statewide polygon using the county-level geography
# ### we'll use this shapefile for a state border when mapping
# va_state_shoreline_clipped <- va_county_shoreline_clipped %>%
#   group_by(state) %>%
#   summarize(geometry = st_union(geometry)) %>%
#   ungroup()

### read in va county-level shape file with fips codes to use as lookup table
va_county_shape <- read_sf("C:\\Users\\abyrum\\OneDrive - The Council of State Governments\\Geospatial_Mapping\\US County Geo Data\\tl_2019_us_county\\tl_2019_us_county.shp") %>%
  clean_names() %>%
  filter(statefp=="51") %>% ### filter by state fip code
  dplyr::select(county=name,
               county_fip=countyfp,
               geoid)

### lose geometry as this is just a lookup table
va_county_lookup <- as.data.frame(va_county_shape) %>% 
    dplyr::select(-(geometry))

### now join va_county_shoreline_clipped and va_county_lookup
va_county_shoreline_clipped_final <- left_join(va_county_shoreline_clipped,
                                               va_county_lookup,
                                               by = "geoid")


```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set constants for mapping
default_font_color <- "#4e4d47"
default_font_family <- "Franklin Gothic Book"
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### create static map theme (based on https://timogrossenbacher.ch/2019/04/bivariate-maps-with-ggplot2-and-sf/)
theme_map <- function(...) {
  theme_minimal() +
  theme(
    text = element_text(family = default_font_family,
                        color = default_font_color),
    # remove all axes
    axis.line = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    # add a subtle grid
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # borders and margins
    plot.margin = unit(c(.5, .5, .2, .5), "cm"),
    panel.border = element_blank(),
    panel.spacing = unit(c(-.1, 0.2, .2, 0.2), "cm"),
    # titles
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 9, hjust = 0,
                               color = default_font_color),
    plot.title = element_text(size = 15, hjust = 0.5,
                              color = default_font_color),
    # plot.subtitle = element_text(size = 10, hjust = 0.5,
    #                              color = default_font_color,
    #                              margin = margin(b = -0.1,
    #                                              t = -0.1,
    #                                              l = 2,
    #                                              unit = "cm"),
    #                              debug = F),
    # # captions
    # plot.caption = element_text(size = 7,
    #                             hjust = .5,
    #                             margin = margin(t = 0.2,
    #                                             b = 0,
    #                                             unit = "cm"),
    #                             color = default_font_color),
    ...
  )
}
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_analysis_geo_data <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Data/VA/analysis/geo"))

# ### group diversion rate and geometry by county
# df_complaints_youth_intake_decision_county_to_join <- df_analytic_complaints_disposition_caseload %>%
#   mutate(fips_code = ifelse(fips_code=="X71",
#                             "071",fips_code),
#          fips_code = ifelse(fips_code=="X21",
#                             "021",fips_code)) %>% 
#   dplyr::group_by(fips_code) %>%
#   dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
#                    `Complaints Diverted (row %)` = n_distinct(unique_complaint_id[intake_diverted_flag=="Yes"])/`All Complaints (N)`) %>%
#   ungroup()
# 
# df_county_level_intake_summary_geo <- left_join(va_county_shoreline_clipped_final,
#                                                      df_complaints_youth_intake_decision_county_to_join,
#                                                      by = c("county_fip"="fips_code"))
# 
# ### write out as rds file (to save time)
# write_rds(df_county_level_intake_summary_geo,
#           file.path(sharepoint_ojjdp_va_analysis_geo_data,"df_county_level_intake_summary_geo.rds"))

### read in rds file for diversion rate and geometry by county
df_county_level_intake_summary_geo <- read_rds(file.path(sharepoint_ojjdp_va_analysis_geo_data,"df_county_level_intake_summary_geo.rds"))

# ### group diversion rate and geometry by csu
# df_csu_level_intake_summary_geo <- df_county_level_intake_complaints_summary_geo %>% 
#   dplyr::group_by(csu) %>% 
#   dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
#                    `Complaints Diverted (row %)` = n_distinct(unique_complaint_id[diverted_flag=="Yes"])/`All Complaints (N)`,
#                    geometry = st_union(geometry)) %>% 
#   ungroup() 
# 
# ### write out as rds file (to save time)
# write_rds(df_csu_level_intake_summary_geo,
#           file.path(sharepoint_ojjdp_va_analysis_geo_data,"df_csu_level_intake_summary_geo.rds"))

### read in rds file for diversion rate and geometry by csu
df_csu_level_intake_summary_geo <- read_rds(file.path(sharepoint_ojjdp_va_analysis_geo_data,"df_csu_level_intake_summary_geo.rds"))

# ### group diversion rate and geometry by csu region
# ### we will initially use this file to add a region layer/label to the map
# df_csu_region_level_intake_summary_geo <- df_county_level_intake_complaints_summary_geo %>% 
#   dplyr::group_by(csu_region) %>% 
#   dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
#                    `Complaints Diverted (row %)` = n_distinct(unique_complaint_id[diverted_flag=="Yes"])/`All Complaints (N)`,
#                    geometry = st_union(geometry)) %>% 
#   ungroup() 
# 
# ### write out as rds file (to save time)
# write_rds(df_csu_region_level_intake_summary_geo,
#           file.path(sharepoint_ojjdp_va_analysis_geo_data,"df_csu_region_level_intake_summary_geo.rds"))

### read in rds file for diversion rate and geometry by csu region
df_csu_region_level_intake_summary_geo <- read_rds(file.path(sharepoint_ojjdp_va_analysis_geo_data,"df_csu_region_level_intake_summary_geo.rds"))

```


## Figure 1: % of all Complaints Diverted by County

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 100%

### create quantiles object
no_classes <- 4

### extract quantiles from var we're mapping
quantiles <- df_county_level_intake_summary_geo %>%
  pull(`Complaints Diverted (row %)`) %>%
  quantile(probs = seq(0, 1, length.out = no_classes + 1), na.rm=TRUE) %>%
  as.vector() 

### make labels for map's legend
label_diversion_rate <- c("27% to 56%","20% to 27%","13% to 20%","2% to 13%")

### create a new variable with the specified quantiles
df_county_level_intake_summary_geo_to_map <- df_county_level_intake_summary_geo %>%
  mutate(percent_diversion_quartile = cut(-`Complaints Diverted (row %)`,
                               breaks = -quantiles,
                               right = TRUE,
                               labels = label_diversion_rate,
                               include.lowest = T)) 


### map via ggplot 
ggplot(
  # define main data source
  data = df_county_level_intake_summary_geo_to_map
) +
  scale_alpha(name = "",
              range = c(0.6, 0),
              guide = F) + # suppress legend
  # add main fill aesthetic
  geom_sf(
    mapping = aes(
      fill = percent_diversion_quartile
      ),
    color = "white",
    size = 0.1
  ) +
  #   scale_fill_distiller(
  #   labels = scales::percent_format(accuracy=1),
  #   direction = 1,
  #   name = "% Bookings with Drug/Alcohol\n Charges"
  # ) +
  ### use jr palette here
    # scale_colour_gradientn(colours = c("#D7EBF1","#AFD6E2","#87C2D4","#2F7084","#1F4A58")) +
 scale_fill_manual(
    values = c("#1F4A58","#2F7084","#87C2D4","#AFD6E2"),
    name = "% of Complaints Diverted",
    na.value = "grey50",
    guide = guide_legend(
     keyheight = unit(7.5, units = "mm"),
     title.position = "top",
     reverse = F # display highest on top
  )) +
  # use white stroke borders for county boundaries
  geom_sf(
    data = df_county_level_intake_summary_geo_to_map,
    fill = "transparent",
    color = "white",
    size = .05
  )  +
  # use additional csu-level shapefile for region border
  geom_sf(
    data = df_csu_level_intake_summary_geo,
    fill = "transparent",
    color = "white",
    size = .65
  )  +
 # geom_label(
 #     data = df_csu_region_level_intake_summary_geo,
 #     aes(geometry = geometry,
 #         label = paste0(csu_region,"\n"," Region")),
 # family = "Franklin Gothic Demi",
 # color = "gray25",
 # size = 2.25,
 # fontface = "bold",
 # stat = "sf_coordinates") +
  # guides(fill = guide_colorbar(barwidth = 8),
  #          direction = "horizontal",
  #     barheight = unit(2, units = "mm"),
  #     barwidth = unit(50, units = "mm"),
  #     draw.ulim = F,
  #     title.position = 'top',
  #     # some shifting around
  #     title.hjust = 0.5,
  #     label.hjust = 0.5) +
  labs(
    title = NULL,
    subtitle = NULL,
    x = NULL,
    y = NULL,
    fill = NULL,
    caption = NULL
  ) +
  # add theme
  theme_map() 
# +
#   theme(
#     # plot.margin = margin(),
#     panel.grid = element_blank(),
#     axis.text.x = element_blank(),
#     axis.text.y = element_blank(),
#     legend.position = "bottom",
#     legend.justification = c(0.5, 0.5),
#     legend.text = element_text(size = 11)) 


# ### write out
# ggsave(
#     filename = file.path(sp_viz_output_path, "charge_type_percent_drug_alcohol_by_jail_non_pc.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Figure 2: % of all Complaints Diverted by Court Service Unit (CSU)

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 100%

### create quantiles object
no_classes <- 4

### extract quantiles from var we're mapping
quantiles <- df_csu_level_intake_summary_geo %>%
  pull(`Complaints Diverted (row %)`) %>%
  quantile(probs = seq(0, 1, length.out = no_classes + 1), na.rm=TRUE) %>%
  as.vector() 

### make labels for map's legend
label_diversion_rate <- c("25% to 34%","18% to 25%","12% to 18%","5% to 12%")

### create a new variable with the specified quantiles
df_csu_level_intake_summary_geo_to_map <- df_csu_level_intake_summary_geo %>%
  mutate(percent_diversion_quartile = cut(-`Complaints Diverted (row %)`,
                               breaks = -quantiles,
                               right = TRUE,
                               labels = label_diversion_rate,
                               include.lowest = T)) 


### map via ggplot 
ggplot(
  # define main data source
  data = df_csu_level_intake_summary_geo_to_map
) +
  scale_alpha(name = "",
              range = c(0.6, 0),
              guide = F) + # suppress legend
  # add main fill aesthetic
  geom_sf(
    mapping = aes(
      fill = percent_diversion_quartile
      ),
    color = "white",
    size = 0.1
  ) +
  #   scale_fill_distiller(
  #   labels = scales::percent_format(accuracy=1),
  #   direction = 1,
  #   name = "% Bookings with Drug/Alcohol\n Charges"
  # ) +
  ### use jr palette here
    # scale_colour_gradientn(colours = c("#D7EBF1","#AFD6E2","#87C2D4","#2F7084","#1F4A58")) +
 scale_fill_manual(
    values = c("#1F4A58","#2F7084","#87C2D4","#AFD6E2"),
    name = "% of Complaints Diverted",
    na.value = "grey50",
    guide = guide_legend(
     keyheight = unit(7.5, units = "mm"),
     title.position = "top",
     reverse = F # display highest on top
  )) +
  # use white stroke borders for county boundaries
  geom_sf(
    data = df_county_level_intake_summary_geo_to_map,
    fill = "transparent",
    color = "white",
    size = .05
  ) +
  # use white stroke borders for csu boundaries
  geom_sf(
    data = df_csu_level_intake_summary_geo_to_map,
    fill = "transparent",
    color = "white",
    size = .65
  )  +
  # use additional csu region-level shapefile for region border
  # geom_sf(
  #   data = df_csu_region_level_intake_summary_geo,
  #   fill = "transparent",
  #   color = "grey20",
  #   size = .35
  # )  + 
 # geom_label(
 #     data = df_csu_level_intake_summary_geo_to_map,
 #     aes(geometry = geometry,
 #         label = paste0(csu)),
 # family = "Franklin Gothic Demi",
 # color = "gray25",
 # size = 3,
 # fontface = "bold",
 # stat = "sf_coordinates") +
 # guides(fill = guide_colorbar(barwidth = 8),
 #          direction = "horizontal",
 #     barheight = unit(2, units = "mm"),
 #     barwidth = unit(50, units = "mm"),
 #     draw.ulim = F,
 #     title.position = 'top',
 #     # some shifting around
 #     title.hjust = 0.5,
 #     label.hjust = 0.5) +
 #  labs(
 #    title = NULL,
 #    subtitle = NULL,
 #    x = NULL,
 #    y = NULL,
 #    fill = NULL,
 #    caption = NULL
 #  ) +
  # add theme
  theme_map() 
# +
#   theme(
#     # plot.margin = margin(),
#     panel.grid = element_blank(),
#     axis.text.x = element_blank(),
#     axis.text.y = element_blank(),
#     legend.position = "bottom",
#     legend.justification = c(0.5, 0.5),
#     legend.text = element_text(size = 11)) 

# ### write out
# ggsave(
#     filename = file.path(sharepoint_ojjdp_va_viz, "csu_level_diversion_rate_map.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Figure 3: % of all Complaints Diverted by Court Service Unit (CSU) (continuous scale)

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 100%

### map via ggplot 
ggplot(
  # define main data source
  data = df_csu_level_intake_summary_geo_to_map
) +
  scale_alpha(name = "",
              range = c(0.6, 0),
              guide = F) + # suppress legend
  # add main fill aesthetic
  geom_sf(
    mapping = aes(
      fill = `Complaints Diverted (row %)`
      ),
    color = "white",
    size = 0.1
  ) +
    scale_fill_distiller(
    labels = scales::percent_format(accuracy=1),
    direction = 1,
    name = "% of Complaints Diverted"
  ) +
  ### use jr palette here
    scale_colour_gradientn(colours = c("#D7EBF1","#AFD6E2","#87C2D4","#2F7084","#1F4A58")) +
 # scale_fill_manual(
 #    values = c("#1F4A58","#2F7084","#87C2D4","#AFD6E2"),
 #    name = "% of Complaints Diverted",
 #    na.value = "grey50",
 #    guide = guide_legend(
 #     keyheight = unit(7.5, units = "mm"),
 #     title.position = "top",
 #     reverse = F # display highest on top
  # )) +
  # use white stroke borders for county boundaries
  geom_sf(
    data = df_county_level_intake_summary_geo_to_map,
    fill = "transparent",
    color = "white",
    size = .05
  ) +
  # use white stroke borders for csu boundaries
  geom_sf(
    data = df_csu_level_intake_summary_geo_to_map,
    fill = "transparent",
    color = "white",
    size = .65
  )  +
  # use additional csu region-level shapefile for region border
  # geom_sf(
  #   data = df_csu_region_level_intake_summary_geo,
  #   fill = "transparent",
  #   color = "grey20",
  #   size = .35
  # )  + 
 # geom_label(
 #     data = df_csu_level_intake_summary_geo_to_map,
 #     aes(geometry = geometry,
 #         label = paste0(csu)),
 # family = "Franklin Gothic Demi",
 # color = "gray25",
 # size = 3,
 # fontface = "bold",
 # stat = "sf_coordinates") +
 guides(fill = guide_colorbar(barwidth = 8),
          direction = "horizontal",
     barheight = unit(2, units = "mm"),
     barwidth = unit(50, units = "mm"),
     draw.ulim = F,
     title.position = 'top',
     # some shifting around
     title.hjust = 0.5,
     label.hjust = 0.5) +
 #  labs(
 #    title = NULL,
 #    subtitle = NULL,
 #    x = NULL,
 #    y = NULL,
 #    fill = NULL,
 #    caption = NULL
 #  ) +
  # add theme
  theme_map() +
  theme(
    # plot.margin = margin(),
    panel.grid = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    legend.position = "bottom",
    legend.justification = c(0.5, 0.5),
    legend.text = element_text(size = 11))

# ### write out
# ggsave(
#     filename = file.path(sharepoint_ojjdp_va_viz, "csu_level_diversion_rate_map.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br><br>

