---
title: "Analysis: Part I"
format: html
---


**Research Questions:**


Using a cohort of first-time system involved youth, look at adjusted differences in likelihood of being diverted and likelihood of a re-complaint for diverted vs. non-diverted youth.

A. How does the likelihood of being diverted differ by race, sex, and geography?

B. For youth who are diverted, how likely are they to come back into the system with a new complaint or new petition within a year of the initial intake decision? 

<br>

**Methods:**

For research question (A) we will build a series of logistic regression models, adjusting for race/ethnicity, age, offense, risk level, and other factors that may also be related to a decision to divert. Our outcome variable will be diversion/petition (0/1) and our independent variables of interest will be race, sex, and CSU. For research question (B) we will take a similar methodological approach, but restrict our cohort to diverted youth and focus on likelihood of a re-complaint within a year of diversion while adjusting for demographics, offense, risk level, etc. For research question (B) our outcome variable will be re-complaint within a year of the initial intake decision date (0/1) and our independent variables of interest will be race, sex, and CSU.

*Cohort:* first time system involved youth (no prior complaints), 2016-2021

*Method:* Logistic Regression, which allows us to look at the relationship between two variables (like race and decision to divert) while adjusting for other factors that may also be related to our outcome (like offense, risk, etc.).

<br>


```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog","ggpattern","scales","tidylog")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())

### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_analysis_analytic_data <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Data/VA/analysis/analytic"))

### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_viz <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Output/VA/r_viz_output"))
```

```{r include=FALSE}
### pull in virginia djj analytic files 

# ### read in df_analytic_complaints_disposition_caseload.rds analytic rds file 
# df_complaints_youth_intake_decision_csu <- read_rds(file.path(sharepoint_ojjdp_va_analysis_analytic_data,"df_complaints_youth_intake_decision_csu.rds"))
# 
# ### read in caseload_clean.rds analytic rds file 
# caseload_clean <- read_rds(file.path(sharepoint_ojjdp_va_analysis_analytic_data,"caseload_clean.rds"))

### read in df_analytic_complaints_disposition_caseload file for analysis
df_analytic_complaints_disposition_caseload <- read_rds(file.path(sharepoint_ojjdp_va_analysis_analytic_data,"df_analytic_complaints_disposition_caseload.rds")) %>% 
  ### when two unique complaints for same individual have same date and both are labelled as first time JJ involvement, keep
  ### most serious offense between them
  filter(jj_history_clean=="No Prior JJ History") %>% 
  ### also filter out complaints with prob/parole violations
  ### and court order violations
  ### and civil commitment offenses
  ### and court summons intake decisions
  ### double check w/ Becky
  filter(dai!="Prob./Parole Violation",
         dai!="Court Order Violation",
         drg!="Civil Commitment",
         intake_decision_label!="COURT SUMMONS") %>% 
  ### create hierarchy of charge types for de-duping youth/intake dates
    mutate(dai_severity_order = case_when(
      dai%in%c("Felony against Persons") ~ 1,
      dai%in%c("Felony Weapons and Felony Narcotics Distribution") ~ 2,
      dai%in%c("Other Felony") ~ 3,
      dai%in%c("Class 1 Misdemeanor Against Persons") ~ 4,
      dai%in%c("Other Class 1 Misdemeanor") ~ 5,
      dai%in%c("Status Offense") ~ 6,
      dai%in%c("Prob./Parole Violation","SENTENCED IN CIRCUIT COURT","Other Violation","Court Order Violation","TRANSFER LEGAL CUSTODY (16.1-278.8.12)") ~ 7,
   TRUE ~ as.numeric(NA))) %>% 
    ### create hierarchy of charge types for de-duping youth/intake dates
    mutate(dai_clean = case_when(
      dai%in%c("Felony against Persons") ~ "Felony against Persons",
      dai%in%c("Felony Weapons and Felony Narcotics Distribution") ~ "Felony Weapons and Felony Narcotics Distribution",
      dai%in%c("Other Felony") ~ "Other Felony",
      dai%in%c("Class 1 Misdemeanor Against Persons") ~ "Class 1 Misdemeanor Against Persons",
      dai%in%c("Other Class 1 Misdemeanor") ~ "Other Class 1 Misdemeanor",
      dai%in%c("Status Offense") & drg!="CHINS" ~ "Status Offense",
      dai%in%c("Status Offense") & drg=="CHINS" ~ "CHINS",
      dai%in%c("Other Violation") ~ "Other Violation",
   TRUE ~ as.character(NA))) %>% 
  mutate(same_dates = ifelse(date_opened==next_complaint_intake_date,
                                                             1,0)) %>% 
  arrange(juvenile_number,
          date_opened,
          dai_severity_order) %>% 
  distinct(juvenile_number,
           .keep_all=TRUE)
  
```

# Research Question A1: Petition

<br>

## Table 1. Model Output: Petition

In the following analysis, the outcome variable is binary -- split into petitioned at intake (excluding court summons) and either diverted, resolved, or referred to another agency. All records with other intake complaint decisions are excluded from this analysis.

**NOTE:** I am currently running the regression on youth with no prior JJ history. 

Predictors included in model are:

* race

* gender

* age at intake

* CSU

* referral/petitioner source

* category of offense

* year of petition

* counts of felony, misdemeanor, status, and violation charges associated with intake/complaint


```{r message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(marginaleffects)

intake_complaints_no_prior_jj_to_model_diversion_petitioned <- df_analytic_complaints_disposition_caseload %>%
  filter(jj_history_clean=="No Prior JJ History",
         !is.na(intake_decision_regression_model_petition)==TRUE) %>% 
  mutate(race = fct_relevel(race_clean, "White"),
         gender = fct_relevel(gender_clean, "Male"),
         referral_source_clean = fct_relevel(referral_source_clean, "Other"),
         date_opened_year = fct_relevel(as.character(date_opened_year), "2015"),
         intake_decision_regression_model_petition_num = ifelse(intake_decision_regression_model_petition=="Petitioned",
                                           1,0)) %>% 
  distinct(juvenile_number,
           .keep_all=TRUE)

va_diversion_petition_model <- glm(
  intake_decision_regression_model_petition_num ~ race + gender + intake_age + csu + referral_source_clean + dai_clean +
    date_opened_year + count_misd_with_case + count_felony_with_case + count_status_with_case + count_violation_with_case,
  family = "binomial", 
  data = intake_complaints_no_prior_jj_to_model_diversion_petitioned)


tab_model(va_diversion_petition_model,
          p.style = "numeric_stars")

```

<br>

## Table 2: Predicted Probablities by Race/Ethnicity

**TO DO:** Double check predicted probability interpretation with categorical variables in model

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%


pred_prob_diversion_petition_race_overall <- predictions(va_diversion_petition_model, 
                                                by = c("race")) %>%
  mutate(rri = estimate / estimate[race == "White"]) %>% 
  dplyr::select(race_eth=race,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high,
                rri)

### print table via kableextra
kable(pred_prob_diversion_petition_race_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 1: Predicted Probablities by Race/Ethnicity

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%
pred_prob_diversion_petition_race <- predictions(va_diversion_petition_model, by = c("race")) %>%
  filter(race%in%c("Black","White","Hispanic","Asian")) 

pred_prob_diversion_petition_race %>%
  mutate(race = fct_reorder(race, estimate, max)) %>%
  ggplot(aes(estimate, race)) +
  geom_point(size = 6.5, alpha = 0.75, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.1)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Petition",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Table 3: Predicted Probablities by Gender

**TO DO:** Double check predicted probability interpretation with categorical variables in model

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_gender_overall <- predictions(va_diversion_petition_model, 
                                                by = c("gender")) %>%
  mutate(rri = estimate / estimate[gender == "Female"]) %>% 
  dplyr::select(gender,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high,
                rri)

### print table via kableextra
kable(pred_prob_diversion_petition_gender_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 2: Predicted Probablities by Gender

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_gender <- predictions(va_diversion_petition_model, by = c("gender")) 

pred_prob_diversion_petition_gender %>%
  mutate(gender = fct_reorder(gender, estimate, max)) %>%
  ggplot(aes(estimate, gender)) +
  geom_point(size = 6.5, alpha = 0.75, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.1)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Petition",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Table 4: Predicted Probablities by CSU

**TO DO:** Double check predicted probability interpretation with categorical variables in model

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_csu_overall <- predictions(va_diversion_petition_model, 
                                                by = c("csu")) %>%
  dplyr::select(csu,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high)

### print table via kableextra
kable(pred_prob_diversion_petition_csu_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 3: Predicted Probablities by CSU

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_csu <- predictions(va_diversion_petition_model, by = c("csu")) 

pred_prob_diversion_petition_csu %>%
  mutate(csu = fct_reorder(csu, estimate, max)) %>%
  ggplot(aes(estimate, csu)) +
  geom_point(size = 3.75, alpha = 0.7, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.1)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Petition",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Table 5: Predicted Probablities by Charge Type

**TO DO:** Double check predicted probability interpretation with categorical variables in model

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_dai_overall <- predictions(va_diversion_petition_model, 
                                                by = c("dai_clean"),
                                                type = "response") %>%
  dplyr::select(dai_clean,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high)

### print table via kableextra
kable(pred_prob_diversion_petition_dai_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 3: Predicted Probablities by Charge Type

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_dai <- predictions(va_diversion_petition_model, by = c("dai_clean")) 

pred_prob_diversion_petition_dai %>%
  mutate(dai_clean = fct_reorder(dai_clean, estimate, max)) %>%
  ggplot(aes(estimate, dai_clean)) +
  geom_point(size = 6.5, alpha = 0.7, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.1)
  ) +
  scale_y_discrete(labels = wrap_format(15)) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Petition",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Figure 4: Predicted Probabilities of Petition by CSU for Status Offenses 

**NOTE:** This analysis excludes CHINS complaints. We may want to exclude CSU's with small N sizes -- I haven't yet done that. 

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_petition_status_by_csu <- predictions(va_diversion_petition_model, by = c("dai_clean","csu")) %>%
  filter(dai_clean%in%c("Status Offense"))

pred_prob_petition_status_by_csu %>%
  mutate(csu = fct_reorder(csu, estimate, max)) %>%
  ggplot(aes(estimate, csu, color = dai_clean)) +
  geom_point(size = 3.5, alpha = 0.85) +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  scale_colour_manual(values = rev(c("#2F7084"))) +
  scale_x_continuous(
    expand = expansion(mult = c(0.1, 0.1)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.15)) +
  guides(color = FALSE) +
  expand_limits(x = 0) +
  labs(
    title = NULL,
    x = "Predicted Probability of Petition",
    y = NULL,
    color = NULL) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(vjust=-0.5))

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br><br>

# Research Question A2: Disposition

<br>

## Table 6. Model Output: Disposition

In the following analysis, the outcome variable is binary -- split into disposed or not disposed (whether complaint had any disposition data, regardless of disposition)

**NOTE:** I am currently running the regression on youth with no prior JJ history. 

Predictors included in model are:

* race

* gender

* age at intake

* CSU

* referral/petitioner source

* category of offense

* year of petition

* counts of felony, misdemeanor, status, and violation charges associated with intake/complaint

```{r message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

intake_complaints_no_prior_jj_to_model_disposition <- df_analytic_complaints_disposition_caseload %>%
  filter(jj_history_clean=="No Prior JJ History",
         !is.na(intake_decision_regression_model_petition)==TRUE) %>% 
  mutate(race = fct_relevel(race_clean, "White"),
         gender = fct_relevel(gender_clean, "Male"),
         referral_source_clean = fct_relevel(referral_source_clean, "Other"),
         date_opened_year = fct_relevel(as.character(date_opened_year), "2015"),
         regression_model_dispo_num = ifelse(!is.na(dispo_description_clean)==TRUE,
                                           1,0)) %>% 
  distinct(juvenile_number,
           .keep_all=TRUE)

va_dispo_model <- glm(
  regression_model_dispo_num ~ race + gender + intake_age + csu + referral_source_clean + dai_clean +
    date_opened_year + count_misd_with_case + count_felony_with_case + count_status_with_case + count_violation_with_case,
  family = "binomial", 
  data = intake_complaints_no_prior_jj_to_model_disposition)


tab_model(va_dispo_model,
          p.style = "numeric_stars")

```

<br>

## Table 7: Predicted Probablities by CSU

**TO DO:** Double check predicted probability interpretation with categorical variables in model

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_dispo_csu_overall <- predictions(va_dispo_model, 
                                                by = c("csu")) %>%
  dplyr::select(csu,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high)

### print table via kableextra
kable(pred_prob_dispo_csu_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 5: Predicted Probablities by CSU

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_dispo_csu <- predictions(va_dispo_model, by = c("csu")) 

pred_prob_dispo_csu %>%
  mutate(csu = fct_reorder(csu, estimate, max)) %>%
  ggplot(aes(estimate, csu)) +
  geom_point(size = 3.75, alpha = 0.7, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.1)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Disposition",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Table 8: Predicted Probablities by Charge Type

**TO DO:** Double check predicted probability interpretation with categorical variables in model

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_dispo_dai_overall <- predictions(va_dispo_model, 
                                                by = c("dai_clean")) %>%
  dplyr::select(dai_clean,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high)

### print table via kableextra
kable(pred_prob_dispo_dai_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 6: Predicted Probablities by Charge Type

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_dispo_dai <- predictions(va_dispo_model, by = c("dai_clean")) 

pred_prob_dispo_dai %>%
  mutate(dai_clean = fct_reorder(dai_clean, estimate, max)) %>%
  ggplot(aes(estimate, dai_clean)) +
  geom_point(size = 6.5, alpha = 0.7, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.1)
  ) +
  scale_y_discrete(labels = wrap_format(15)) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Disposition",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Figure 7: Predicted Probabilities of Disposition by CSU for Status Offenses 

**NOTE:** This analysis excludes CHINS complaints. We may want to exclude CSU's with small N sizes -- I haven't yet done that. 

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_dispo_status_by_csu <- predictions(va_dispo_model, by = c("dai_clean","csu")) %>%
  filter(dai_clean%in%c("Status Offense"))

pred_prob_dispo_status_by_csu %>%
  mutate(csu = fct_reorder(csu, estimate, max)) %>%
  ggplot(aes(estimate, csu, color = dai_clean)) +
  geom_point(size = 3.5, alpha = 0.85) +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  scale_colour_manual(values = rev(c("#2F7084"))) +
  scale_x_continuous(
    expand = expansion(mult = c(0.1, 0.1)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.15)) +
  guides(color = FALSE) +
  expand_limits(x = 0) +
  labs(
    title = NULL,
    x = "Predicted Probability of Disposition",
    y = NULL,
    color = NULL) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(vjust=-0.5))

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br><br>

# Research Question B1: Subsequent Complaint

<br>

## Table 9. Model Output: Subsequent Complaint within One Year

In the following analysis, the outcome variable is binary -- whether a youth received another complaint within a year of their first intake (where the intake decision was diversion). All records with other intake complaint decisions are excluded from this analysis.

**NOTE:** I am currently running the regression on youth with no prior JJ history *and* who were initially diverted. I have also removed youth whose first complaint occurred after 6/30/2020. Since the sample is through 6/30/2021, there needs to be at least a year from a youth's initial intake during which there could be a subsequent complaint/petition. 


Predictors included in model are:

* race

* gender

* age at intake

* CSU

* referral/petitioner source

* category of offense

* year of petition

* counts of felony, misdemeanor, status, and violation charges associated with intake/complaint


```{r message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

intake_initial_diversion_re_complaint_within_a_year_model <- df_analytic_complaints_disposition_caseload %>%
  filter(jj_history_clean=="No Prior JJ History",
         intake_decision_clean=="Diverted",
         !is.na(intake_decision_regression_model_petition)==TRUE,
         date_opened<="2020-06-30") %>% 
  mutate(race = fct_relevel(race_clean, "White"),
         gender = fct_relevel(gender_clean, "Male"),
         referral_source_clean = fct_relevel(referral_source_clean, "Other"),
         date_opened_year = fct_relevel(as.character(date_opened_year), "2015")) %>% 
  distinct(juvenile_number,
           .keep_all=TRUE)

va_diversion_re_complaint_model <- glm(
  regression_outcome_new_complaint_one_year_first_time_jj ~ race + gender + intake_age + csu + referral_source_clean + dai_clean +
    date_opened_year + count_misd_with_case + count_felony_with_case + count_status_with_case + count_violation_with_case,
  family = "binomial", 
  data = intake_initial_diversion_re_complaint_within_a_year_model)


tab_model(va_diversion_re_complaint_model,
          p.style = "numeric_stars")

```

<br>

## Table 10: Predicted Probablities by Race/Ethnicity

**TO DO:** Double check predicted probability interpretation with categorical variables in model

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_race_overall <- predictions(va_diversion_re_complaint_model, 
                                                by = c("race")) %>%
  mutate(rri = estimate / estimate[race == "White"]) %>% 
  dplyr::select(race_eth=race,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high,
                rri)

### print table via kableextra
kable(pred_prob_diversion_petition_race_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 8: Predicted Probablities by Race/Ethnicity

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_race <- predictions(va_diversion_re_complaint_model, by = c("race")) %>%
  filter(race%in%c("Black","White","Hispanic","Asian")) 

pred_prob_diversion_petition_race %>%
  mutate(race = fct_reorder(race, estimate, max)) %>%
  ggplot(aes(estimate, race)) +
  geom_point(size = 6.5, alpha = 0.75, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.05)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Second Complaint",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Table 11: Predicted Probablities by Gender

**TO DO:** Double check predicted probability interpretation with categorical variables in model

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_gender_overall <- predictions(va_diversion_re_complaint_model, 
                                                by = c("gender")) %>%
  mutate(rri = estimate / estimate[gender == "Female"]) %>% 
  dplyr::select(gender,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high,
                rri)

### print table via kableextra
kable(pred_prob_diversion_petition_gender_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 9: Predicted Probablities by Gender

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_gender <- predictions(va_diversion_re_complaint_model, by = c("gender")) 

pred_prob_diversion_petition_gender %>%
  mutate(gender = fct_reorder(gender, estimate, max)) %>%
  ggplot(aes(estimate, gender)) +
  geom_point(size = 6.5, alpha = 0.75, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.05)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Second Complaint",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Table 12: Predicted Probablities by CSU

**TO DO:** Double check predicted probability interpretation with categorical variables in model

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_csu_overall <- predictions(va_diversion_re_complaint_model, 
                                                by = c("csu")) %>%
  dplyr::select(csu,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high)

### print table via kableextra
kable(pred_prob_diversion_petition_csu_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 10: Predicted Probablities by CSU

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_csu <- predictions(va_diversion_re_complaint_model, by = c("csu")) 

pred_prob_diversion_petition_csu %>%
  mutate(csu = fct_reorder(csu, estimate, max)) %>%
  ggplot(aes(estimate, csu)) +
  geom_point(size = 3.75, alpha = 0.7, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.05)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Second Complaint",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Table 13: Predicted Probablities by Charge Type

**TO DO:** Double check predicted probability interpretation with categorical variables in model

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_dai_overall <- predictions(va_diversion_re_complaint_model, 
                                                by = c("dai_clean")) %>%
  dplyr::select(dai_clean,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high)

### print table via kableextra
kable(pred_prob_diversion_petition_dai_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 11: Predicted Probablities by Charge Type

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_dai <- predictions(va_diversion_re_complaint_model, by = c("dai_clean")) 

pred_prob_diversion_petition_dai %>%
  mutate(dai_clean = fct_reorder(dai_clean, estimate, max)) %>%
  ggplot(aes(estimate, dai_clean)) +
  geom_point(size = 6.5, alpha = 0.7, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.05)
  ) +
  scale_y_discrete(labels = wrap_format(15)) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Second Complaint",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Figure 12: Predicted Probabilities by CSU for Status Offenses

**NOTE:** This analysis excludes CHINS complaints. We may want to exclude CSU's with small N sizes -- I haven't yet done that. 

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_petition_status_by_csu <- predictions(va_diversion_re_complaint_model, by = c("dai_clean","csu")) %>%
  filter(dai_clean%in%c("Status Offense"))

pred_prob_petition_status_by_csu %>%
  mutate(csu = fct_reorder(csu, estimate, max)) %>%
  ggplot(aes(estimate, csu)) +
  geom_point(size = 3.5, alpha = 0.85, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_colour_manual(values = rev(c("#2F7084"))) +
  scale_x_continuous(
    expand = expansion(mult = c(0.1, 0.1)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.05)) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Second Complaint",
    y = NULL,
    color = NULL) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(vjust=-0.5))

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br><br>

# Research Question B2: Subsequent Petition

<br>

## Table 14. Model Output: Petition within One Year

In the following analysis, the outcome variable is binary -- whether a youth received a petitioned complaint within a year of their first intake (where the intake decision was diversion). All records with other intake complaint decisions are excluded from this analysis.

**NOTE:** I am currently running the regression on youth with no prior JJ history *and* who were initially diverted. I have also removed youth whose first complaint occurred after 6/30/2020. Since the sample is through 6/30/2021, there needs to be at least a year from a youth's initial intake during which there could be a subsequent complaint/petition. 


Predictors included in model are:

* race

* gender

* age at intake

* CSU

* referral/petitioner source

* category of offense

* year of petition

* counts of felony, misdemeanor, status, and violation charges associated with intake/complaint


Another control we could add is something on how rural/urban each county is...

```{r message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

intake_initial_diversion_new_petition_within_a_year_model <- df_analytic_complaints_disposition_caseload %>%
  filter(jj_history_clean=="No Prior JJ History",
         intake_decision_clean=="Diverted",
         !is.na(intake_decision_regression_model_petition)==TRUE,
         date_opened<="2020-06-30") %>% 
  mutate(race = fct_relevel(race_clean, "White"),
         gender = fct_relevel(gender_clean, "Male"),
         referral_source_clean = fct_relevel(referral_source_clean, "Other"),
         date_opened_year = fct_relevel(as.character(date_opened_year), "2015")) %>% 
  distinct(juvenile_number,
           .keep_all=TRUE)

va_diversion_new_petition_model <- glm(
  regression_outcome_new_petition_one_year_first_time_jj ~ race + gender + intake_age + csu + referral_source_clean + dai_clean +
    date_opened_year + count_misd_with_case + count_felony_with_case + count_status_with_case + count_violation_with_case,
  family = "binomial", 
  data = intake_initial_diversion_new_petition_within_a_year_model)


tab_model(va_diversion_new_petition_model,
          p.style = "numeric_stars")

```

<br>

## Table 15: Predicted Probablities by Race/Ethnicity

**TO DO:** Double check predicted probability interpretation with categorical variables in model

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_race_overall <- predictions(va_diversion_new_petition_model, 
                                                by = c("race")) %>%
  mutate(rri = estimate / estimate[race == "White"]) %>% 
  dplyr::select(race_eth=race,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high,
                rri)

### print table via kableextra
kable(pred_prob_diversion_petition_race_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 13: Predicted Probablities by Race/Ethnicity

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_race <- predictions(va_diversion_new_petition_model, by = c("race")) %>%
  filter(race%in%c("Black","White","Hispanic","Asian")) 

pred_prob_diversion_petition_race %>%
  mutate(race = fct_reorder(race, estimate, max)) %>%
  ggplot(aes(estimate, race)) +
  geom_point(size = 6.5, alpha = 0.75, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.05)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Second Complaint",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Table 16: Predicted Probablities by Gender

**TO DO:** Double check predicted probability interpretation with categorical variables in model

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_gender_overall <- predictions(va_diversion_new_petition_model, 
                                                by = c("gender")) %>%
  mutate(rri = estimate / estimate[gender == "Female"]) %>% 
  dplyr::select(gender,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high,
                rri)

### print table via kableextra
kable(pred_prob_diversion_petition_gender_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 14: Predicted Probablities by Gender

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_gender <- predictions(va_diversion_new_petition_model, by = c("gender")) 

pred_prob_diversion_petition_gender %>%
  mutate(gender = fct_reorder(gender, estimate, max)) %>%
  ggplot(aes(estimate, gender)) +
  geom_point(size = 6.5, alpha = 0.75, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.05)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Subsequent Petition",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Table 17: Predicted Probablities by CSU

**TO DO:** Double check predicted probability interpretation with categorical variables in model

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_csu_overall <- predictions(va_diversion_new_petition_model, 
                                                by = c("csu")) %>%
  dplyr::select(csu,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high)

### print table via kableextra
kable(pred_prob_diversion_petition_csu_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 15: Predicted Probablities by CSU

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_csu <- predictions(va_diversion_new_petition_model, by = c("csu")) 

pred_prob_diversion_petition_csu %>%
  mutate(csu = fct_reorder(csu, estimate, max)) %>%
  ggplot(aes(estimate, csu)) +
  geom_point(size = 3.75, alpha = 0.7, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.05)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Subsequent Petition",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Table 18: Predicted Probablities by Charge Type

**TO DO:** Double check predicted probability interpretation with categorical variables in model

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_dai_overall <- predictions(va_diversion_new_petition_model, 
                                                by = c("dai_clean")) %>%
  dplyr::select(dai_clean,
                predicted_probability=estimate,
                confidence_interval_low=conf.low,
                confidence_interval_high=conf.high)

### print table via kableextra
kable(pred_prob_diversion_petition_dai_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 16: Predicted Probablities by Charge Type

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_dai <- predictions(va_diversion_new_petition_model, by = c("dai_clean")) 

pred_prob_diversion_petition_dai %>%
  mutate(dai_clean = fct_reorder(dai_clean, estimate, max)) %>%
  ggplot(aes(estimate, dai_clean)) +
  geom_point(size = 6.5, alpha = 0.7, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.05)
  ) +
  scale_y_discrete(labels = wrap_format(15)) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Subsequent Petition",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Figure 17: Predicted Probabilities by CSU for Status Offenses

**NOTE:** This analysis excludes CHINS complaints. We may want to exclude CSU's with small N sizes -- I haven't yet done that. 

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_petition_status_by_csu <- predictions(va_diversion_new_petition_model, by = c("dai_clean","csu")) %>%
  filter(dai_clean%in%c("Status Offense"))

pred_prob_petition_status_by_csu %>%
  mutate(csu = fct_reorder(csu, estimate, max)) %>%
  ggplot(aes(estimate, csu)) +
  geom_point(size = 3.5, alpha = 0.85, colour = "#2F7084") +
  geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
  # scale_colour_manual(values = rev(c("#2F7084"))) +
  scale_x_continuous(
    expand = expansion(mult = c(0.1, 0.1)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.05)) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Subsequent Petition",
    y = NULL,
    color = NULL) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(vjust=-0.5))

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br><br>
