---
title: "Analysis: Part I"
format: html
---


**Research Questions:**


Using a cohort of first-time system involved youth, look at adjusted differences in likelihood of being diverted and likelihood of a re-complaint for diverted vs. non-diverted youth.

A. How does the likelihood of being diverted differ by race, sex, and geography?

B. For youth who are diverted, how likely are they to come back into the system with a new complaint or new petition within a year of the initial intake decision? 

<br>

**Methods:**

For research question (A) we will build a series of logistic regression models, adjusting for race/ethnicity, age, offense, risk level, and other factors that may also be related to a decision to divert. Our outcome variable will be diversion/petition (0/1) and our independent variables of interest will be race, sex, and CSU. For research question (B) we will take a similar methodological approach, but restrict our cohort to diverted youth and focus on likelihood of a re-complaint within a year of diversion while adjusting for demographics, offense, risk level, etc. For research question (B) our outcome variable will be re-complaint within a year of the initial intake decision date (0/1) and our independent variables of interest will be race, sex, and CSU.

*Cohort:* first time system involved youth (no prior complaints), 2016-2021

*Method:* Logistic Regression, which allows us to look at the relationship between two variables (like race and decision to divert) while adjusting for other factors that may also be related to our outcome (like offense, risk, etc.).

<br>


```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog","ggpattern","scales")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())

### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_analysis_analytic_data <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Data/VA/analysis/analytic"))

### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_viz <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Output/VA/r_viz_output"))
```

```{r include=FALSE}
### pull in virginia djj analytic files 

# ### read in df_analytic_complaints_disposition_caseload.rds analytic rds file 
# df_complaints_youth_intake_decision_csu <- read_rds(file.path(sharepoint_ojjdp_va_analysis_analytic_data,"df_complaints_youth_intake_decision_csu.rds"))
# 
# ### read in caseload_clean.rds analytic rds file 
# caseload_clean <- read_rds(file.path(sharepoint_ojjdp_va_analysis_analytic_data,"caseload_clean.rds"))

### read in df_analytic_complaints_disposition_caseload file for analysis
df_analytic_complaints_disposition_caseload <- read_rds(file.path(sharepoint_ojjdp_va_analysis_analytic_data,"df_analytic_complaints_disposition_caseload.rds")) 
```

# Outcome Variable: Petition

<br>

## Table 1. Model Output

In the following analysis, the outcome variable is binary -- split into petitioned at intake (excluding court summons) and either diverted, resolved, or referred to another agency. All records with other intake complaint decisions are excluded from this analysis.

**NOTE:** I am currently running the regression on youth with no prior JJ history -- also filtering on intakes labelled as either "Delinquent" or "Status" (we probably need to ask Nina why there are youth with no prior JJ history, but violations). Predictors included in preliminary model are:

* race

* gender

* age at intake

* CSU

* referral/petitioner source

* category of offense

* year of petition

* counts of felony, misdemeanor, status, and violation charges associated with intake/complaint


Another control we could add is something on how rural/urban each county is...

```{r message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(marginaleffects)

intake_complaints_no_prior_jj_to_model_diversion_petitioned <- df_analytic_complaints_disposition_caseload %>%
  filter(jj_history_clean=="No Prior JJ History",
         flg_category%in%c("Deliquent","Status"),
         !is.na(intake_decision_regression_model_petition)==TRUE) %>% 
  mutate(race = fct_relevel(race_clean, "White"),
         gender = fct_relevel(gender_clean, "Male"),
         referral_source_clean = fct_relevel(referral_source_clean, "Other"),
         date_opened_year = fct_relevel(as.character(date_opened_year), "2015")) %>% 
  distinct(juvenile_number,
           .keep_all=TRUE)

va_diversion_petition_model <- glm(
  intake_decision_regression_model_petition ~ race + gender + intake_age + csu + referral_source_clean + dai +
    date_opened_year + count_misd_with_case + count_felony_with_case + count_status_with_case + count_violation_with_case,
  family = "binomial", 
  data = intake_complaints_no_prior_jj_to_model_diversion_petitioned)


tab_model(va_diversion_petition_model,
          p.style = "numeric_stars")

```

<br>

## Table 2: Predicted Probablities by Race/Ethnicity

**TO DO:** Double check predicted probability interpretation with categorical variables in model

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_race_overall <- predictions(va_diversion_petition_model, 
                                                variables = c("race")) %>%
  mutate(rri = predicted / predicted[race == "White"]) %>% 
  dplyr::select(race_eth=race,
                predicted_probability=predicted,
                std_error=std.error,
                rri)

### print table via kableextra
kable(pred_prob_diversion_petition_race_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 1: Predicted Probablities by Race/Ethnicity

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_race <- predictions(va_diversion_petition_model, variables = c("race")) %>%
  filter(race%in%c("Black","White","Hispanic","Asian")) 

pred_prob_diversion_petition_race %>%
  mutate(race = fct_reorder(race, predicted, max)) %>%
  ggplot(aes(predicted, race)) +
  geom_point(size = 6.5, alpha = 0.75, colour = "#1F4A58") +
  geom_linerange(aes(xmin = predicted-std.error, xmax = predicted+std.error)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.1)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Petition",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Table 3: Predicted Probablities by Gender

**TO DO:** Double check predicted probability interpretation with categorical variables in model

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_gender_overall <- predictions(va_diversion_petition_model, 
                                                variables = c("gender")) %>%
  mutate(rri = predicted / predicted[gender == "Female"]) %>% 
  dplyr::select(gender,
                predicted_probability=predicted,
                std_error=std.error,
                rri)

### print table via kableextra
kable(pred_prob_diversion_petition_gender_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 2: Predicted Probablities by Gender

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_gender <- predictions(va_diversion_petition_model, variables = c("gender")) 

pred_prob_diversion_petition_gender %>%
  mutate(race = fct_reorder(gender, predicted, max)) %>%
  ggplot(aes(predicted, gender)) +
  geom_point(size = 6.5, alpha = 0.75, colour = "#1F4A58") +
  geom_linerange(aes(xmin = predicted-std.error, xmax = predicted+std.error)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.1)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Petition",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Table 4: Predicted Probablities by CSU

**TO DO:** Double check predicted probability interpretation with categorical variables in model

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_csu_overall <- predictions(va_diversion_petition_model, 
                                                variables = c("csu")) %>%
  dplyr::select(csu,
                predicted_probability=predicted,
                std_error=std.error)

### print table via kableextra
kable(pred_prob_diversion_petition_csu_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 3: Predicted Probablities by CSU

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_csu <- predictions(va_diversion_petition_model, variables = c("csu")) 

pred_prob_diversion_petition_csu %>%
  mutate(race = fct_reorder(csu, predicted, max)) %>%
  ggplot(aes(predicted, csu)) +
  geom_point(size = 6.5, alpha = 0.75, colour = "#1F4A58") +
  geom_linerange(aes(xmin = predicted-std.error, xmax = predicted+std.error)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.1)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Petition",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Table 4: Predicted Probablities by Charge Type

**TO DO:** Double check predicted probability interpretation with categorical variables in model

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_dai_overall <- predictions(va_diversion_petition_model, 
                                                variables = c("dai")) %>%
  dplyr::select(dai,
                predicted_probability=predicted,
                std_error=std.error)

### print table via kableextra
kable(pred_prob_diversion_petition_dai_overall, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Figure 3: Predicted Probablities by Charge Type

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

pred_prob_diversion_petition_dai <- predictions(va_diversion_petition_model, variables = c("dai")) 

pred_prob_diversion_petition_dai %>%
  mutate(race = fct_reorder(dai, predicted, max)) %>%
  ggplot(aes(predicted, dai)) +
  geom_point(size = 6.5, alpha = 0.75, colour = "#1F4A58") +
  geom_linerange(aes(xmin = predicted-std.error, xmax = predicted+std.error)) +
  # scale_color_discrete(values = "#2F7084") +
  scale_x_continuous(
    expand = expansion(mult = c(0.2, 0.2)),
    labels = label_percent(1),
    breaks = seq(0, 1, by = 0.1)
  ) +
  guides(color = FALSE) +
  expand_limits(x = .25) +
  labs(
    title = NULL,
    x = "Predicted Probability of Petition",
    y = NULL,
    color = NULL
  ) +
  theme(
    plot.title = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title.x = element_text(vjust=-0.5)
  ) 

# ### save out as png
# ggsave(
#     filename = file.path(sharepoint_viz_path, "pred_prob_revocation_race_supervision_type_overall.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br><br>
