---
title: "Part II Analysis: Disposition"
format: html
---

**Data Sample:** 

* Juvenile intake complaints with intake dates from July 1, 2015 - June 30, 2021

* Dispositions – all dispositions for the intake complaints in the sample. 


**Research Question:**

Conduct a front-end system assessment from intake through petition for all complaints 2016-2021.


**Methods:**

We will conduct a descriptive analysis of the front end of the system from intake through petition, provide unadjusted counts, RRI’s and means tests where applicable, by race, sex, offense, risk, CSU, and year for:

*	Complaints

*	Intake decisions: divert, resolve, petition, other

*	Average LOS on diversion 

*	Diversion completions: successful, unsuccessful, other

*	Dispositions on petitioned cases

*Cohort:* All complaints from 2016-2021  

<br>

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())

### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_analysis_analytic_data <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Data/VA/analysis/analytic"))

### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_viz <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Output/VA/r_viz_output"))
```

```{r include=FALSE}
### pull in preliminary virginia djj analytic files 

### read in preliminary analytic rds file 
df_complaints_youth_intake_decision_csu <- read_rds(file.path(sharepoint_ojjdp_va_analysis_analytic_data,"df_complaints_youth_intake_decision_csu.rds"))

### write out file for preliminary analysis
caseload_clean <- read_rds(file.path(sharepoint_ojjdp_va_analysis_analytic_data,"caseload_clean.rds"))
```

```{r include=FALSE,warning=FALSE,include=FALSE}
### create denominator -- unique complaint for entire sample
unique_complaints_sample_denom <- n_distinct(df_complaints_youth_intake_decision_csu$unique_complaint_id)

### create denominator -- unique youth for entire sample
unique_youth_sample_denom <- n_distinct(df_complaints_youth_intake_decision_csu$juvenile_number)
```


**Note:** See coding of intake decisions in `Intake Complaints, Intake Decision Descriptions` table on `codebook` page in `sample descriptives` tab

# Tables


## Table 1: % of All Complaints Diverted, 2015-2021

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### overall complaints by diversion status
df_complaints_youth_intake_decision_table <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(intake_decision_clean) %>% 
  dplyr::summarise(`Unique Complaints (N)` = n_distinct(unique_complaint_id),
            `Complaints, Percent of Sample (%)` = scales::percent(`Unique Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Intake Decision` = intake_decision_clean) 


### print table via kableextra
kable(df_complaints_youth_intake_decision_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Table 2: % of All Complaints Diverted by Year

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_year <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(date_opened_year) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Year of Complaint` = date_opened_year) 

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Year of Complaint` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_year_final <- rbind(df_complaints_youth_intake_decision_table_year,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_year_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(8, bold = TRUE)
```

<br>

## Table 3: % of All Complaints Diverted by Race/Ethnicity

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_race <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean) 

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Race/Ethnicity` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_race_final <- rbind(df_complaints_youth_intake_decision_table_race,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_race_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(8, bold = TRUE)
```

<br>

## Table 4: % of All Complaints Diverted by Gender

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_gender <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(gender_clean) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Gender` = gender_clean) 

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Gender` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_gender_final <- rbind(df_complaints_youth_intake_decision_table_gender,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_gender_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE)
```

<br>

## Table 5: % of All Complaints Diverted by Age at Petition

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

**Question:** We seem to be missing age (pet_age) for about 35% of all records in the intake complaints file -- how should we interpret this? Something seems off with this table -- why is the diversion rate so much higher for youth whose age is missing? Does missing age mean youth was not formally petitioned and thus they don't have age here?

**TO DO:** Decide on which ages to exclude because of likely data collection issues (e.g. ages of 0 or 44)

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_age <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(intake_age) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Age at Intake` = intake_age) 

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Age at Intake` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_age_final <- rbind(df_complaints_youth_intake_decision_table_age,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_age_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(44, bold = TRUE)
```

<br>

## Table 6a: % of All Complaints Diverted by Offense Type (most serious offense; mso_flag == "Y")

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_offense <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(dai) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Offense Description` = dai)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Offense Description` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_offense_final <- rbind(df_complaints_youth_intake_decision_table_offense,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_offense_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(10, bold = TRUE)
```

<br>

## Table 6b: % of All Complaints Diverted by Status Offense Type (most serious offense is status; mso_flag == "Y")

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_offense_status <- df_complaints_youth_intake_decision_csu %>% 
  filter(dai=="Status Offense") %>% 
  dplyr::group_by(drg) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>%  
  ungroup() %>% 
  dplyr::rename(`Status Offense Description` = drg)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  filter(dai=="Status Offense") %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Status Offense Description` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_offense_status_final <- rbind(df_complaints_youth_intake_decision_table_offense_status,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_offense_status_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(4, bold = TRUE)
```

<br>

## Table 7: % of All Complaints Diverted by Court Service Unit (CSU)

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_csu <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(csu) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`CSU` = csu)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>%  
  ungroup() %>% 
  dplyr::mutate(`CSU` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_csu_final <- rbind(df_complaints_youth_intake_decision_table_csu,
                                                             df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_csu_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(33, bold = TRUE)
```

<br>

## Table 8: % of All Complaints Diverted by Court Service Unit (CSU) Region

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

See CSU regions here: https://www.djj.virginia.gov/pages/community/court-service-units.htm

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_csu_region <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(csu_region) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`CSU Region` = csu_region)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`CSU Region` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_csu_region_final <- rbind(df_complaints_youth_intake_decision_table_csu_region,
                                                             df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_csu_region_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 9: % of All Complaints Diverted by Prior JJ History 

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

**Question:** How should we interpret missing prior JJ complaint data? About 40% of all intake complaints records appear to have missing data in these columns

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_jj_history <- df_complaints_youth_intake_decision_csu %>% 
  filter(!is.na(jj_history_clean)==TRUE) %>% 
  dplyr::group_by(jj_history_clean) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`JJ History` = jj_history_clean)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  filter(!is.na(jj_history_clean)==TRUE) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`JJ History` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_jj_history_final <- rbind(df_complaints_youth_intake_decision_table_jj_history,
                                                             df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_jj_history_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 10: % of All Complaints Diverted by Petitioner Type

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_pet_desc <- df_complaints_youth_intake_decision_csu %>% 
  filter(!is.na(petitioner_desc)==TRUE) %>% 
  dplyr::group_by(petitioner_desc) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Petitioner Description` = petitioner_desc)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  filter(!is.na(petitioner_desc)==TRUE) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Petitioner Description` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_pet_desc_final <- rbind(df_complaints_youth_intake_decision_table_pet_desc,
                                                             df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_pet_desc_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(24, bold = TRUE)
```

<br>

