---
title: "Virginia DJJ Data File Codebooks"
format: html
---

**Data Sample:** 

* Juvenile intake complaints with intake dates from July 1, 2015 - June 30, 2021

* Dispositions – all dispositions for the intake complaints in the sample. 

* Caseload – all intake complaints in the sample that are associated with a workload status for diversion - "Diversion At Intake" or "Diversion Program Beyond 90 Days"


**For all missing data plots**, here are the % missingness categories: "Good" <= 5% missing, "OK" <= 40% missing, "Bad" <= 80% missing, and "Remove" = 100% missing

<br>

This syntax pulls in all data files provided by DJJ stored as a series of Excel file tabs -- creates high-level codebooks for each using the DataExplorer package (https://boxuancui.github.io/DataExplorer/index.html). File names reflect the names provided by Dallas County.


```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())
```

```{r include=FALSE}
### pull in virginia djj data from raw data folder

### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_raw_data <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Data/VA/raw"))

########################################################
### import first excel file w/ multiple tabs with purrr
########################################################

### using purrr::map, import list of tabs from excel worksheet
ojjdp_va_raw_tab_list_file_one <- purrr::map(purrr::set_names(excel_sheets(file.path(sharepoint_ojjdp_va_raw_data,
                                                              "CSG Front End data 01202023 - pt1 - SENSITIVE.xlsx"))),
                      read_excel, 
                      path = file.path(sharepoint_ojjdp_va_raw_data,"CSG Front End data 01202023 - pt1 - SENSITIVE.xlsx")) %>% 
  purrr::map(janitor::clean_names)

### clean names of all imported tabs before converting to dataframes
names(ojjdp_va_raw_tab_list_file_one) <- janitor::make_clean_names(names(ojjdp_va_raw_tab_list_file_one))

### then convert list of tabs to distinct dataframes with names from tabs
purrr::map(names(ojjdp_va_raw_tab_list_file_one),
           ~assign(.x, 
                   ojjdp_va_raw_tab_list_file_one[[.x]], 
        envir = .GlobalEnv)) 

########################################################
### now import second file from djj -- with only one tab
########################################################
df_djj_intake_complaints_raw <- openxlsx::read.xlsx(file.path(sharepoint_ojjdp_va_raw_data,
                                                              "CSG Front End data 01202023 - pt2 - SENSITIVE.xlsx"),
                                                    sheet = 1) %>% 
  clean_names()
```

```{r include=FALSE}
# Custom function
plot_missing_2 <-
function (data, group = list(Good = 0.05, Okay = 0.4, Poor = 0.8, 
  Remove =  1), geom_label_args = list(), title = NULL, ggtheme = theme_gray(), 
theme_config = list(legend.position = c("bottom"))) 
{
  pct_missing <- Missingness <- NULL
  missing_value <- data.table(profile_missing(data))
  group <- group[sort.list(unlist(group))]
  invisible(lapply(seq_along(group), function(i) {
    if (i == 1) {
      missing_value[pct_missing <= group[[i]], `:=`(Missingness,
         names(group)[i])]
    } else {
  missing_value[pct_missing > group[[i - 1]] & pct_missing <= 
     group[[i]], `:=`(Missingness, names(group)[i])]
    }
}))
  output <- ggplot(missing_value, aes_string(x = "feature", 
    y = "num_missing", fill = "Missingness")) + geom_bar(stat = "identity") + 
   scale_fill_manual("Missingness", values = c("Good"="green2","Okay"="gold","Poor"="darkorange","Remove"="firebrick2")) + coord_flip() + xlab("Features") + 
   ylab("Missing Rows")
  geom_label_args_list <- list(mapping = aes(label = paste0(round(100 * 
    pct_missing, 2), "%")))
  output <- output + do.call("geom_label", c(geom_label_args_list, 
     geom_label_args))
  class(output) <- c("single", class(output))
  plotDataExplorer(plot_obj = output, title = title, ggtheme = ggtheme, 
   theme_config = theme_config)
}
```


<br>

## Intake Complaints File

**DJJ Description:** Juvenile intake complaints with intake dates from July 1, 2015 - June 30, 2021

<br>

### Intake Complaints, Data Overview
```{r out.width="50%",echo=FALSE,warning=FALSE,message=FALSE}
### run the `DataExplorer` function introduce()
table <- DataExplorer::introduce(df_djj_intake_complaints_raw) %>% 
  pivot_longer(rows:memory_usage, names_to = "Measure", values_to = "Count")

kable(table, format.args = list(big.mark = ","), 
      align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                 row_label_position = "l") 
```

<br>

### Intake Complaints, Fields Included
```{r out.width="50%",echo=FALSE,warning=FALSE,message=FALSE}
### join pertinent variable labels from 'data_field_list' dataframe (the high-level data dictionary that DJJ provided)
### using snakecase to clean values in columns
column_labels <- data_field_list %>% 
  mutate(Variable = snakecase::to_any_case(field_name)) %>% 
  filter(excel_tab=="Intake Complaints") %>% 
  dplyr::rename(Description=description) %>% 
  dplyr::select(Variable,
                Description)
  
### create table with kable
kable(column_labels, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                row_label_position = "l")
```

<br>

### Intake Complaints, Missing Data
```{r out.width="120%",echo=FALSE,warning=FALSE,message=FALSE}
### run the `DataExplorer` function plot_missing()
plot_missing_2(df_djj_intake_complaints_raw)
```

<br><br>

## Disposition File 

**DJJ Description:** All dispositions for the intake complaints in the sample 

<br>

### Disposition, Data Overview
```{r out.width="50%",echo=FALSE,warning=FALSE,message=FALSE}
### run the `DataExplorer` function introduce()
table <- DataExplorer::introduce(disposition) %>% 
  pivot_longer(rows:memory_usage, names_to = "Measure", values_to = "Count")

kable(table, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), row_label_position = "l") 
```

<br>

### Disposition, Fields Included
```{r out.width="50%",echo=FALSE,warning=FALSE,message=FALSE}
### join pertinent variable labels from 'data_field_list' dataframe (the high-level data dictionary that DJJ provided)
### using snakecase to clean values in columns
column_labels <- data_field_list %>% 
  mutate(Variable = snakecase::to_any_case(field_name)) %>% 
  filter(excel_tab=="Disposition") %>% 
  dplyr::rename(Description=description) %>% 
  dplyr::select(Variable,
                Description)
  
### create table with kable
kable(column_labels, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                row_label_position = "l")
```

<br>

### Disposition, Missing Data
```{r out.width="120%",echo=FALSE,warning=FALSE,message=FALSE}
### run the `DataExplorer` function plot_missing()
plot_missing_2(disposition)
```

<br><br>

## Caseload File 

**DJJ Description:** All intake complaints in the sample that are associated with a workload status for diversion - "Diversion At Intake" or "Diversion Program Beyond 90 Days"

<br>

### Caseload, Data Overview
```{r out.width="50%",echo=FALSE,warning=FALSE,message=FALSE}
### run the `DataExplorer` function introduce()
table <- DataExplorer::introduce(caseload) %>% 
  pivot_longer(rows:memory_usage, names_to = "Measure", values_to = "Count")

kable(table, format.args = list(big.mark = ","), align=rep('c')) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), row_label_position = "l") 
```

<br>

### Caseload, Fields Included
```{r out.width="50%",echo=FALSE,warning=FALSE,message=FALSE}
### join pertinent variable labels from 'data_field_list' dataframe (the high-level data dictionary that DJJ provided)
### using snakecase to clean values in columns
column_labels <- data_field_list %>% 
  mutate(Variable = snakecase::to_any_case(field_name)) %>% 
  filter(excel_tab=="Caseload") %>% 
  dplyr::rename(Description=description) %>% 
  dplyr::select(Variable,
                Description)
  
### create table with kable
kable(column_labels, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                row_label_position = "l")
```

<br>

### Caseload, Missing Data
```{r out.width="120%",echo=FALSE,warning=FALSE,message=FALSE}
### run the `DataExplorer` function plot_missing()
plot_missing_2(caseload)
```

<br><br>
