---
title: "Analysis: Part II"
format: html
---

**Data Sample:** 

* Juvenile intake complaints with intake dates from July 1, 2015 - June 30, 2021

* Dispositions – all dispositions for the intake complaints in the sample. 


**Research Question:**

Conduct a front-end system assessment from intake through petition for all complaints 2016-2021.


**Methods:**

We will conduct a descriptive analysis of the front end of the system from intake through petition, provide unadjusted counts, RRI’s and means tests where applicable, by race, sex, offense, risk, CSU, and year for:

*	Complaints

*	Intake decisions: divert, resolve, petition, other

*	Average LOS on diversion 

*	Diversion completions: successful, unsuccessful, other

*	Dispositions on petitioned cases

*Cohort:* All complaints from 2016-2021  

<br>

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())
```

```{r include=FALSE}
### pull in virginia djj data from raw data folder

### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_raw_data <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Data/VA/raw"))

########################################################
### import first excel file w/ multiple tabs with purrr
########################################################

### using purrr::map, import list of tabs from excel worksheet
ojjdp_va_raw_tab_list_file_one <- purrr::map(purrr::set_names(excel_sheets(file.path(sharepoint_ojjdp_va_raw_data,
                                                              "CSG Front End data 01202023 - pt1 - SENSITIVE.xlsx"))),
                      read_excel, 
                      path = file.path(sharepoint_ojjdp_va_raw_data,"CSG Front End data 01202023 - pt1 - SENSITIVE.xlsx")) %>% 
  purrr::map(janitor::clean_names)

### clean names of all imported tabs before converting to dataframes
names(ojjdp_va_raw_tab_list_file_one) <- janitor::make_clean_names(names(ojjdp_va_raw_tab_list_file_one))

### then convert list of tabs to distinct dataframes with names from tabs
purrr::map(names(ojjdp_va_raw_tab_list_file_one),
           ~assign(.x, 
                   ojjdp_va_raw_tab_list_file_one[[.x]], 
        envir = .GlobalEnv)) 

########################################################
### now import second file from djj -- with only one tab
########################################################
df_djj_intake_complaints_raw <- openxlsx::read.xlsx(file.path(sharepoint_ojjdp_va_raw_data,
                                                              "CSG Front End data 01202023 - pt2 - SENSITIVE.xlsx"),
                                                    sheet = 1) %>% 
  clean_names()
```

```{r include=FALSE, message=FALSE, warning=FALSE}
#############################################
### clean and de-dup df_djj_intake_complaints_raw dataframe
### this is our base file for the sample
#############################################
df_djj_intake_complaints_clean <- df_djj_intake_complaints_raw %>% 
  distinct(juvenile_number,
           case_number,
           offense_number,
           .keep_all=TRUE) %>% ### no records dropped
  ### keep most serious offense associated with intake case/complaint
  dplyr::filter(mso_flag == "Y") %>% 
  ### according to DJJ documentation, multiple offenses may have mso flag of 1 if
  ### severity ranking is tied; so now de-dup those instances 
  ### note: if we decide to further explore counts of offenses/types of status offenses
  ### we will want the full dataframe duplicated by complaint/intake/offense
  distinct(juvenile_number,
           case_number,
           .keep_all=TRUE) %>% 
  ### clean race/ethnicity and gender
  ### use factor function to assign labels to values
  mutate(race_clean = case_when(
    race=="I" & hispanic!="Y" ~ 1,
    race=="A" & hispanic!="Y" ~ 2,
    race=="B" & hispanic!="Y" ~ 3,
    hispanic=="Y" ~ 4,
    race=="W" & hispanic!="Y" ~ 5,
    race %in% c("X","O") & hispanic!="Y" ~ 6,
    TRUE ~ 7),
    race_clean = factor(race_clean,
         levels = c(1,2,3,4,5,6,7),
         labels = c("American Indian", "Asian", "Black", "Hispanic", "White", "Other","Missing"))) %>% 
  mutate(gender_clean = case_when(
    sex=="F" ~ 1,
    sex=="M" ~ 2,
    TRUE ~ as.numeric(NA)),
    gender_clean = factor(gender_clean,
         levels = c(1,2),
         labels = c("Female", "Male"))) %>%   
### clean dates and create year for potential grouping in future trend analysis
  mutate(date_opened = ymd(as_date(excel_numeric_to_date(as.numeric(as.character(date_opened)), 
                                                  date_system = "modern"))),
         ysai_date = ymd(as_date(ysai_date)),
         date_opened_year = year(date_opened)) 

### clean up codebook values that we need
codebook_intake_decision_values <- codebook %>% 
  filter(field_name=="INTAKE_DECISION") %>% 
  dplyr::select(intake_decision=code,
                intake_decision_label=options,
                intake_decision_description=definitions) %>% 
  mutate(intake_decision = as.numeric(intake_decision))

### unique youth and complaints per year
df_complaints_youth_intake_decision <- df_djj_intake_complaints_clean %>% 
  mutate(intake_decision = as.numeric(intake_decision)) %>% 
  left_join(codebook_intake_decision_values,
            by = "intake_decision") %>% 
  ### create diversion flag
  ### create unique complaint-level ID
  mutate(diverted_flag = ifelse(intake_decision_label%in%c("UNSUCCESSFUL DIVERSION/PETITION FILED", "SUCCESSFUL DIVERSION","UNSUCCESSFUL DIVERSION/NO PETITION FILED","REQ'D TO PARTICIPATE-DIVERSION"),
                                1,0),
         diverted_flag = factor(diverted_flag,
                                levels = c(1,0),
                                labels = c("Yes","No")),
         unique_complaint_id = paste0(juvenile_number,case_number,.keep_all=TRUE)) %>% 
  ### create var for jj history using flags provided by DJJ
   mutate(jj_history_clean = case_when(
    prior_adj==0 ~ "No Prior JJ History",
    prior_other>0 ~ "Prior 'Other' History",
    (prior_chinsup>0 | prior_chins>0 | prior_other_status>0) ~ "Prior Status/CHINS/CHINsup",
    prior_misd>0 ~ "Prior Misdemeanor",
    prior_felony>0 ~ "Prior Felony",
    TRUE ~ as.character(NA)),
    jj_history_clean = factor(jj_history_clean,
                              levels = c("No Prior JJ History","Prior 'Other' History","Prior Status/CHINS/CHINsup","Prior Misdemeanor","Prior Felony")))

########################################
### clean and de-dup disposition dataframe
########################################
### note: disposition file is unique by youth, case number, offense number, disposition, amd days from intake to disposition
disposition_clean <- disposition %>% 
  distinct(juvenile_number,
           case_number,
           offense_number,
           description,
           .keep_all=TRUE) ### no records dropped
  
  ### next step: de-dup by disposition -- keeping most serious?
  

########################################
### clean and de-dup caseload dataframe
########################################
caseload_clean <- caseload %>% 
  distinct(juvenile_number,
           offense_number,
           .keep_all=TRUE) ### need to look into duplicates

```

```{r include=FALSE,warning=FALSE,include=FALSE}
### create denominator -- unique complaint for entire sample
unique_complaints_sample_denom <- n_distinct(df_complaints_youth_intake_decision$unique_complaint_id)

### create denominator -- unique youth for entire sample
unique_youth_sample_denom <- n_distinct(df_complaints_youth_intake_decision$juvenile_number)
```

```{r include=FALSE,warning=FALSE,include=FALSE}
### create lists of court service unit (CSU) regions
### see here: https://www.djj.virginia.gov/pages/community/court-service-units.htm
eastern_region <- c("001",
                    "002",
                    "02A",
                    "003",
                    "004",
                    "005",
                    "007",
                    "008")

northern_region <- c("017",
                    "018",
                    "019",
                    "020",
                    "026",
                    "031")

western_region <- c("021",
                    "022",
                    "023",
                    "027",
                    "028",
                    "029",
                    "030")

southern_region <- c("006",
                    "010",
                    "011",
                    "012",
                    "013",
                    "014")

central_region <- c("009",
                    "015",
                    "016",
                    "024",
                    "013",
                    "025")
```


```{r include=FALSE,warning=FALSE,message=FALSE}
### add csu region to df
df_complaints_youth_intake_decision_csu <- df_complaints_youth_intake_decision %>% 
  mutate(csu_region = case_when(
    csu %in% eastern_region ~ "Eastern",
    csu %in% northern_region ~ "Northern",
    csu %in% western_region ~ "Western",
    csu %in% southern_region ~ "Southern",
    csu %in% central_region ~ "Central", 
    TRUE ~ as.character(NA)))
```

<br>

# Tables


## Table 1: % of All Complaints Diverted, 2015-2021

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### overall complaints by diversion status
df_complaints_youth_intake_decision_table <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(diverted_flag) %>% 
  dplyr::summarise(`Unique Complaints (N)` = n_distinct(unique_complaint_id),
            `Complaints, Percent of Sample (%)` = scales::percent(`Unique Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Diverted?` = diverted_flag) 


### print table via kableextra
kable(df_complaints_youth_intake_decision_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Table 2: % of All Complaints Diverted by Year

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_year <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(date_opened_year) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="Yes"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Not Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="No"]),
                   `Complaints Not Diverted (row %)` = scales::percent(`Complaints Not Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Year of Complaint` = date_opened_year) 

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="Yes"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Not Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="No"]),
                   `Complaints Not Diverted (row %)` = scales::percent(`Complaints Not Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Year of Complaint` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_year_final <- rbind(df_complaints_youth_intake_decision_table_year,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_year_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(8, bold = TRUE)
```

<br>

## Table 3: % of All Complaints Diverted by Race/Ethnicity

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_race <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="Yes"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Not Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="No"]),
                   `Complaints Not Diverted (row %)` = scales::percent(`Complaints Not Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean) 

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="Yes"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Not Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="No"]),
                   `Complaints Not Diverted (row %)` = scales::percent(`Complaints Not Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Race/Ethnicity` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_race_final <- rbind(df_complaints_youth_intake_decision_table_race,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_race_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(8, bold = TRUE)
```

<br>

## Table 4: % of All Complaints Diverted by Gender

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_gender <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(gender_clean) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="Yes"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Not Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="No"]),
                   `Complaints Not Diverted (row %)` = scales::percent(`Complaints Not Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Gender` = gender_clean) 

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="Yes"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Not Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="No"]),
                   `Complaints Not Diverted (row %)` = scales::percent(`Complaints Not Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Gender` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_gender_final <- rbind(df_complaints_youth_intake_decision_table_gender,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_gender_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE)
```

<br>

## Table 5: % of All Complaints Diverted by Age at Petition

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

**Question:** We seem to be missing age (pet_age) for about 35% of all records in the intake complaints file -- how should we interpret this? 

**TO DO:** Decide on which ages to exclude because of likely data collection issues (e.g. ages of 0 or 44)

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_age <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(pet_age) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="Yes"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Not Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="No"]),
                   `Complaints Not Diverted (row %)` = scales::percent(`Complaints Not Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Age at Petition` = pet_age) 

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="Yes"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Not Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="No"]),
                   `Complaints Not Diverted (row %)` = scales::percent(`Complaints Not Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Age at Petition` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_age_final <- rbind(df_complaints_youth_intake_decision_table_age,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_age_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(44, bold = TRUE)
```

<br>

## Table 6: % of All Complaints Diverted by Offense Type (most serious offense; mso_flag == "Y")

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_offense <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(dai) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="Yes"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Not Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="No"]),
                   `Complaints Not Diverted (row %)` = scales::percent(`Complaints Not Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Offense Description` = dai)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="Yes"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Not Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="No"]),
                   `Complaints Not Diverted (row %)` = scales::percent(`Complaints Not Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Offense Description` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_offense_final <- rbind(df_complaints_youth_intake_decision_table_offense,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_offense_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(10, bold = TRUE)
```

<br>

## Table 7: % of All Complaints Diverted by Court Service Unit (CSU)

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_csu <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(csu) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="Yes"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Not Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="No"]),
                   `Complaints Not Diverted (row %)` = scales::percent(`Complaints Not Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`CSU` = csu)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="Yes"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Not Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="No"]),
                   `Complaints Not Diverted (row %)` = scales::percent(`Complaints Not Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`CSU` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_csu_final <- rbind(df_complaints_youth_intake_decision_table_csu,
                                                             df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_csu_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(33, bold = TRUE)
```

<br>

## Table 8: % of All Complaints Diverted by Court Service Unit (CSU) Region

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

See CSU regions here: https://www.djj.virginia.gov/pages/community/court-service-units.htm

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_csu_region <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(csu_region) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="Yes"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Not Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="No"]),
                   `Complaints Not Diverted (row %)` = scales::percent(`Complaints Not Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`CSU Region` = csu_region)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="Yes"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Not Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="No"]),
                   `Complaints Not Diverted (row %)` = scales::percent(`Complaints Not Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`CSU Region` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_csu_region_final <- rbind(df_complaints_youth_intake_decision_table_csu_region,
                                                             df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_csu_region_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 9: % of All Complaints Diverted by Prior JJ History 

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

**Question:** How should we interpret missing prior JJ complaint data? About 40% of all intake complaints records appear to have missing data in these columns

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_jj_history <- df_complaints_youth_intake_decision_csu %>% 
  filter(!is.na(jj_history_clean)==TRUE) %>% 
  dplyr::group_by(jj_history_clean) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="Yes"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Not Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="No"]),
                   `Complaints Not Diverted (row %)` = scales::percent(`Complaints Not Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`JJ History` = jj_history_clean)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  filter(!is.na(jj_history_clean)==TRUE) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="Yes"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Not Diverted (N)` = n_distinct(unique_complaint_id[diverted_flag=="No"]),
                   `Complaints Not Diverted (row %)` = scales::percent(`Complaints Not Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`JJ History` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_jj_history_final <- rbind(df_complaints_youth_intake_decision_table_jj_history,
                                                             df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_jj_history_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>
