---
title: "Sample Descriptive Statistics"
format: html
---

In this file, we'll import all of the Virginia DJJ files provided and create preliminary cross-tabulations and merges to explore basic counts, trends, and double check primary keys and joins across the data files. 

See `Codebooks` and `Data Diagram` tabs for more information on each individual data file. 

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())
```

```{r include=FALSE}
### pull in virginia djj data from raw data folder

### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_raw_data <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Data/VA/raw"))

########################################################
### import first excel file w/ multiple tabs with purrr
########################################################

### using purrr::map, import list of tabs from excel worksheet
ojjdp_va_raw_tab_list_file_one <- purrr::map(purrr::set_names(excel_sheets(file.path(sharepoint_ojjdp_va_raw_data,
                                                              "CSG Front End data 01202023 - pt1 - SENSITIVE.xlsx"))),
                      read_excel, 
                      path = file.path(sharepoint_ojjdp_va_raw_data,"CSG Front End data 01202023 - pt1 - SENSITIVE.xlsx")) %>% 
  purrr::map(janitor::clean_names)

### clean names of all imported tabs before converting to dataframes
names(ojjdp_va_raw_tab_list_file_one) <- janitor::make_clean_names(names(ojjdp_va_raw_tab_list_file_one))

### then convert list of tabs to distinct dataframes with names from tabs
purrr::map(names(ojjdp_va_raw_tab_list_file_one),
           ~assign(.x, 
                   ojjdp_va_raw_tab_list_file_one[[.x]], 
        envir = .GlobalEnv)) 

########################################################
### now import second file from djj -- with only one tab
########################################################
df_djj_intake_complaints_raw <- openxlsx::read.xlsx(file.path(sharepoint_ojjdp_va_raw_data,
                                                              "CSG Front End data 01202023 - pt2 - SENSITIVE.xlsx"),
                                                    sheet = 1) %>% 
  clean_names()
```

```{r include=FALSE, message=FALSE, warning=FALSE}
#############################################
### clean and de-dup df_djj_intake_complaints_raw dataframe
### this is our base file for the sample
#############################################
df_djj_intake_complaints_clean <- df_djj_intake_complaints_raw %>% 
  distinct(juvenile_number,
           case_number,
           offense_number,
           .keep_all=TRUE) %>% ### no records dropped
  ### clean race/ethnicity and gender
  ### use factor function to assign labels to values
  mutate(race_clean = case_when(
    race=="I" & hispanic!="Y" ~ 1,
    race=="A" & hispanic!="Y" ~ 2,
    race=="B" & hispanic!="Y" ~ 3,
    hispanic=="Y" ~ 4,
    race=="W" & hispanic!="Y" ~ 5,
    race %in% c("X","O") & hispanic!="Y" ~ 6,
    TRUE ~ 7),
    race_clean = factor(race_clean,
         levels = c(1,2,3,4,5,6,7),
         labels = c("American Indian", "Asian", "Black", "Hispanic", "White", "Other","Missing"))) %>% 
  mutate(gender_clean = case_when(
    sex=="F" ~ 1,
    sex=="M" ~ 2,
    TRUE ~ as.numeric(NA)),
    gender_clean = factor(gender_clean,
         levels = c(1,2),
         labels = c("Female", "Male"))) %>%   
### clean dates and create year for potential grouping in future trend analysis
  mutate(date_opened = ymd(as_date(excel_numeric_to_date(as.numeric(as.character(date_opened)), 
                                                  date_system = "modern"))),
         ysai_date = ymd(as_date(ysai_date)),
         date_opened_year = year(date_opened)) 

########################################
### clean and de-dup disposition dataframe
########################################
### note: disposition file is unique by youth, case number, offense number, disposition, amd days from intake to disposition
disposition_clean <- disposition %>% 
  distinct(juvenile_number,
           case_number,
           offense_number,
           description,
           .keep_all=TRUE) ### no records dropped
  
  ### next step: de-dup by disposition -- keeping most serious?
  

########################################
### clean and de-dup caseload dataframe
########################################
caseload_clean <- caseload %>% 
  distinct(juvenile_number,
           offense_number,
           .keep_all=TRUE) ### need to look into duplicates

```

<br>

# Sample Descriptives

**Data Sample:** 

* Juvenile intake complaints with intake dates from July 1, 2015 - June 30, 2021

* Dispositions – all dispositions for the intake complaints in the sample. 

* Caseload – all intake complaints in the sample that are associated with a workload status for diversion - "Diversion At Intake" or "Diversion Program Beyond 90 Days"



## Table 1. Unique Youth and Complaints by Year (Year of Complaint)

```{r echo=FALSE,warning=FALSE,message=FALSE}
### create denominator -- unique complaint for entire sample
unique_complaints_sample_denom <- n_distinct(df_djj_intake_complaints_clean$juvenile_number,
                                            df_djj_intake_complaints_clean$case_number)

### create denominator -- unique youth for entire sample
unique_youth_sample_denom <- n_distinct(df_djj_intake_complaints_clean$juvenile_number)

### unique youth and complaints per year
df_complaints_youth_per_year <- df_djj_intake_complaints_clean %>% 
  dplyr::group_by(date_opened_year) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(juvenile_number),
            `Unique Complaints (N)` = n_distinct(juvenile_number,case_number),
            `Complaints, Percent of Sample (%)` = scales::percent(`Unique Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Year of Complaint` = date_opened_year) %>% 
  mutate(`Year of Complaint` = as.character(`Year of Complaint`))

### overall
df_complaints_youth_overall <- df_djj_intake_complaints_clean %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(juvenile_number),
            `Unique Complaints (N)` = n_distinct(juvenile_number,case_number),
            `Complaints, Percent of Sample (%)` = scales::percent(`Unique Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1)) %>%  
  mutate(`Year of Complaint` = "Overall")

### combine tables for kable
df_complaints_youth_per_year_table <- rbind(df_complaints_youth_per_year,
                                           df_complaints_youth_overall)

### print table via kableextra
kable(df_complaints_youth_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(8, bold = TRUE)
```

<br>

## Table 2: Unique Youth and Complaints by Race/Ethnicity

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth and complaints per year
df_complaints_youth_race <- df_djj_intake_complaints_clean %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(juvenile_number),
            `Unique Youth, Percent of Sample (%)` = scales::percent(`Unique Youth (N)`/unique_youth_sample_denom,
                                                                       accuracy = .1),
            `Unique Complaints (N)` = n_distinct(juvenile_number,case_number),
            `Complaints, Percent of Sample (%)` = scales::percent(`Unique Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean) %>% 
  mutate(`Race/Ethnicity` = as.character(`Race/Ethnicity`))

### overall
df_complaints_youth_overall_race <- df_djj_intake_complaints_clean %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(juvenile_number),
            `Unique Youth, Percent of Sample (%)` = scales::percent(`Unique Youth (N)`/unique_youth_sample_denom,
                                                                       accuracy = .1),
            `Unique Complaints (N)` = n_distinct(juvenile_number,case_number),
            `Complaints, Percent of Sample (%)` = scales::percent(`Unique Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1)) %>%  
  mutate(`Race/Ethnicity` = "Overall")

### combine tables for kable
df_complaints_youth_race_table <- rbind(df_complaints_youth_race,
                                       df_complaints_youth_overall_race)

### print table via kableextra
kable(df_complaints_youth_race_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(8, bold = TRUE)
```

<br>

## Table 3: Unique Youth and Complaints by Intake Type

```{r echo=FALSE,message=FALSE,warning=FALSE}
### clean up codebook values that we need
codebook_intake_decision_values <- codebook %>% 
  filter(field_name=="INTAKE_DECISION") %>% 
  dplyr::select(intake_decision=code,
                intake_decision_label=options,
                intake_decision_description=definitions) %>% 
  mutate(intake_decision = as.numeric(intake_decision))

### unique youth and complaints per year
df_complaints_youth_intake_decision <- df_djj_intake_complaints_clean %>% 
  mutate(intake_decision = as.numeric(intake_decision)) %>% 
  left_join(codebook_intake_decision_values,
            by = "intake_decision") %>% 
  dplyr::group_by(intake_decision_label) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(juvenile_number),
            `Unique Youth, Percent of Sample (%)` = scales::percent(`Unique Youth (N)`/unique_youth_sample_denom,
                                                                       accuracy = .1),
            `Unique Complaints (N)` = n_distinct(juvenile_number,case_number),
            `Complaints, Percent of Sample (%)` = scales::percent(`Unique Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Intake Decision` = intake_decision_label) 


### print table via kableextra
kable(df_complaints_youth_intake_decision, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Table 4: Unique Youth and Complaints by Petitioner Type

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth and complaints per year
df_complaints_youth_pet_type <- df_djj_intake_complaints_clean %>% 
  dplyr::group_by(petitioner_desc) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(juvenile_number),
            `Unique Youth, Percent of Sample (%)` = scales::percent(`Unique Youth (N)`/unique_youth_sample_denom,
                                                                       accuracy = .1),
            `Unique Complaints (N)` = n_distinct(juvenile_number,case_number),
            `Complaints, Percent of Sample (%)` = scales::percent(`Unique Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Petitioner Type` = petitioner_desc) 


### print table via kableextra
kable(df_complaints_youth_pet_type, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Table 5: Unique Youth and Complaints by Offense Type

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth and complaints per year
df_complaints_youth_offense_type <- df_djj_intake_complaints_clean %>% 
  dplyr::group_by(dai) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(juvenile_number),
            `Unique Youth, Percent of Sample (%)` = scales::percent(`Unique Youth (N)`/unique_youth_sample_denom,
                                                                       accuracy = .1),
            `Unique Complaints (N)` = n_distinct(juvenile_number,case_number),
            `Complaints, Percent of Sample (%)` = scales::percent(`Unique Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Offense Description` = dai) 


### print table via kableextra
kable(df_complaints_youth_offense_type, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Table 6: Unique Youth and Complaints by Delinquent/Status/Technical Flag

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth and complaints per year
df_complaints_youth_offense_type_flag <- df_djj_intake_complaints_clean %>% 
  dplyr::group_by(flg_category) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(juvenile_number),
            `Unique Youth, Percent of Sample (%)` = scales::percent(`Unique Youth (N)`/unique_youth_sample_denom,
                                                                       accuracy = .1),
            `Unique Complaints (N)` = n_distinct(juvenile_number,case_number),
            `Complaints, Percent of Sample (%)` = scales::percent(`Unique Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Delinquent/Status/Technical Flag` = flg_category) 


### print table via kableextra
kable(df_complaints_youth_offense_type_flag, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Table 7: Unique Youth and Complaints by Disposition Type

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth and complaints per year
df_complaints_youth_dispo <- disposition_clean %>% 
  dplyr::group_by(description) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(juvenile_number),
            `Unique Youth, Percent of Sample (%)` = scales::percent(`Unique Youth (N)`/unique_youth_sample_denom,
                                                                       accuracy = .1),
            `Unique Complaints (N)` = n_distinct(juvenile_number,case_number),
            `Complaints, Percent of Sample (%)` = scales::percent(`Unique Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Disposition` = description) 


### print table via kableextra
kable(df_complaints_youth_dispo, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>
