---
title: "Sample Descriptive Statistics"
format: html
---

In this file, we'll import all of the Virginia DJJ files provided and create preliminary cross-tabulations and merges to explore basic counts, trends, and double check primary keys and joins across the data files. 

See `Codebooks` and `Data Diagram` tabs for more information on each individual data file. 

TBD

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())
```

```{r include=FALSE}
### pull in virginia djj data from raw data folder

### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_raw_data <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Data/VA/raw"))

########################################################
### import first excel file w/ multiple tabs with purrr
########################################################

### using purrr::map, import list of tabs from excel worksheet
ojjdp_va_raw_tab_list_file_one <- purrr::map(purrr::set_names(excel_sheets(file.path(sharepoint_ojjdp_va_raw_data,
                                                              "CSG Front End data 01202023 - pt1 - SENSITIVE.xlsx"))),
                      read_excel, 
                      path = file.path(sharepoint_ojjdp_va_raw_data,"CSG Front End data 01202023 - pt1 - SENSITIVE.xlsx")) %>% 
  purrr::map(janitor::clean_names)

### clean names of all imported tabs before converting to dataframes
names(ojjdp_va_raw_tab_list_file_one) <- janitor::make_clean_names(names(ojjdp_va_raw_tab_list_file_one))

### then convert list of tabs to distinct dataframes with names from tabs
purrr::map(names(ojjdp_va_raw_tab_list_file_one),
           ~assign(.x, 
                   ojjdp_va_raw_tab_list_file_one[[.x]], 
        envir = .GlobalEnv)) 

########################################################
### now import second file from djj -- with only one tab
########################################################
df_djj_intake_complaints_raw <- openxlsx::read.xlsx(file.path(sharepoint_ojjdp_va_raw_data,
                                                              "CSG Front End data 01202023 - pt2 - SENSITIVE.xlsx"),
                                                    sheet = 1) %>% 
  clean_names()
```

```{r eval=FALSE,include=FALSE}
#############################################
### clean and de-dup child dataframe
### this is our base demo file for the sample
#############################################
child_clean <- child %>% 
  distinct(unique_id,
           .keep_all=TRUE) %>% ### no records dropped
  ### clean race/ethnicity and gender
  mutate(race_clean = case_when(
    race=="Asian or Pacific Islander" & ethnicity!="Hispanic" ~ 1,
    race=="Black" & ethnicity!="Hispanic" ~ 2,
    ethnicity=="Hispanic" ~ 3,
    race=="White" & ethnicity!="Hispanic" ~ 4,
    race %in% c("Unknown","American Indian or Alaskan Native") & ethnicity!="Hispanic" ~ 5,
    TRUE ~ as.numeric(NA)),
    race_clean = factor(race_clean,
         levels = c(1,2,3,4,5),
         labels = c("Asian", "Black", "Hispanic", "White", "Other"))) %>% 
  mutate(gender_clean = case_when(
    gender=="Female" ~ 1,
    gender=="Male" ~ 2,
    TRUE ~ as.numeric(NA)),
    gender_clean = factor(gender_clean,
         levels = c(1,2),
         labels = c("Female", "Male"))) ### use factor function to assign labels to values

########################################
### clean and de-dup offenses dataframe
########################################
offenses_clean <- offenses %>% 
  distinct(unique_id,
           referral_number,
           offense_id,
           .keep_all=TRUE) %>% ### no records dropped
  ### clean dates and create years for potential grouping in future trend analysis
  mutate(offense_date = ymd(as_date(offense_date)),
         referral_date = ymd(as_date(referral_date)),
         disposition_date = ymd(as_date(excel_numeric_to_date(as.numeric(as.character(disposition_date)), 
                                                  date_system = "modern"))),         
         offense_year = year(offense_date),
         referral_year = year(referral_date),
         disposition_year = year(disposition_date)) %>% 
  ### create unique referral ID and unique offense ID for possible filtering or counting
  mutate(unique_referral_id = paste0(unique_id,
                                     referral_number),
         unique_offense_id = paste0(unique_id,
                                    referral_number,
                                    offense_id)) %>% 
  ### calculate number of offenses per referral by grouping by unique_referral_id
  group_by(unique_referral_id) %>% 
  mutate(unique_offenses_per_referral_count = n_distinct(unique_offense_id,
                                                         na.rm = TRUE)) %>% 
  ungroup()

########################################
### clean and de-dup supervision dataframe
########################################
supervision_clean <- supervision %>% 
  distinct(unique_id,
           referral_number,
           supervision_begin_date,
           .keep_all=TRUE) %>% ### 1 record dropped (note: 170 recods have duplicated IDs but different begin dates)
  ### clean dates and create years for potential grouping in future trend analysis
  mutate(supervision_begin_date = ymd(as_date(supervision_begin_date)),
         supervision_end_date = ymd(as_date(supervision_end_date)),
         supervision_begin_year = year(supervision_begin_date),
         supervision_end_year = year(supervision_end_date)) %>% 
  ### create unique referral ID possible filtering, joining, or counting
  mutate(unique_referral_id = paste0(unique_id,
                                     referral_number)) 

#############################################
### clean and de-dup supervision_level dataframe
#############################################

### by unique_id, referral_number, phase_begin_date, phase_end_date
supervision_level_clean <- supervision_level %>% 
  distinct(unique_id,
           referral_number,
           phase,
           phase_begin_date,
           phase_end_date,
           .keep_all=TRUE) ### 1 record dropped 
```

<br>

# Sample Descriptives

**Data Sample:** 

* Juvenile intake complaints with intake dates from July 1, 2015 - June 30, 2021

* Dispositions – all dispositions for the intake complaints in the sample. 

* Caseload – all intake complaints in the sample that are associated with a workload status for diversion - "Diversion At Intake" or "Diversion Program Beyond 90 Days"



## Table 1. Unique Youth and Referrals by Year (Year of Referral)

```{r eval=FALSE,include=FALSE}
### create denominator -- unique referrals for entire sample
unique_referrals_sample_denom <- n_distinct(offenses_clean$unique_id,
                                            offenses_clean$referral_number)

### create denominator -- unique youth for entire sample
unique_youth_sample_denom <- n_distinct(offenses_clean$unique_id)

### unique youth and referrals per year
df_referrals_youth_per_year <- offenses_clean %>% 
  dplyr::group_by(referral_year) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Referrals, Percent of Sample (%)` = scales::percent(`Unique Referrals (N)`/unique_referrals_sample_denom,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Year of Referral` = referral_year) %>% 
  mutate(`Year of Referral` = as.character(`Year of Referral`))

### overall
df_referrals_youth_overall <- offenses_clean %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Referrals, Percent of Sample (%)` = scales::percent(`Unique Referrals (N)`/unique_referrals_sample_denom,
                                                                       accuracy = .1)) %>% 
  mutate(`Year of Referral` = "Overall")

### combine tables for kable
df_referrals_youth_per_year_table <- rbind(df_referrals_youth_per_year,df_referrals_youth_overall)

### print table via kableextra
kable(df_referrals_youth_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(14, bold = TRUE)
```

```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
## Join 1. Join of `Child` and `Offenses`

### left join of child file to offenses file in order to see if there is much missingness
### i.e. are there offenses without demo records? 
offenses_child_demo_join <- 
  left_join(offenses_clean,
            child_clean,
            by = "unique_id") ### join looks good; all records join
```

<br>
