---
title: "Analysis: Part I"
format: html
---


**Research Questions:**


Using a cohort of first-time system involved youth, look at adjusted differences in likelihood of being diverted and likelihood of a re-complaint for diverted vs. non-diverted youth.

A. How does the likelihood of being diverted differ by race, sex, and geography?

B. For youth who are diverted, how likely are they to come back into the system with a new complaint or new petition within a year of the initial intake decision? 

<br>

**Methods:**

For research question (A) we will build a series of logistic regression models, adjusting for race/ethnicity, age, offense, risk level, and other factors that may also be related to a decision to divert. Our outcome variable will be diversion/petition (0/1) and our independent variables of interest will be race, sex, and CSU. For research question (B) we will take a similar methodological approach, but restrict our cohort to diverted youth and focus on likelihood of a re-complaint within a year of diversion while adjusting for demographics, offense, risk level, etc. For research question (B) our outcome variable will be re-complaint within a year of the initial intake decision date (0/1) and our independent variables of interest will be race, sex, and CSU.

*Cohort:* first time system involved youth (no prior complaints), 2016-2021

*Method:* Logistic Regression, which allows us to look at the relationship between two variables (like race and decision to divert) while adjusting for other factors that may also be related to our outcome (like offense, risk, etc.).

<br>

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())
```

```{r include=FALSE}
### pull in virginia djj data from raw data folder

### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_raw_data <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Data/VA/raw"))

########################################################
### import first excel file w/ multiple tabs with purrr
########################################################

### using purrr::map, import list of tabs from excel worksheet
ojjdp_va_raw_tab_list_file_one <- purrr::map(purrr::set_names(excel_sheets(file.path(sharepoint_ojjdp_va_raw_data,
                                                              "CSG Front End data 01202023 - pt1 - SENSITIVE.xlsx"))),
                      read_excel, 
                      path = file.path(sharepoint_ojjdp_va_raw_data,"CSG Front End data 01202023 - pt1 - SENSITIVE.xlsx")) %>% 
  purrr::map(janitor::clean_names)

### clean names of all imported tabs before converting to dataframes
names(ojjdp_va_raw_tab_list_file_one) <- janitor::make_clean_names(names(ojjdp_va_raw_tab_list_file_one))

### then convert list of tabs to distinct dataframes with names from tabs
purrr::map(names(ojjdp_va_raw_tab_list_file_one),
           ~assign(.x, 
                   ojjdp_va_raw_tab_list_file_one[[.x]], 
        envir = .GlobalEnv)) 

########################################################
### now import second file from djj -- with only one tab
########################################################
df_djj_intake_complaints_raw <- openxlsx::read.xlsx(file.path(sharepoint_ojjdp_va_raw_data,
                                                              "CSG Front End data 01202023 - pt2 - SENSITIVE.xlsx"),
                                                    sheet = 1) %>% 
  clean_names()
```

```{r include=FALSE, message=FALSE, warning=FALSE}
#############################################
### clean and de-dup df_djj_intake_complaints_raw dataframe
### this is our base file for the sample
#############################################
df_djj_intake_complaints_clean <- df_djj_intake_complaints_raw %>% 
  distinct(juvenile_number,
           case_number,
           offense_number,
           .keep_all=TRUE) %>% ### no records dropped
  ### clean race/ethnicity and gender
  ### use factor function to assign labels to values
  mutate(race_clean = case_when(
    race=="I" & hispanic!="Y" ~ 1,
    race=="A" & hispanic!="Y" ~ 2,
    race=="B" & hispanic!="Y" ~ 3,
    hispanic=="Y" ~ 4,
    race=="W" & hispanic!="Y" ~ 5,
    race %in% c("X","O") & hispanic!="Y" ~ 6,
    TRUE ~ 7),
    race_clean = factor(race_clean,
         levels = c(1,2,3,4,5,6,7),
         labels = c("American Indian", "Asian", "Black", "Hispanic", "White", "Other","Missing"))) %>% 
  mutate(gender_clean = case_when(
    sex=="F" ~ 1,
    sex=="M" ~ 2,
    TRUE ~ as.numeric(NA)),
    gender_clean = factor(gender_clean,
         levels = c(1,2),
         labels = c("Female", "Male"))) %>%   
### clean dates and create year for potential grouping in future trend analysis
  mutate(date_opened = ymd(as_date(excel_numeric_to_date(as.numeric(as.character(date_opened)), 
                                                  date_system = "modern"))),
         ysai_date = ymd(as_date(ysai_date)),
         date_opened_year = year(date_opened)) 

########################################
### clean and de-dup disposition dataframe
########################################
### note: disposition file is unique by youth, case number, offense number, disposition, amd days from intake to disposition
disposition_clean <- disposition %>% 
  distinct(juvenile_number,
           case_number,
           offense_number,
           description,
           .keep_all=TRUE) ### no records dropped
  
  ### next step: de-dup by disposition -- keeping most serious?
  

########################################
### clean and de-dup caseload dataframe
########################################
caseload_clean <- caseload %>% 
  distinct(juvenile_number,
           offense_number,
           .keep_all=TRUE) ### need to look into duplicates

```

<br>

