---
title: "Part II Analysis: Disposition"
format: html
---

**Data Sample:** 

* Juvenile intake complaints with intake dates from July 1, 2015 - June 30, 2021

* Dispositions – all dispositions for the intake complaints in the sample. 


**Research Question:**

Conduct a front-end system assessment from intake through petition for all complaints 2016-2021.


**Methods:**

We will conduct a descriptive analysis of the front end of the system from intake through petition, provide unadjusted counts, RRI’s and means tests where applicable, by race, sex, offense, risk, CSU, and year for:

*	Complaints

*	Intake decisions: divert, resolve, petition, other

*	Average LOS on diversion 

*	Diversion completions: successful, unsuccessful, other

*	Dispositions on petitioned cases

*Cohort:* All complaints from 2016-2021  

<br>

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())

### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_analysis_analytic_data <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Data/VA/analysis/analytic"))

### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_viz <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Output/VA/r_viz_output"))
```

```{r include=FALSE}
### pull in virginia djj analytic files 

# ### read in df_analytic_complaints_disposition_caseload.rds analytic rds file 
# disposition_clean <- read_rds(file.path(sharepoint_ojjdp_va_analysis_analytic_data,"disposition_clean.rds"))

### read in df_analytic_complaints_disposition_caseload file for analysis
df_analytic_complaints_disposition_caseload <- read_rds(file.path(sharepoint_ojjdp_va_analysis_analytic_data,"df_analytic_complaints_disposition_caseload.rds"))
```

```{r include=FALSE,warning=FALSE,include=FALSE}
### create denominator -- unique complaint for entire sample
unique_complaints_sample_denom <- n_distinct(df_analytic_complaints_disposition_caseload$unique_complaint_id)

### create denominator -- unique youth for entire sample
unique_youth_sample_denom <- n_distinct(df_analytic_complaints_disposition_caseload$juvenile_number)
```

<br>

**NOTE:** Because dispositions file is still duplicated (one complaint may have multiple associated dispositions), percentages will not add up to 100 -- we need to create ranking of disposition severity and de-duplicate this file by selecting the most serious disposition associated with a complaint as a next step. 



**Business rules to discuss:** 

* For disposition file cleaning/analysis, should I first filter on intake complaint==petitioned, then merge to dispositions file? We would need to expand current definition of petitioned to include unsuccessful diversions that were eventually petitioned, right? 

# Tables


## Table 1: Disposition Outcomes, 2015-2021

Note: The preliminary options for grouping dispositions that I am using are: Detention, Commitment, Probation/Supervision, Deferral, Community Service, Fine, No further action/none, Restitution, Other. See the `Disposition, Preliminary Disposition Groupings` table on the `codebook` page in the `sample descriptives` tab for a full list of each disposition and I've grouped it. 

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### overall complaints by diversion status
df_complaints_disposition_outcome_table <- df_analytic_complaints_disposition_caseload %>% 
  dplyr::group_by(dispo_description_clean) %>% 
  dplyr::summarise(`Unique Disposed Complaints (N)` = n_distinct(unique_complaint_id),
            `Disposed Complaints, Percent of Sample (%)` = scales::percent(`Unique Disposed Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Disposition` = dispo_description_clean) 


### print table via kableextra
kable(df_complaints_disposition_outcome_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Table 2: Disposition Outcomes by Year

Note: The preliminary options for grouping dispositions that I am using are: Detention, Commitment, Probation/Supervision, Deferral, Community Service, Fine, No further action/none, Restitution, Other. See the `Disposition, Preliminary Disposition Groupings` table on the `codebook` page in the `sample descriptives` tab for a full list of each disposition and I've grouped it. 

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_disposition_outcome_table_year <- df_analytic_complaints_disposition_caseload %>% 
  dplyr::group_by(date_opened_year) %>% 
  dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Disposed Complaints (column %)` = scales::percent(`All Disposed Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Detention (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Detention"]),
                   `Detention (row %)` = scales::percent(`Detention (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Commitment (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Commitment"]),
                   `Commitment (row %)` = scales::percent(`Commitment (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row %)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Deferral (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Deferral"]),
                   `Deferral (row %)` = scales::percent(`Deferral (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Community Service (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Community Service"]),
                   `Community Service (row %)` = scales::percent(`Community Service (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Fine (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Fine"]),
                   `Fine (row %)` = scales::percent(`Fine (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `No further action/none (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="No further action/none"]),
                   `No further action/none (row %)` = scales::percent(`No further action/none (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Restitution (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Restitution"]),
                   `Restitution (row %)` = scales::percent(`Restitution (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Year of Complaint` = date_opened_year) 

### unique complaints statewide
df_complaints_disposition_outcome_table_overall <- df_analytic_complaints_disposition_caseload %>% 
     dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Disposed Complaints (column %)` = scales::percent(`All Disposed Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Detention (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Detention"]),
                   `Detention (row %)` = scales::percent(`Detention (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Commitment (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Commitment"]),
                   `Commitment (row %)` = scales::percent(`Commitment (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row %)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Deferral (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Deferral"]),
                   `Deferral (row %)` = scales::percent(`Deferral (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Community Service (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Community Service"]),
                   `Community Service (row %)` = scales::percent(`Community Service (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Fine (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Fine"]),
                   `Fine (row %)` = scales::percent(`Fine (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `No further action/none (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="No further action/none"]),
                   `No further action/none (row %)` = scales::percent(`No further action/none (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Restitution (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Restitution"]),
                   `Restitution (row %)` = scales::percent(`Restitution (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Year of Complaint` = "Overall") 

### combine two dataframes for table
df_complaints_disposition_outcome_table_year_final <- rbind(df_complaints_disposition_outcome_table_year,
                                                              df_complaints_disposition_outcome_table_overall)


### print table via kableextra
kable(df_complaints_disposition_outcome_table_year_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(8, bold = TRUE)
```


<br>

## Table 3: Disposition Outcomes by YASI Risk Level

**TO DO:** Double check that I’m using correct YASI assessment for dispo exploration (does it matter if it is initial, case closure, etc.?)

Note: The preliminary options for grouping dispositions that I am using are: Detention, Commitment, Probation/Supervision, Deferral, Community Service, Fine, No further action/none, Restitution, Other. See the `Disposition, Preliminary Disposition Groupings` table on the `codebook` page in the `sample descriptives` tab for a full list of each disposition and I've grouped it. 

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_disposition_outcome_table_risk_score <- df_analytic_complaints_disposition_caseload %>% 
  dplyr::group_by(risk_level_clean) %>% 
      dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Disposed Complaints (column %)` = scales::percent(`All Disposed Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Detention (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Detention"]),
                   `Detention (row %)` = scales::percent(`Detention (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Commitment (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Commitment"]),
                   `Commitment (row %)` = scales::percent(`Commitment (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row %)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Deferral (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Deferral"]),
                   `Deferral (row %)` = scales::percent(`Deferral (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Community Service (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Community Service"]),
                   `Community Service (row %)` = scales::percent(`Community Service (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Fine (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Fine"]),
                   `Fine (row %)` = scales::percent(`Fine (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `No further action/none (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="No further action/none"]),
                   `No further action/none (row %)` = scales::percent(`No further action/none (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Restitution (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Restitution"]),
                   `Restitution (row %)` = scales::percent(`Restitution (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Risk Score` = risk_level_clean) 

### unique complaints statewide
df_complaints_disposition_outcome_table_overall <- df_analytic_complaints_disposition_caseload %>% 
   dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Disposed Complaints (column %)` = scales::percent(`All Disposed Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Detention (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Detention"]),
                   `Detention (row %)` = scales::percent(`Detention (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Commitment (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Commitment"]),
                   `Commitment (row %)` = scales::percent(`Commitment (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row %)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Deferral (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Deferral"]),
                   `Deferral (row %)` = scales::percent(`Deferral (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Community Service (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Community Service"]),
                   `Community Service (row %)` = scales::percent(`Community Service (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Fine (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Fine"]),
                   `Fine (row %)` = scales::percent(`Fine (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `No further action/none (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="No further action/none"]),
                   `No further action/none (row %)` = scales::percent(`No further action/none (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Restitution (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Restitution"]),
                   `Restitution (row %)` = scales::percent(`Restitution (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Risk Score` = "Overall") 

### combine two dataframes for table
df_complaints_disposition_outcome_table_risk_score_final <- rbind(df_complaints_disposition_outcome_table_risk_score,df_complaints_disposition_outcome_table_overall)


### print table via kableextra
kable(df_complaints_disposition_outcome_table_risk_score_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(4, bold = TRUE)
```

<br>

## Table 4: Disposition Outcomes by Gender

Note: The preliminary options for grouping dispositions that I am using are: Detention, Commitment, Probation/Supervision, Deferral, Community Service, Fine, No further action/none, Restitution, Other. See the `Disposition, Preliminary Disposition Groupings` table on the `codebook` page in the `sample descriptives` tab for a full list of each disposition and I've grouped it. 

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_disposition_outcome_table_gender <- df_analytic_complaints_disposition_caseload %>% 
  dplyr::group_by(gender_clean) %>% 
      dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Disposed Complaints (column %)` = scales::percent(`All Disposed Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Detention (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Detention"]),
                   `Detention (row %)` = scales::percent(`Detention (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Commitment (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Commitment"]),
                   `Commitment (row %)` = scales::percent(`Commitment (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row %)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Deferral (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Deferral"]),
                   `Deferral (row %)` = scales::percent(`Deferral (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Community Service (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Community Service"]),
                   `Community Service (row %)` = scales::percent(`Community Service (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Fine (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Fine"]),
                   `Fine (row %)` = scales::percent(`Fine (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `No further action/none (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="No further action/none"]),
                   `No further action/none (row %)` = scales::percent(`No further action/none (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Restitution (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Restitution"]),
                   `Restitution (row %)` = scales::percent(`Restitution (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Gender` = gender_clean) 

### unique complaints statewide
df_complaints_disposition_outcome_table_overall <- df_analytic_complaints_disposition_caseload %>% 
   dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Disposed Complaints (column %)` = scales::percent(`All Disposed Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Detention (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Detention"]),
                   `Detention (row %)` = scales::percent(`Detention (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Commitment (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Commitment"]),
                   `Commitment (row %)` = scales::percent(`Commitment (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row %)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Deferral (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Deferral"]),
                   `Deferral (row %)` = scales::percent(`Deferral (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Community Service (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Community Service"]),
                   `Community Service (row %)` = scales::percent(`Community Service (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Fine (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Fine"]),
                   `Fine (row %)` = scales::percent(`Fine (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `No further action/none (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="No further action/none"]),
                   `No further action/none (row %)` = scales::percent(`No further action/none (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Restitution (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Restitution"]),
                   `Restitution (row %)` = scales::percent(`Restitution (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Gender` = "Overall") 

### combine two dataframes for table
df_complaints_disposition_outcome_table_gender_final <- rbind(df_complaints_disposition_outcome_table_gender,
                                                              df_complaints_disposition_outcome_table_overall)


### print table via kableextra
kable(df_complaints_disposition_outcome_table_gender_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE)
```

<br>

## Table 5: Disposition Outcomes by Age at Disposition

Note: The preliminary options for grouping dispositions that I am using are: Detention, Commitment, Probation/Supervision, Deferral, Community Service, Fine, No further action/none, Restitution, Other. See the `Disposition, Preliminary Disposition Groupings` table on the `codebook` page in the `sample descriptives` tab for a full list of each disposition and I've grouped it. 

**TO DO:** Decide on which ages to exclude because of likely data collection issues (e.g. ages of 0 or 44); current process is removing youth <8 and >18

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_disposition_outcome_table_age <- df_analytic_complaints_disposition_caseload %>% 
   filter(court_disp_age>8,
         court_disp_age<18) %>% 
  dplyr::group_by(dispo_age_clean) %>% 
   dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Disposed Complaints (column %)` = scales::percent(`All Disposed Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Detention (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Detention"]),
                   `Detention (row %)` = scales::percent(`Detention (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Commitment (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Commitment"]),
                   `Commitment (row %)` = scales::percent(`Commitment (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row %)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Deferral (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Deferral"]),
                   `Deferral (row %)` = scales::percent(`Deferral (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Community Service (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Community Service"]),
                   `Community Service (row %)` = scales::percent(`Community Service (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Fine (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Fine"]),
                   `Fine (row %)` = scales::percent(`Fine (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `No further action/none (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="No further action/none"]),
                   `No further action/none (row %)` = scales::percent(`No further action/none (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Restitution (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Restitution"]),
                   `Restitution (row %)` = scales::percent(`Restitution (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Age at Intake` = dispo_age_clean) 

### unique complaints statewide
df_complaints_disposition_outcome_table_overall <- df_analytic_complaints_disposition_caseload %>% 
   filter(court_disp_age>8,
         court_disp_age<18) %>% 
     dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Disposed Complaints (column %)` = scales::percent(`All Disposed Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Detention (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Detention"]),
                   `Detention (row %)` = scales::percent(`Detention (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Commitment (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Commitment"]),
                   `Commitment (row %)` = scales::percent(`Commitment (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row %)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Deferral (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Deferral"]),
                   `Deferral (row %)` = scales::percent(`Deferral (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Community Service (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Community Service"]),
                   `Community Service (row %)` = scales::percent(`Community Service (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Fine (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Fine"]),
                   `Fine (row %)` = scales::percent(`Fine (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `No further action/none (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="No further action/none"]),
                   `No further action/none (row %)` = scales::percent(`No further action/none (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Restitution (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Restitution"]),
                   `Restitution (row %)` = scales::percent(`Restitution (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Age at Intake` = "Overall") 

### combine two dataframes for table
df_complaints_disposition_outcome_table_age_final <- rbind(df_complaints_disposition_outcome_table_age,
                                                              df_complaints_disposition_outcome_table_overall)


### print table via kableextra
kable(df_complaints_disposition_outcome_table_age_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE)
```

<br>

## Table 6a: Disposition Outcomes by Offense Type (most serious offense; mso_flag == "Y")

Note: The preliminary options for grouping dispositions that I am using are: Detention, Commitment, Probation/Supervision, Deferral, Community Service, Fine, No further action/none, Restitution, Other. See the `Disposition, Preliminary Disposition Groupings` table on the `codebook` page in the `sample descriptives` tab for a full list of each disposition and I've grouped it. 

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_disposition_outcome_table_offense <- df_analytic_complaints_disposition_caseload %>% 
  dplyr::group_by(dai) %>% 
    dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Disposed Complaints (column %)` = scales::percent(`All Disposed Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Detention (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Detention"]),
                   `Detention (row %)` = scales::percent(`Detention (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Commitment (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Commitment"]),
                   `Commitment (row %)` = scales::percent(`Commitment (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row %)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Deferral (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Deferral"]),
                   `Deferral (row %)` = scales::percent(`Deferral (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Community Service (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Community Service"]),
                   `Community Service (row %)` = scales::percent(`Community Service (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Fine (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Fine"]),
                   `Fine (row %)` = scales::percent(`Fine (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `No further action/none (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="No further action/none"]),
                   `No further action/none (row %)` = scales::percent(`No further action/none (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Restitution (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Restitution"]),
                   `Restitution (row %)` = scales::percent(`Restitution (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Offense Description` = dai)  

### unique complaints statewide
df_complaints_disposition_outcome_table_overall <- df_analytic_complaints_disposition_caseload %>% 
   dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Disposed Complaints (column %)` = scales::percent(`All Disposed Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Detention (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Detention"]),
                   `Detention (row %)` = scales::percent(`Detention (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Commitment (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Commitment"]),
                   `Commitment (row %)` = scales::percent(`Commitment (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row %)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Deferral (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Deferral"]),
                   `Deferral (row %)` = scales::percent(`Deferral (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Community Service (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Community Service"]),
                   `Community Service (row %)` = scales::percent(`Community Service (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Fine (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Fine"]),
                   `Fine (row %)` = scales::percent(`Fine (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `No further action/none (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="No further action/none"]),
                   `No further action/none (row %)` = scales::percent(`No further action/none (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Restitution (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Restitution"]),
                   `Restitution (row %)` = scales::percent(`Restitution (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Offense Description` = "Overall") 

### combine two dataframes for table
df_complaints_disposition_outcome_table_offense_final <- rbind(df_complaints_disposition_outcome_table_offense,
                                                              df_complaints_disposition_outcome_table_overall)


### print table via kableextra
kable(df_complaints_disposition_outcome_table_offense_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(10, bold = TRUE)
```

<br>

## Table 6b: Disposition Outcomes by Status Offense Type (most serious offense is status; mso_flag == "Y")

Note: The preliminary options for grouping dispositions that I am using are: Detention, Commitment, Probation/Supervision, Deferral, Community Service, Fine, No further action/none, Restitution, Other. See the `Disposition, Preliminary Disposition Groupings` table on the `codebook` page in the `sample descriptives` tab for a full list of each disposition and I've grouped it. 

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_disposition_outcome_table_offense_status <- df_analytic_complaints_disposition_caseload %>% 
  filter(dai=="Status Offense") %>% 
  dplyr::group_by(drg) %>% 
    dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Disposed Complaints (column %)` = scales::percent(`All Disposed Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Detention (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Detention"]),
                   `Detention (row %)` = scales::percent(`Detention (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Commitment (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Commitment"]),
                   `Commitment (row %)` = scales::percent(`Commitment (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row %)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Deferral (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Deferral"]),
                   `Deferral (row %)` = scales::percent(`Deferral (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Community Service (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Community Service"]),
                   `Community Service (row %)` = scales::percent(`Community Service (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Fine (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Fine"]),
                   `Fine (row %)` = scales::percent(`Fine (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `No further action/none (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="No further action/none"]),
                   `No further action/none (row %)` = scales::percent(`No further action/none (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Restitution (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Restitution"]),
                   `Restitution (row %)` = scales::percent(`Restitution (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Status Offense Description` = drg)  

### unique complaints statewide
df_complaints_disposition_outcome_table_overall <- df_analytic_complaints_disposition_caseload %>% 
  filter(dai=="Status Offense") %>% 
     dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Disposed Complaints (column %)` = scales::percent(`All Disposed Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Detention (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Detention"]),
                   `Detention (row %)` = scales::percent(`Detention (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Commitment (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Commitment"]),
                   `Commitment (row %)` = scales::percent(`Commitment (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row %)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Deferral (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Deferral"]),
                   `Deferral (row %)` = scales::percent(`Deferral (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Community Service (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Community Service"]),
                   `Community Service (row %)` = scales::percent(`Community Service (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Fine (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Fine"]),
                   `Fine (row %)` = scales::percent(`Fine (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `No further action/none (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="No further action/none"]),
                   `No further action/none (row %)` = scales::percent(`No further action/none (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Restitution (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Restitution"]),
                   `Restitution (row %)` = scales::percent(`Restitution (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Status Offense Description` = "Overall") 

### combine two dataframes for table
df_complaints_disposition_outcome_table_offense_status_final <- rbind(df_complaints_disposition_outcome_table_offense_status,
                                                              df_complaints_disposition_outcome_table_overall)


### print table via kableextra
kable(df_complaints_disposition_outcome_table_offense_status_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(4, bold = TRUE)
```

<br>

## Table 7: Disposition Outcomes by Prior JJ History 

Note: The preliminary options for grouping dispositions that I am using are: Detention, Commitment, Probation/Supervision, Deferral, Community Service, Fine, No further action/none, Restitution, Other. See the `Disposition, Preliminary Disposition Groupings` table on the `codebook` page in the `sample descriptives` tab for a full list of each disposition and I've grouped it.  


```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_disposition_outcome_table_jj_history <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(jj_history_clean)==TRUE) %>% 
  dplyr::group_by(jj_history_clean) %>% 
  dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Disposed Complaints (column %)` = scales::percent(`All Disposed Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Detention (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Detention"]),
                   `Detention (row %)` = scales::percent(`Detention (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Commitment (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Commitment"]),
                   `Commitment (row %)` = scales::percent(`Commitment (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row %)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Deferral (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Deferral"]),
                   `Deferral (row %)` = scales::percent(`Deferral (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Community Service (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Community Service"]),
                   `Community Service (row %)` = scales::percent(`Community Service (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Fine (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Fine"]),
                   `Fine (row %)` = scales::percent(`Fine (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `No further action/none (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="No further action/none"]),
                   `No further action/none (row %)` = scales::percent(`No further action/none (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Restitution (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Restitution"]),
                   `Restitution (row %)` = scales::percent(`Restitution (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`JJ History` = jj_history_clean)  

### unique complaints statewide
df_complaints_disposition_outcome_table_overall <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(jj_history_clean)==TRUE) %>% 
   dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Disposed Complaints (column %)` = scales::percent(`All Disposed Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Detention (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Detention"]),
                   `Detention (row %)` = scales::percent(`Detention (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Commitment (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Commitment"]),
                   `Commitment (row %)` = scales::percent(`Commitment (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row %)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Deferral (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Deferral"]),
                   `Deferral (row %)` = scales::percent(`Deferral (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Community Service (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Community Service"]),
                   `Community Service (row %)` = scales::percent(`Community Service (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Fine (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Fine"]),
                   `Fine (row %)` = scales::percent(`Fine (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `No further action/none (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="No further action/none"]),
                   `No further action/none (row %)` = scales::percent(`No further action/none (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Restitution (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Restitution"]),
                   `Restitution (row %)` = scales::percent(`Restitution (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  dplyr::mutate(`JJ History` = "Overall") 

### combine two dataframes for table
df_complaints_disposition_outcome_table_jj_history_final <- rbind(df_complaints_disposition_outcome_table_jj_history,
                                                             df_complaints_disposition_outcome_table_overall)


### print table via kableextra
kable(df_complaints_disposition_outcome_table_jj_history_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 8: Disposition Outcomes by Petitioner Type/Referral Source

Note: The preliminary options for grouping dispositions that I am using are: Detention, Commitment, Probation/Supervision, Deferral, Community Service, Fine, No further action/none, Restitution, Other. See the `Disposition, Preliminary Disposition Groupings` table on the `codebook` page in the `sample descriptives` tab for a full list of each disposition and I've grouped it.  

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### unique complaints split out
df_complaints_disposition_outcome_table_pet_desc <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(referral_source_clean)==TRUE) %>% 
  dplyr::group_by(referral_source_clean) %>% 
   dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Disposed Complaints (column %)` = scales::percent(`All Disposed Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Detention (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Detention"]),
                   `Detention (row %)` = scales::percent(`Detention (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Commitment (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Commitment"]),
                   `Commitment (row %)` = scales::percent(`Commitment (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row %)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Deferral (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Deferral"]),
                   `Deferral (row %)` = scales::percent(`Deferral (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Community Service (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Community Service"]),
                   `Community Service (row %)` = scales::percent(`Community Service (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Fine (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Fine"]),
                   `Fine (row %)` = scales::percent(`Fine (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `No further action/none (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="No further action/none"]),
                   `No further action/none (row %)` = scales::percent(`No further action/none (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Restitution (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Restitution"]),
                   `Restitution (row %)` = scales::percent(`Restitution (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Petitioner/Referral Source` = referral_source_clean) %>% 
  arrange(desc(`All Disposed Complaints (N)`))

### overall
df_complaints_disposition_outcome_table_overall <- df_analytic_complaints_disposition_caseload %>% 
  filter(!is.na(referral_source_clean)==TRUE) %>% 
    dplyr::summarise(`All Disposed Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Disposed Complaints (column %)` = scales::percent(`All Disposed Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Detention (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Detention"]),
                   `Detention (row %)` = scales::percent(`Detention (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Commitment (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Commitment"]),
                   `Commitment (row %)` = scales::percent(`Commitment (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Probation/Supervision (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Probation/Supervision"]),
                   `Probation/Supervision (row %)` = scales::percent(`Probation/Supervision (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Deferral (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Deferral"]),
                   `Deferral (row %)` = scales::percent(`Deferral (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Community Service (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Community Service"]),
                   `Community Service (row %)` = scales::percent(`Community Service (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Fine (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Fine"]),
                   `Fine (row %)` = scales::percent(`Fine (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `No further action/none (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="No further action/none"]),
                   `No further action/none (row %)` = scales::percent(`No further action/none (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Restitution (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Restitution"]),
                   `Restitution (row %)` = scales::percent(`Restitution (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[dispo_description_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Disposed Complaints (N)`,
                                                                       accuracy = .1)) %>%  
  dplyr::mutate(`Petitioner/Referral Source` = "Overall") 

### combine two dataframes for table
df_complaints_disposition_outcome_table_pet_desc_final <- rbind(df_complaints_disposition_outcome_table_pet_desc,
                                                             df_complaints_disposition_outcome_table_overall) 


### print table via kableextra
kable(df_complaints_disposition_outcome_table_pet_desc_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(9, bold = TRUE)
```

<br>
