---
title: "Part II Analysis: Diversion"
format: html
---

**Data Sample:** 

* Juvenile intake complaints with intake dates from July 1, 2015 - June 30, 2021

* Dispositions – all dispositions for the intake complaints in the sample. 


**Research Question:**

Conduct a front-end system assessment from intake through petition for all complaints 2016-2021.


**Methods:**

We will conduct a descriptive analysis of the front end of the system from intake through petition, provide unadjusted counts, RRI’s and means tests where applicable, by race, sex, offense, risk, CSU, and year for:

*	Complaints

*	Intake decisions: divert, resolve, petition, other

*	Average LOS on diversion 

*	Diversion completions: successful, unsuccessful, other

*	Dispositions on petitioned cases

*Cohort:* All complaints from 2016-2021  

<br>

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())

### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_analysis_analytic_data <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Data/VA/analysis/analytic"))

### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_viz <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Output/VA/r_viz_output"))
```

```{r include=FALSE}
### pull in preliminary virginia djj analytic files 

### read in preliminary analytic rds file 
df_complaints_youth_intake_decision_csu <- read_rds(file.path(sharepoint_ojjdp_va_analysis_analytic_data,"df_complaints_youth_intake_decision_csu.rds"))

### write out file for preliminary analysis
caseload_clean <- read_rds(file.path(sharepoint_ojjdp_va_analysis_analytic_data,"caseload_clean.rds"))
```

```{r include=FALSE,warning=FALSE,include=FALSE}
### create denominator -- unique complaint for entire sample
unique_complaints_sample_denom <- n_distinct(df_complaints_youth_intake_decision_csu$unique_complaint_id)

### create denominator -- unique youth for entire sample
unique_youth_sample_denom <- n_distinct(df_complaints_youth_intake_decision_csu$juvenile_number)
```


**Note:** See coding of intake decisions in `Intake Complaints, Intake Decision Descriptions` table on `codebook` page in `sample descriptives` tab

# Tables


## Table 1: % of All Complaints Diverted, 2015-2021

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### overall complaints by diversion status
df_complaints_youth_intake_decision_table <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(intake_decision_clean) %>% 
  dplyr::summarise(`Unique Complaints (N)` = n_distinct(unique_complaint_id),
            `Complaints, Percent of Sample (%)` = scales::percent(`Unique Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Intake Decision` = intake_decision_clean) 


### print table via kableextra
kable(df_complaints_youth_intake_decision_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Table 2: % of All Complaints Diverted by Year

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_year <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(date_opened_year) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Year of Complaint` = date_opened_year) 

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Year of Complaint` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_year_final <- rbind(df_complaints_youth_intake_decision_table_year,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_year_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(8, bold = TRUE)
```

<br>

## Table 3: % of All Complaints Diverted by Race/Ethnicity

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_race <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean) 

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Race/Ethnicity` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_race_final <- rbind(df_complaints_youth_intake_decision_table_race,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_race_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(8, bold = TRUE)
```

<br>

## Table 4: % of All Complaints Diverted by Gender

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_gender <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(gender_clean) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Gender` = gender_clean) 

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Gender` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_gender_final <- rbind(df_complaints_youth_intake_decision_table_gender,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_gender_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE)
```

<br>

## Table 5: % of All Complaints Diverted by Age at Petition

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

**Question:** We seem to be missing age (pet_age) for about 35% of all records in the intake complaints file -- how should we interpret this? Something seems off with this table -- why is the diversion rate so much higher for youth whose age is missing? Does missing age mean youth was not formally petitioned and thus they don't have age here?

**TO DO:** Decide on which ages to exclude because of likely data collection issues (e.g. ages of 0 or 44)

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_age <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(intake_age) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Age at Intake` = intake_age) 

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Age at Intake` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_age_final <- rbind(df_complaints_youth_intake_decision_table_age,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_age_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(44, bold = TRUE)
```

<br>

## Table 6a: % of All Complaints Diverted by Offense Type (most serious offense; mso_flag == "Y")

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_offense <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(dai) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Offense Description` = dai)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Offense Description` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_offense_final <- rbind(df_complaints_youth_intake_decision_table_offense,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_offense_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(10, bold = TRUE)
```

<br>

## Table 6b: % of All Complaints Diverted by Status Offense Type (most serious offense is status; mso_flag == "Y")

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_offense_status <- df_complaints_youth_intake_decision_csu %>% 
  filter(dai=="Status Offense") %>% 
  dplyr::group_by(drg) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>%  
  ungroup() %>% 
  dplyr::rename(`Status Offense Description` = drg)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  filter(dai=="Status Offense") %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Status Offense Description` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_offense_status_final <- rbind(df_complaints_youth_intake_decision_table_offense_status,
                                                              df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_offense_status_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(4, bold = TRUE)
```

<br>

## Table 7: % of All Complaints Diverted by Court Service Unit (CSU)

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_csu <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(csu) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`CSU` = csu)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>%  
  ungroup() %>% 
  dplyr::mutate(`CSU` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_csu_final <- rbind(df_complaints_youth_intake_decision_table_csu,
                                                             df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_csu_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(33, bold = TRUE)
```

<br>

## Table 8: % of All Complaints Diverted by Court Service Unit (CSU) Region

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

See CSU regions here: https://www.djj.virginia.gov/pages/community/court-service-units.htm

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_csu_region <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::group_by(csu_region) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`CSU Region` = csu_region)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`CSU Region` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_csu_region_final <- rbind(df_complaints_youth_intake_decision_table_csu_region,
                                                             df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_csu_region_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 9: % of All Complaints Diverted by Prior JJ History 

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

**Question:** How should we interpret missing prior JJ complaint data? About 40% of all intake complaints records appear to have missing data in these columns

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_jj_history <- df_complaints_youth_intake_decision_csu %>% 
  filter(!is.na(jj_history_clean)==TRUE) %>% 
  dplyr::group_by(jj_history_clean) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`JJ History` = jj_history_clean)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  filter(!is.na(jj_history_clean)==TRUE) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`JJ History` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_jj_history_final <- rbind(df_complaints_youth_intake_decision_table_jj_history,
                                                             df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_jj_history_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 10: % of All Complaints Diverted by Petitioner Type

Note: I am currently coding the following intake decisions as 'Diverted`: "UNSUCCESSFUL DIVERSION/PETITION FILED" (code of '18'), "SUCCESSFUL DIVERSION" (code of '20'), and "UNSUCCESSFUL DIVERSION/NO PETITION FILED" (code of '21'). All other intake decisions are coded as "Not Diverted". 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique complaints split out
df_complaints_youth_intake_decision_table_pet_desc <- df_complaints_youth_intake_decision_csu %>% 
  filter(!is.na(petitioner_desc)==TRUE) %>% 
  dplyr::group_by(petitioner_desc) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Petitioner Description` = petitioner_desc)  

### unique complaints statewide
df_complaints_youth_intake_decision_table_overall <- df_complaints_youth_intake_decision_csu %>% 
  filter(!is.na(petitioner_desc)==TRUE) %>% 
  dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
                   `All Complaints (column %)` = scales::percent(`All Complaints (N)`/unique_complaints_sample_denom,
                                                                       accuracy = .1),
                   `Complaints Petitioned (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Petitioned"]),
                   `Complaints Petitioned (row %)` = scales::percent(`Complaints Petitioned (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Diverted (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Diverted"]),
                   `Complaints Diverted (row %)` = scales::percent(`Complaints Diverted (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Complaints Dismissed (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Dismissed"]),
                   `Complaints Dismissed (row %)` = scales::percent(`Complaints Dismissed (N)`/`All Complaints (N)`,
                                                                       accuracy = .1),
                   `Other (N)` = n_distinct(unique_complaint_id[intake_decision_clean=="Other"]),
                   `Other (row %)` = scales::percent(`Other (N)`/`All Complaints (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::mutate(`Petitioner Description` = "Overall") 

### combine two dataframes for table
df_complaints_youth_intake_decision_table_pet_desc_final <- rbind(df_complaints_youth_intake_decision_table_pet_desc,
                                                             df_complaints_youth_intake_decision_table_overall)


### print table via kableextra
kable(df_complaints_youth_intake_decision_table_pet_desc_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(24, bold = TRUE)
```

<br>

## Table 11: Average Length of Stay on Diversion by Race/Ethnicity

Both measures of LOS on diversion are calculated by DJJ and provided in the `caseload` file -- see codebook page for more information. The two LOS measures are the "Number of days on the workload status "Diversion at Intake"" and the "Number of days on the workload status "Diversion Beyond 90 Days"". **Still need to check for duplicates**

```{r echo=FALSE,message=FALSE,warning=FALSE}
###  mean and median diversion lengths of stay by race/ethnicity
df_diversion_race_eth_los <- caseload_clean %>% 
  filter(!is.na(div_at_int)==TRUE | !is.na(div_bey_90)==TRUE) %>% 
  group_by(race_clean) %>% 
  dplyr::summarise(`Mean Diversion (at intake)` = mean(div_at_int,
                                           na.rm=TRUE),
                   `Median Diversion (at intake)` = median(div_at_int,
                                           na.rm=TRUE),
                   `Mean Diversion (beyond 90 days)` = mean(div_bey_90,
                                           na.rm=TRUE),
                   `Median Diversion (beyond 90 days)` = median(div_bey_90,
                                           na.rm=TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean)

### overall mean and median diversion lengths of stay
df_diversion_overall_los <- caseload_clean %>% 
  filter(!is.na(div_at_int)==TRUE | !is.na(div_bey_90)==TRUE) %>% 
  dplyr::summarise(`Mean Diversion (at intake)` = mean(div_at_int,
                                           na.rm=TRUE),
                   `Median Diversion (at intake)` = median(div_at_int,
                                           na.rm=TRUE),
                   `Mean Diversion (beyond 90 days)` = mean(div_bey_90,
                                           na.rm=TRUE),
                   `Median Diversion (beyond 90 days)` = median(div_bey_90,
                                           na.rm=TRUE)) %>% 
  mutate(`Race/Ethnicity` = "Overall")
 
### combine two dataframes for table
df_diversion_race_eth_los_final <- rbind(df_diversion_race_eth_los,
                                                             df_diversion_overall_los)

### print table via kableextra
kable(df_diversion_race_eth_los_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(8, bold = TRUE)
```

<br>

## Table 12: Average Length of Stay on Diversion by Gender

Both measures of LOS on diversion are calculated by DJJ and provided in the `caseload` file -- see codebook page for more information. The two LOS measures are the "Number of days on the workload status "Diversion at Intake"" and the "Number of days on the workload status "Diversion Beyond 90 Days"". **Still need to check for duplicates**

```{r echo=FALSE,message=FALSE,warning=FALSE}
###  mean and median diversion lengths of stay by race/ethnicity
df_diversion_gender_los <- caseload_clean %>% 
  filter(!is.na(div_at_int)==TRUE | !is.na(div_bey_90)==TRUE) %>% 
  group_by(gender_clean) %>% 
  dplyr::summarise(`Mean Diversion (at intake)` = mean(div_at_int,
                                           na.rm=TRUE),
                   `Median Diversion (at intake)` = median(div_at_int,
                                           na.rm=TRUE),
                   `Mean Diversion (beyond 90 days)` = mean(div_bey_90,
                                           na.rm=TRUE),
                   `Median Diversion (beyond 90 days)` = median(div_bey_90,
                                           na.rm=TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Gender` = gender_clean)

### overall mean and median diversion lengths of stay
df_diversion_overall_los <- caseload_clean %>% 
  filter(!is.na(div_at_int)==TRUE | !is.na(div_bey_90)==TRUE) %>% 
  dplyr::summarise(`Mean Diversion (at intake)` = mean(div_at_int,
                                           na.rm=TRUE),
                   `Median Diversion (at intake)` = median(div_at_int,
                                           na.rm=TRUE),
                   `Mean Diversion (beyond 90 days)` = mean(div_bey_90,
                                           na.rm=TRUE),
                   `Median Diversion (beyond 90 days)` = median(div_bey_90,
                                           na.rm=TRUE)) %>% 
  mutate(`Gender` = "Overall")
 
### combine two dataframes for table
df_diversion_gender_los_final <- rbind(df_diversion_gender_los,
                                                             df_diversion_overall_los)

### print table via kableextra
kable(df_diversion_gender_los_final, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE)
```

<br><br>

# Visuals

```{r include=FALSE,message=FALSE,warning=FALSE}
### read in census/acs api key from environmnent
### this allows us to pull census/acs data via the tidycensus package
readRenviron("~/.Renviron")

### read in va county-level shape file and keep geometry for mapping
### from kyle walker/tidycensus: specify cb = TRUE which defaults to the Census Bureau’s cartographic boundary shapefiles. Cartographic boundary shapefiles are preferred to the core TIGER/Line shapefiles in tidycensus as their smaller size speeds up processing and because they are pre-clipped to the US coastline.
va_county_shoreline_clipped <- get_acs(
  geography = "county",
  variables = "B19013_001",
  state = "VA",
  year = 2020,
  geometry = TRUE,
  cb = TRUE
  ) %>%
  clean_names() %>%
  # mutate(county = word(NAME, 1)) %>% 
  group_by(geoid) %>%
  summarize(geometry = st_union(geometry)) %>%
  ungroup() 

# ### use group_by and st_union to create statewide polygon using the county-level geography
# ### we'll use this shapefile for a state border when mapping
# nh_state_shape <- nh_county_shape %>%
#   group_by(statefp) %>% 
#   summarize(geometry = st_union(geometry)) %>% 
#   ungroup()

### read in va county-level shape file with fips codes to use as lookup table
va_county_shape <- read_sf("C:\\Users\\abyrum\\OneDrive - The Council of State Governments\\Geospatial_Mapping\\US County Geo Data\\tl_2019_us_county\\tl_2019_us_county.shp") %>%
  clean_names() %>% 
  filter(statefp=="51") %>% ### filter by state fip code 
  dplyr::select(county=name, 
               county_fip=countyfp,
               geoid)

### lose geometry as this is just a lookup table
va_county_lookup <- as.data.frame(va_county_shape) %>% 
    dplyr::select(-(geometry))

### now join va_county_shoreline_clipped and va_county_lookup
va_county_shoreline_clipped_final <- left_join(va_county_shoreline_clipped,
                                               va_county_lookup,
                                               by = "geoid")


```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set constants for mapping
default_font_color <- "#4e4d47"
default_font_family <- "Franklin Gothic Book"
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### create static map theme (based on https://timogrossenbacher.ch/2019/04/bivariate-maps-with-ggplot2-and-sf/)
theme_map <- function(...) {
  theme_minimal() +
  theme(
    text = element_text(family = default_font_family,
                        color = default_font_color),
    # remove all axes
    axis.line = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    # add a subtle grid
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # borders and margins
    plot.margin = unit(c(.5, .5, .2, .5), "cm"),
    panel.border = element_blank(),
    panel.spacing = unit(c(-.1, 0.2, .2, 0.2), "cm"),
    # titles
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 9, hjust = 0,
                               color = default_font_color),
    plot.title = element_text(size = 15, hjust = 0.5,
                              color = default_font_color),
    # plot.subtitle = element_text(size = 10, hjust = 0.5,
    #                              color = default_font_color,
    #                              margin = margin(b = -0.1,
    #                                              t = -0.1,
    #                                              l = 2,
    #                                              unit = "cm"),
    #                              debug = F),
    # # captions
    # plot.caption = element_text(size = 7,
    #                             hjust = .5,
    #                             margin = margin(t = 0.2,
    #                                             b = 0,
    #                                             unit = "cm"),
    #                             color = default_font_color),
    ...
  )
}
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set sharepoint path using csgjcr function
sharepoint_ojjdp_va_analysis_geo_data <- csgjcr::csg_sp_path(file.path("JJ_OJJDP/Data/VA/analysis/geo"))

# ### group diversion rate and geometry by county
# df_complaints_youth_intake_decision_county_to_join <- df_complaints_youth_intake_decision_csu %>% 
#   dplyr::group_by(fips_code) %>%
#   dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
#                    `Complaints Diverted (row %)` = n_distinct(unique_complaint_id[diverted_flag=="Yes"])/`All Complaints (N)`) %>%
#   ungroup()
# 
# df_county_level_intake_summary_geo <- left_join(va_county_shoreline_clipped_final,
#                                                      df_complaints_youth_intake_decision_county_to_join,
#                                                      by = c("county_fip"="fips_code"))
# 
# ### write out as rds file (to save time)
# write_rds(df_county_level_intake_summary_geo,
#           file.path(sharepoint_ojjdp_va_analysis_geo_data,"df_county_level_intake_summary_geo.rds"))

### read in rds file for diversion rate and geometry by county
df_county_level_intake_summary_geo <- read_rds(file.path(sharepoint_ojjdp_va_analysis_geo_data,"df_county_level_intake_summary_geo.rds"))

# ### group diversion rate and geometry by csu
# df_csu_level_intake_summary_geo <- df_county_level_intake_complaints_summary_geo %>% 
#   dplyr::group_by(csu) %>% 
#   dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
#                    `Complaints Diverted (row %)` = n_distinct(unique_complaint_id[diverted_flag=="Yes"])/`All Complaints (N)`,
#                    geometry = st_union(geometry)) %>% 
#   ungroup() 
# 
# ### write out as rds file (to save time)
# write_rds(df_csu_level_intake_summary_geo,
#           file.path(sharepoint_ojjdp_va_analysis_geo_data,"df_csu_level_intake_summary_geo.rds"))

### read in rds file for diversion rate and geometry by csu
df_csu_level_intake_summary_geo <- read_rds(file.path(sharepoint_ojjdp_va_analysis_geo_data,"df_csu_level_intake_summary_geo.rds"))

# ### group diversion rate and geometry by csu region
# ### we will initially use this file to add a region layer/label to the map
# df_csu_region_level_intake_summary_geo <- df_county_level_intake_complaints_summary_geo %>% 
#   dplyr::group_by(csu_region) %>% 
#   dplyr::summarise(`All Complaints (N)` = n_distinct(unique_complaint_id),
#                    `Complaints Diverted (row %)` = n_distinct(unique_complaint_id[diverted_flag=="Yes"])/`All Complaints (N)`,
#                    geometry = st_union(geometry)) %>% 
#   ungroup() 
# 
# ### write out as rds file (to save time)
# write_rds(df_csu_region_level_intake_summary_geo,
#           file.path(sharepoint_ojjdp_va_analysis_geo_data,"df_csu_region_level_intake_summary_geo.rds"))

### read in rds file for diversion rate and geometry by csu region
df_csu_region_level_intake_summary_geo <- read_rds(file.path(sharepoint_ojjdp_va_analysis_geo_data,"df_csu_region_level_intake_summary_geo.rds"))

```


## Figure 1: % of all Complaints Diverted by County

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### create quantiles object
no_classes <- 4

### extract quantiles from var we're mapping
quantiles <- df_county_level_intake_summary_geo %>%
  pull(`Complaints Diverted (row %)`) %>%
  quantile(probs = seq(0, 1, length.out = no_classes + 1), na.rm=TRUE) %>%
  as.vector() 

### make labels for map's legend
label_diversion_rate <- c("27% to 56%","20% to 27%","13% to 20%","2% to 13%")

### create a new variable with the specified quantiles
df_county_level_intake_summary_geo_to_map <- df_county_level_intake_summary_geo %>%
  mutate(percent_diversion_quartile = cut(-`Complaints Diverted (row %)`,
                               breaks = -quantiles,
                               right = TRUE,
                               labels = label_diversion_rate,
                               include.lowest = T)) 


### map via ggplot 
ggplot(
  # define main data source
  data = df_county_level_intake_summary_geo_to_map
) +
  scale_alpha(name = "",
              range = c(0.6, 0),
              guide = F) + # suppress legend
  # add main fill aesthetic
  geom_sf(
    mapping = aes(
      fill = percent_diversion_quartile
      ),
    color = "white",
    size = 0.1
  ) +
  #   scale_fill_distiller(
  #   labels = scales::percent_format(accuracy=1),
  #   direction = 1,
  #   name = "% Bookings with Drug/Alcohol\n Charges"
  # ) +
  ### use jr palette here
    # scale_colour_gradientn(colours = c("#D7EBF1","#AFD6E2","#87C2D4","#2F7084","#1F4A58")) +
 scale_fill_manual(
    values = c("#1F4A58","#2F7084","#87C2D4","#AFD6E2"),
    name = "% of Intake Complaints Diverted",
    na.value = "grey50",
    guide = guide_legend(
     keyheight = unit(7.5, units = "mm"),
     title.position = "top",
     reverse = F # display highest on top
  )) +
  # use white stroke borders for county boundaries
  geom_sf(
    data = df_county_level_intake_summary_geo_to_map,
    fill = "transparent",
    color = "white",
    size = .3
  )  +
  # use additional csu-level shapefile for region border
  geom_sf(
    data = df_csu_level_intake_summary_geo,
    fill = "transparent",
    color = "grey10",
    size = .8
  )  +
 # geom_label(
 #     data = df_csu_region_level_intake_summary_geo,
 #     aes(geometry = geometry,
 #         label = paste0(csu_region,"\n"," Region")),
 # family = "Franklin Gothic Demi",
 # color = "gray25",
 # size = 2.25,
 # fontface = "bold",
 # stat = "sf_coordinates") +
  # guides(fill = guide_colorbar(barwidth = 8),
  #          direction = "horizontal",
  #     barheight = unit(2, units = "mm"),
  #     barwidth = unit(50, units = "mm"),
  #     draw.ulim = F,
  #     title.position = 'top',
  #     # some shifting around
  #     title.hjust = 0.5,
  #     label.hjust = 0.5) +
  labs(
    title = NULL,
    subtitle = NULL,
    x = NULL,
    y = NULL,
    fill = NULL,
    caption = NULL
  ) +
  # add theme
  theme_map() 
# +
#   theme(
#     # plot.margin = margin(),
#     panel.grid = element_blank(),
#     axis.text.x = element_blank(),
#     axis.text.y = element_blank(),
#     legend.position = "bottom",
#     legend.justification = c(0.5, 0.5),
#     legend.text = element_text(size = 11)) 


# ### write out
# ggsave(
#     filename = file.path(sp_viz_output_path, "charge_type_percent_drug_alcohol_by_jail_non_pc.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br>

## Figure 2: % of all Complaints Diverted by Court Service Unit (CSU)

```{r echo=FALSE,message=FALSE,warning=FALSE}
#| column: page-right
#| out-width: 85%

### create quantiles object
no_classes <- 4

### extract quantiles from var we're mapping
quantiles <- df_csu_level_intake_summary_geo %>%
  pull(`Complaints Diverted (row %)`) %>%
  quantile(probs = seq(0, 1, length.out = no_classes + 1), na.rm=TRUE) %>%
  as.vector() 

### make labels for map's legend
label_diversion_rate <- c("25% to 34%","18% to 25%","12% to 18%","5% to 12%")

### create a new variable with the specified quantiles
df_csu_level_intake_summary_geo_to_map <- df_csu_level_intake_summary_geo %>%
  mutate(percent_diversion_quartile = cut(-`Complaints Diverted (row %)`,
                               breaks = -quantiles,
                               right = TRUE,
                               labels = label_diversion_rate,
                               include.lowest = T)) 


### map via ggplot 
ggplot(
  # define main data source
  data = df_csu_level_intake_summary_geo_to_map
) +
  scale_alpha(name = "",
              range = c(0.6, 0),
              guide = F) + # suppress legend
  # add main fill aesthetic
  geom_sf(
    mapping = aes(
      fill = percent_diversion_quartile
      ),
    color = "white",
    size = 0.1
  ) +
  #   scale_fill_distiller(
  #   labels = scales::percent_format(accuracy=1),
  #   direction = 1,
  #   name = "% Bookings with Drug/Alcohol\n Charges"
  # ) +
  ### use jr palette here
    # scale_colour_gradientn(colours = c("#D7EBF1","#AFD6E2","#87C2D4","#2F7084","#1F4A58")) +
 scale_fill_manual(
    values = c("#1F4A58","#2F7084","#87C2D4","#AFD6E2"),
    name = "% of Intake Complaints Diverted",
    na.value = "grey50",
    guide = guide_legend(
     keyheight = unit(7.5, units = "mm"),
     title.position = "top",
     reverse = F # display highest on top
  )) +
  # use white stroke borders for county boundaries
  geom_sf(
    data = df_csu_level_intake_summary_geo_to_map,
    fill = "transparent",
    color = "white",
    size = .3
  )  +
  # use additional csu region-level shapefile for region border
  geom_sf(
    data = df_csu_region_level_intake_summary_geo,
    fill = "transparent",
    color = "grey10",
    size = .8
  )  +
 geom_label(
     data = df_csu_region_level_intake_summary_geo,
     aes(geometry = geometry,
         label = paste0(csu_region)),
 family = "Franklin Gothic Demi",
 color = "gray25",
 size = 3,
 fontface = "bold",
 stat = "sf_coordinates") +
  # guides(fill = guide_colorbar(barwidth = 8),
  #          direction = "horizontal",
  #     barheight = unit(2, units = "mm"),
  #     barwidth = unit(50, units = "mm"),
  #     draw.ulim = F,
  #     title.position = 'top',
  #     # some shifting around
  #     title.hjust = 0.5,
  #     label.hjust = 0.5) +
  labs(
    title = NULL,
    subtitle = NULL,
    x = NULL,
    y = NULL,
    fill = NULL,
    caption = NULL
  ) +
  # add theme
  theme_map() 
# +
#   theme(
#     # plot.margin = margin(),
#     panel.grid = element_blank(),
#     axis.text.x = element_blank(),
#     axis.text.y = element_blank(),
#     legend.position = "bottom",
#     legend.justification = c(0.5, 0.5),
#     legend.text = element_text(size = 11)) 

# ### write out
# ggsave(
#     filename = file.path(sharepoint_ojjdp_va_viz, "csu_level_diversion_rate_map.png"),
#     plot = last_plot(),
#     device = ragg::agg_png,
#     dpi = 300,
#     height = 5.25,
#     width = 10,
#     units = "in",
#     bg = "transparent"
#   )
```

<br><br>
